---
output: html_document
---

```{r set up, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

library(dplyr)
library(tidyr)

# setwd('eez/conf/web')

# data with information
layers <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/layers_eez_base.csv")
targets <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/layers_eez_targets.csv")
layers_web <- "http://ohi-science.org/ohi-global/layers.html"
short_goal_web <- "https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/goal_descriptions_short"

# function to grab the info needed for the data layers
data_grab <- function(goal_code = "FIS", dims = c("status", "trend")){

st <- targets %>%
  filter(goal==goal_code, dimension %in% dims) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))
}

```


## Food Provision: Fisheries

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "FIS.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "FIS", dims = c("status", "trend"))

```

**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "FIS", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "FIS", dims = "resilience")

```

---- 

## Food Provision: Mariculture

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "MAR.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model
**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "MAR", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "MAR", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "MAR", dims = "resilience")

```


---- 

## Artisanal Fishing Opportunity 


```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "AO.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "AO", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "AO", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "AO", dims = "resilience")

```

---- 

## Natural Products

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "NP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "NP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "NP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "NP", dims = "resilience")

```

---- 

## Carbon Storage


```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "CS.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CS", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CS", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CS", dims = "resilience")

```



---- 

## Coastal Protection


```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "CP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CP", dims = "resilience")

```


---- 

## Tourism & Recreation

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "TR.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "TR", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "TR", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "TR", dims = "resilience")

```



---- 

## Livelihoods & Economies: Livelihoods

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "LIV.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LIV", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LIV", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LIV", dims = "resilience")

```

---- 

## Livelihoods & Economies: Economies

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "ECO.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ECO", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ECO", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ECO", dims = "resilience")

```


---- 

## Sense of Place: Iconic Species
```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "ICO.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ICO", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ICO", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ICO", dims = "resilience")

```


---- 

## Sense of Place: Lasting Special Places

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "LSP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LSP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LSP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LSP", dims = "resilience")

```



---- 

## Clean Waters

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "CW.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CW", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CW", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CW", dims = "resilience")

```



---- 

## Biodiversity: Species
```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "SPP.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "SPP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "SPP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "SPP", dims = "resilience")

```


---- 

## Biodiversity: Habitats

```{r, echo=FALSE, results='hide'}

        x <- tempfile(fileext = 'Rmd')
        on.exit(unlink(x))
        download.file(file.path(short_goal_web, "HAB.Rmd"), x) 
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "HAB", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "HAB", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "HAB", dims = "resilience")

```

