---
title: "Exploring AO"
author: "Jamie Afflerbach"
date: "11/7/2016"
output: html_document
---

```{r setup, echo=F, warning=F,message=F}
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=F,fig.width = 8, fig.height = 6)

options(digits = 2)

source('~/github/ohiprep/src/R/common.R')
library(readr)
library(ggplot2)
library(plotly)

goalname <- 'AO'
scenario <- c('eez2012', 'eez2013', 'eez2014', 'eez2015', 'eez2016')
dim_test <- 'score'

georegion_labels <- read_csv('~/github/ohicore/inst/extdata/georegion_labels.csv') %>%
  select(rgn_id, r1 = r1_label, r2 = r2_label, rgn_name = rgn_label) %>%
  group_by(r1) %>%
  mutate(n_r1 = n()) %>%
  ungroup()


```



***

### Georegional trends in AO scores
```{r}

scores_df <- lapply(scenario, FUN = function(x) {
      read_csv(file.path('~/github/ohi-global', x, 'scores.csv')) %>%
        mutate(scenario = x)
    }) %>%
  bind_rows() %>%
  filter(goal == goalname) %>%
  rename(rgn_id = region_id) %>%
  inner_join(georegion_labels, by = 'rgn_id')

status_line <- ggplot(scores_df %>% 
                        filter(dimension == dim_test), 
                      aes(x = scenario, y = score, group = rgn_id, color = r1, text = rgn_name)) +
  geom_line(size = 1, alpha = .8) +
  facet_wrap("r1")+
  labs(color = 'georegion',
       title = paste0(goalname, ' ', dim_test))+ theme(legend.position="none")+ theme(legend.position="none")

print(status_line)
ggsave(paste0('testing_goals_ja/', goalname, '_', dim_test, '.png'))
```


```{r}
#looking at mean 

mean_geo_score <- ggplot(scores_df%>%
                    group_by(r1, scenario,dimension)%>%
                    summarise(mean_score = mean(score),
                              sd_score = sd(score)),
                    aes(x=scenario, y = mean_score, group = dimension, color = dimension, text = r1))+
    facet_wrap('r1')+
  #geom_errorbar(aes(ymin=mean_score-sd_score, ymax=mean_score+sd_score), width=.1)+
  geom_line(size=1,alpha=0.7)+
theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(color = 'georegion',
       title = paste0("Dimensions of ", goalname, ' through time'))

print(mean_geo_score)


# looking at mean trend

mean_geo_trend <- ggplot(scores_df%>%
                            filter(dimension == 'trend')%>%
                    group_by(r1, scenario)%>%
                    summarise(mean_trend = mean(score),
                              sd_score = sd(score)),
                    aes(x=scenario, y = mean_trend, group = r1, color = r1, text = r1))+
    facet_wrap('r1')+
  geom_errorbar(aes(ymin=mean_trend-sd_score, ymax=mean_trend+sd_score), width=.1)+
  geom_line(size=1,alpha=0.7)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(color = 'georegion',
       title = paste0("Mean ", goalname, ' ', 'trend through time'))+ theme(legend.position="none")

print(mean_geo_trend)


```


***

### Countries with increased AO scores
```{r score_changes}

diffs_df <- scores_df %>%
            filter(dimension == dim_test) %>%
            group_by(rgn_id) %>%
            mutate(incr_score = first(score) < last(score),
                   decr_score = first(score) > last(score)) %>%
            ungroup()

incr_df <- diffs_df %>% 
  filter(incr_score)

  incr_status_line <- ggplot(incr_df, 
                             aes(x = scenario, y = score, group = rgn_id, color = r1, text = rgn_name)) +
    facet_wrap(~r1)+
    geom_line(size = 1, alpha = .8) +
    # scale_color_brewer(palette = 'RdYlBu') +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    labs(color = 'georegion',
         title = paste0('increase in ', goalname, ' ', dim_test, '; n = ', length(incr_df$rgn_id %>% unique())))
  
ggplotly(incr_status_line, tooltip = c('text', 'y'))
ggsave(paste0('testing_goals_ja/', goalname, '_', dim_test, '_incr.png'))
  
  incr_df1 <- incr_df %>%
    select(rgn_id, rgn_name, r1, n_r1) %>%
    distinct() %>%
    group_by(r1) %>%
    mutate(prop_incr = n()/n_r1) %>%
    ungroup() %>%
    select(r1, prop_incr) %>%
    distinct()
  
```

#### Proportion of region with increasing scores
```{r}
  DT::datatable(incr_df1)

```

***

### Countries with decreased AO scores

```{r ao_decr}
decr_df <- diffs_df %>% 
  filter(decr_score)

  decr_status_line <- ggplot(decr_df, 
                             aes(x = scenario, y = score, group = rgn_id, color = r1, text = rgn_name)) +
    geom_line(size = 1, alpha = .8) +
    facet_wrap(~r1)+
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    labs(color = 'georegion',
         title = paste0('decrease in ', goalname, ' ', dim_test, '; n = ', length(decr_df$rgn_id %>% unique())))
  
  ggplotly(decr_status_line,tooltip = c('text', 'y'))
  ggsave(paste0('testing_goals_ja/', goalname, '_', dim_test, '_decr.png'))
  
  decr_df1 <- decr_df %>%
    select(rgn_id, rgn_name, r1, n_r1) %>%
    distinct() %>%
    group_by(r1) %>%
    mutate(prop_dec = n()/n_r1) %>%
    ungroup() %>%
    select(r1, prop_dec) %>%
    distinct()
```

#### Proportion of regions with decreasing scores
```{r}

  DT::datatable(decr_df1)

```

***

### Countries with no change

```{r}

same_df <- diffs_df %>% 
  filter(!decr_score & !incr_score)

  same_df_check <- same_df %>%
    select(-scenario) %>%
    distinct() %>%
    group_by(rgn_id) %>%
    mutate(dupes = n() > 1) %>%
    ungroup()
  
  same_status_pt <- ggplot(same_df %>% 
                              filter(!decr_score & !incr_score) %>%
                             filter(scenario == 'eez2016'), 
                           aes(x = scenario, y = score, color = r1, text = rgn_name)) +
    geom_jitter(height = 0) +
    labs(color = 'georegion',
         title = paste0('no change in ', goalname, ' ', dim_test, '; n = ', length(same_df$rgn_id %>% unique())))
  
 ggplotly(same_status_pt,tooltip = c('text', 'y'))
  ggsave(paste0('testing_goals_ja/', goalname, '_', dim_test, '_same.png'))
  
  same_df1 <- same_df %>%
    select(rgn_id, rgn_name, r1, n_r1) %>%
    distinct() %>%
    group_by(r1) %>%
    mutate(prop_same = n()/n_r1) %>%
    ungroup() %>%
    select(r1, prop_same) %>%
    distinct()
  
  DT::datatable(same_df1)

```

***

### Countries with NA for AO goal

There are no countries with NA for the AO goal.
```{r nas_ao}

na_df <- scores_df %>%
  filter(dimension == dim_test & is.na(score)) %>%
  mutate(blah = paste0(scenario, '_', rgn_name))

message('NAs in ', goalname, ' ', dim_test, ':\n  ', paste0(na_df$blah, collapse = '\n  '))

```

### Taking a closer look at Africa

Libya has a large increase between 2012-2013 then slow decrease. Equatorial guinea strongest decreasing trend.

```{r}
### some additional testing/plotting to examine by specific regions

scores_df %>% 
  filter(str_detect(r2, 'Africa')) %>% ### filter by r2 to access sub-region names; by r1 for georegion names
  filter(dimension == dim_test) %>%
  .$score %>% 
  hist(main = "AO scores of African Countries")

af <- ggplot(scores_df %>% 
         filter(str_detect(r2, 'Africa')) %>% ### can filter by r1 regions or r2 subregions here;
         filter(dimension == dim_test), 
       aes(text=rgn_name, x = scenario, y = score, group = rgn_id, color = r2, text = rgn_name)) + ### color = r2 so codes by sub-regions
  geom_line(size = 1, alpha = .8) +
  facet_wrap(~r2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(color = 'georegion',
       title = paste0(goalname, ' ', dim_test, "-Africa"))

ggplotly(af, tooltip = c('text', 'y'))
```


#### Looking at Asia

```{r}
scores_df %>% 
  filter(str_detect(r2, 'Asia')) %>% ### filter by r2 to access sub-region names; by r1 for georegion names
  filter(dimension == dim_test) %>%
  .$score %>% 
  hist(main = "AO scores of Asian Countries")

as <- ggplot(scores_df %>% 
         filter(str_detect(r2, 'Asia')) %>% ### can filter by r1 regions or r2 subregions here;
         filter(dimension == dim_test), 
       aes(text=rgn_name, x = scenario, y = score, group = rgn_id, color = r2, text = rgn_name)) + ### color = r2 so codes by sub-regions
  facet_wrap(~r2)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  geom_line(size = 1, alpha = .8) +
  labs(color = 'georegion',
       title = paste0(goalname, ' ', dim_test,"-Asia"))

ggplotly(as, tooltip = c('text', 'y'))


```


Looking at Oman, Equatorial Guinea and Libya

```{r}
ctrs <- c("Libya", "Equatorial Guinea","Oman")

new_df <- scores_df%>%
          filter(rgn_name %in% ctrs)

ctry <- ggplot(new_df,aes(x = scenario, y = score, group = dimension, color = dimension, text = dimension))+
  geom_line(size = 1, alpha = 0.7)+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  facet_wrap(~rgn_name)

ggplotly(ctry, tooltip = c('text','y'))

```






