```{r set up}
#load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(hwriter)
library(RColorBrewer)
library(knitr)
library(googleVis)
library(ohicore)
library(sp)
library(rgdal)
library(DT)
library(broom)
library(nlme)

# Set working directory when not knitting:
 setwd("global2016/Reporting")
scenario <- "2016" #identify scenario of focus (this can be changed to obtain data for other years)
benchmark = 2015  # year that is used for old vs. new OHI analyses
oldCommit = '1d4dcb1abb82dc1d20817acca33c7e7d2ef1b52f' # '4da6b4a1d69d694264ea68456359a939b0c03f9c' = commit for 2014 analysis
colorScheme <- 'new'  # color scheme to use on flower plots ("new" = color reflects size score and is not the original rainbow)
saveFile <- 'global2016' #location where files that are created are to be saved

## General files to load
rgn_names <- read.csv(sprintf('../../eez%s/layers/rgn_global.csv', scenario)) %>%
  dplyr::select(region_id = rgn_id, country = label) %>%
  dplyr::mutate(country = as.character(country))

rgn_names$country[rgn_names$region_id == 212] <- "Gilbert Islands (Kiribati)"
rgn_names$country[rgn_names$region_id == 148] <- "Line Islands (Kiribati)"
rgn_names$country[rgn_names$region_id == 157] <- "Phoenix Islands (Kiribati)"


radicalFile = '2016-11-17' #date extension on the radical data files that are used for all tables/figures



```

  
```{r future state dataprep, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}

meta <- read.csv('../../eez2016/conf/goals.csv', stringsAsFactors=FALSE) %>%
  mutate(parent = ifelse(parent=="", goal, parent)) %>%
  mutate(supragoal = ifelse(goal == parent, "supragoal", NA)) %>%
  filter(supragoal == "supragoal") %>%
  select(goal=parent, weight)

data <- read.csv(sprintf('../radical_%s.csv', radicalFile)) 

### getting index status scores (it seems like this should be output in ohicore,
### I think this change would occur in line 207 in CalculateAll.R)
index_status <- data %>%
  filter(goal != "Index") %>%
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  filter(region_id != 300) %>%
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213) %>%
  filter(dimension == "status") %>%
  left_join(meta, by="goal") %>%
  filter(goal %in% meta$goal) %>%
  group_by(scenario, region_id) %>%
  summarize(value = weighted.mean(value, weight, na.rm=TRUE)) %>%
  mutate(goal = "Index") %>%
  mutate(dimension = "status") %>%
  select(scenario, goal, dimension, region_id, value) %>%
  data.frame()

data_and_status <- data %>%
  rbind(index_status) %>%
  filter(goal == "Index") %>%
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  filter(region_id != 300) %>%
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  %>%
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(variable= paste(dimension, scenario, sep="_")) %>%
  select(region_id, value, country, variable) %>%
  data.frame()

data_sp <- spread(data_and_status, variable, value) %>%
  mutate(pred_change = likely_future_state_2012 - status_2012) %>%
  mutate(obs_change = status_2016 - status_2012)

write_csv(data_sp, 'data/fig5_data.csv')

```



# Analyses of data

One thing we have been interested in is how well the likely future state score actually predicts the future score.

My initial conclusions are that the trend/pressure/resilience components of the likely future state score are not improving our predictions.

### Scores 2012 vs 2016
```{r scores 2012 to 2016 compare fig5a}

data_sp <- read_csv('data/fig5_data.csv')
mod <- lm(score_2016 ~ score_2012, data=data_sp)
summary(mod)

score_diff <- data_sp$score_2016 - data_sp$score_2012
score_up10 <- data_sp$country[score_diff >= 10]
score_down10 <- data_sp$country[score_diff <= (-10)]

data_sp <- data_sp %>%
  mutate(label_up10 = ifelse(country %in% score_up10, as.character(country), NA)) %>%
    mutate(label_down10 = ifelse(country %in% score_down10, as.character(country), NA))


p <-   ggplot(data_sp, aes(x=score_2012, y=score_2016)) +
  geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=1.75, color="gray30", alpha=0.5) +
  geom_text(aes(label=label_down10), hjust=0, nudge_x=1.5, size=2) + 
  geom_text(aes(label=label_up10), hjust=1, nudge_x=-1.5, size=2) + 
  theme_bw() + 
  labs(x="Observed 2012 score", y="Observed 2016 score") +
  geom_abline(slope=1, intercept=0, color="red") +
  xlim(0, 100) +
  ylim(0, 100)
p
ggsave("figures/scores_2012vs2016.png", width = 4, height=3)


## use to ID regions
  # plotly_fig <- plotly::ggplotly(p)
  # plotly_fig

```


### Observed 2016 status vs. 2012 likely future status
```{r future state first, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}

mod <- lm(status_2016 ~ likely_future_state_2012, data=data_sp)
summary(mod)
confint(mod)

p <-   ggplot(data_sp, aes(x=likely_future_state_2012, y=status_2016)) +
  geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=1.75, color="gray30", alpha=0.5) +
  theme_bw() + 
  labs(x="Predicted 2016 status (from 2012 data)", y="Observed 2016 status") +
  geom_abline(slope=1, intercept=0, color="red") +
  stat_smooth(method=lm, se=FALSE, color="black", size=0.75) +
  xlim(0, 100) +
  ylim(0, 100)
p
ggsave("figures/pred_obs_status.png", width = 4, height=3)

## use to ID regions
  # plotly_fig <- plotly::ggplotly(p)
  # plotly_fig


```

### Predicted change in status vs. observed change in status (from 2012 to 2016)
*Methods:* Another way to look at these is to compare the predicted and observed changes in status from 2012 to 2016.  

The predicted change in status was calculated as: status (2012) minus likely future score (2012).
The observed change in score was calcualted as status (2012) minus status (2016).

*Results:* There was no correlation between the predicted change in status and the observed change in status:
```{r future state third 5c, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}

mod <- lm(obs_change ~ pred_change, data=data_sp)
summary(mod)


p <-   ggplot(data_sp, aes(x=pred_change, y=obs_change)) +
  geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=1.75, color="gray30", alpha=0.5) +
  theme_bw() + 
  labs(y="Observed change in status", x="Predicted change in status")
  #geom_abline(slope=1, intercept=0, color="red") 
p
ggsave("figures/change_vs_predictedChange.png", width = 4, height=3)


## use to ID regions
  # plotly_fig <- plotly::ggplotly(p)
  # plotly_fig


```

### Looking more closely at patterns within goals/subgoals
The next step in the above analysis is to look within each goal/subgoal to get a better feel for possible relationships between trend and pressure/resilience components.

```{r future state goal dataprep, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}

data <- read.csv(sprintf('../radical_%s.csv', radicalFile)) 

data <- data %>%
filter(goal != "Index") %>%
filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
filter(region_id != 300) %>%
filter(region_id <= 250) %>%       # get rid of high seas regions
filter(region_id != 213)  %>%
left_join(rgn_names, by=c('region_id'))

data_goal <- function(data, goal="AO"){ #goal="CP"
data_g <- data[data$goal==goal, ]

data_g <- data_g %>%
filter(scenario %in% c(2012, 2016)) %>%
mutate(dim_scen = paste(dimension, scenario, sep="_")) %>%
select(dim_scen, region_id, country, value) %>%
spread(dim_scen, value) %>%
mutate(pred_change = likely_future_state_2012 - status_2012) %>%
mutate(obs_change = status_2016 - status_2012) %>%
mutate(r_minus_p = resilience_2012 - pressures_2012)

p <-   ggplot(data_g, aes(x=pred_change, y=obs_change)) +
geom_point(shape=19) +
theme_bw() + 
labs(title=goal, y="Observed change in status", x="Predicted change in status") +
geom_abline(slope=1, intercept=0, color="red")
print(p)

mod <- lm(obs_change ~ pred_change, data=data_g)
print(summary(mod))    

mod2 <- lm(obs_change ~ trend_2012 + r_minus_p, data=data_g)
print(summary(mod2))

mod3 <- lm(obs_change ~ trend_2012 + pressures_2012 + resilience_2012, data=data_g)
print(summary(mod3))
}


```

### AO: A closer look
```{r future state AO, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="AO")

```

### BD/SPP: A closer look
```{r future state SPP, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="SPP")

```

### BD/HAB: A closer look
```{r future state HAB, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="HAB")

```

### CP: A closer look
```{r future state CP, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="CP")

```

### CS: A closer look
```{r future state CS, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="CS")

```

### CW: A closer look
```{r future state CW, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="CW")

```

### FP/FIS: A closer look
```{r future state FIS, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="FIS")

```

### FP/MAR: A closer look
```{r future state MAR, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="MAR")

```

### SP/ICO: A closer look
```{r future state ICO, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="ICO")

```

### SP/LSP: A closer look
```{r future state LSP, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="LSP")

```

### NP: A closer look
```{r future state NP, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="NP")

```

### TR: A closer look
```{r future state TR, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
data_goal(data, goal="TR")

```
