--- 
title: Layers descriptions 
output: 
  html_document: 
    toc: true 
    toc_depth: 1 
    number_sections: false 
    toc_float: yes 
---

```{r, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE} 
 library(dplyr) 
 library(tidyr) 
 library(knitr) 
 
 layer_meta <- read.csv('../../eez_layers_meta_data/layers_eez_base.csv', stringsAsFactors = FALSE) 
 layer_path <- 'https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers' 
 
 
```

 
#Adjusted workforce size 
####[le_workforcesize_adj](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_workforcesize_adj.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_workforcesize_adj.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of jobs

 
#Adjustment factor for jobs (current) 
####[le_jobs_cur_adj_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_jobs_cur_adj_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_cur_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for jobs (reference) 
####[le_jobs_ref_adj_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_jobs_ref_adj_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_ref_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for revenue (current) 
####[le_rev_cur_adj_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_rev_cur_adj_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_cur_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for revenue (reference) 
####[le_rev_ref_adj_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_rev_ref_adj_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_ref_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for wages (current) 
####[le_wage_cur_adj_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_wage_cur_adj_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_cur_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for wages (reference) 
####[le_wage_ref_adj_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_wage_ref_adj_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_ref_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Areas of blast fishing 
####[np_blast](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/np_blast.csv) {-} 
```{r, child = '../../global_supplement/layers_info/np_blast.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Areas of poison fishing 
####[np_cyanide](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/np_cyanide.csv) {-} 
```{r, child = '../../global_supplement/layers_info/np_cyanide.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Artisanal fisheries management effectiveness 
####[fp_mora_artisanal](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_mora_artisanal.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mora_artisanal.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Artisanal fisheries opportunity 
####[ao_access](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/ao_access.csv) {-} 
```{r, child = '../../global_supplement/layers_info/ao_access.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Average species condition 
####[spp_status](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/spp_status.csv) {-} 
```{r, child = '../../global_supplement/layers_info/spp_status.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 status score

 
#Average species condition trend 
####[spp_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/spp_trend.csv) {-} 
```{r, child = '../../global_supplement/layers_info/spp_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend score

 
#B/Bmsy estimates 
####[fis_b_bmsy](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fis_b_bmsy.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fis_b_bmsy.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 B/Bmsy

 
#Carbon storage weights 
####[element_wts_cs_km2_x_storage](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/element_wts_cs_km2_x_storage.csv) {-} 
```{r, child = '../../global_supplement/layers_info/element_wts_cs_km2_x_storage.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 extent*storage

 
#Chemical pollution 
####[po_chemicals](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_chemicals.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_chemicals.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Chemical pollution trend 
####[cw_chemical_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cw_chemical_trend.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cw_chemical_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#CITES signatories 
####[g_cites](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/g_cites.csv) {-} 
```{r, child = '../../global_supplement/layers_info/g_cites.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 0 or 1

 
#Coastal chemical pollution 
####[po_chemicals_3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_chemicals_3nm.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_chemicals_3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal nutrient pollution 
####[po_nutrients_3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_nutrients_3nm.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_nutrients_3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal protected marine areas (fishing preservation) 
####[fp_mpa_coast](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_mpa_coast.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mpa_coast.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal protected marine areas (habitat preservation) 
####[hd_mpa_coast](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hd_mpa_coast.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hd_mpa_coast.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal protection weights 
####[element_wts_cp_km2_x_protection](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/element_wts_cp_km2_x_protection.csv) {-} 
```{r, child = '../../global_supplement/layers_info/element_wts_cp_km2_x_protection.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 extent*rank

 
#Commercial fishing management 
####[fp_mora](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_mora.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mora.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Economic diversity 
####[li_sector_evenness](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/li_sector_evenness.csv) {-} 
```{r, child = '../../global_supplement/layers_info/li_sector_evenness.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled

 
#Economic need for artisanal fishing 
####[ao_need](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/ao_need.csv) {-} 
```{r, child = '../../global_supplement/layers_info/ao_need.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#EEZ protected marine areas (fishing preservation) 
####[fp_mpa_eez](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_mpa_eez.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mpa_eez.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#EEZ protected marine areas (habitat preservation) 
####[hd_mpa_eez](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hd_mpa_eez.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hd_mpa_eez.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Fishery catch data 
####[fis_meancatch](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fis_meancatch.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fis_meancatch.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 tonnes

 
#Food provision weights 
####[fp_wildcaught_weight](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_wildcaught_weight.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_wildcaught_weight.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#GDP 
####[le_gdp](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_gdp.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_gdp.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 2012 USD

 
#GDP per capita PPP 
####[le_gdp_pc_ppp](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_gdp_pc_ppp.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_gdp_pc_ppp.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 USD

 
#Genetic escapes 
####[sp_genetic](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/sp_genetic.csv) {-} 
```{r, child = '../../global_supplement/layers_info/sp_genetic.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Global Competitiveness Index (GCI) scores 
####[li_gci](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/li_gci.csv) {-} 
```{r, child = '../../global_supplement/layers_info/li_gci.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled

 
#Habitat condition 
####[hab_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hab_health.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hab_health.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Habitat condition trend 
####[hab_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hab_trend.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hab_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Habitat extent 
####[hab_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hab_extent.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hab_extent.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Habitat weights 
####[element_wts_hab_pres_abs](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/element_wts_hab_pres_abs.csv) {-} 
```{r, child = '../../global_supplement/layers_info/element_wts_hab_pres_abs.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 boolean

 
#High bycatch due to artisanal fishing 
####[fp_art_hb](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_art_hb.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_art_hb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#High bycatch due to commercial fishing 
####[fp_com_hb](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_com_hb.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_com_hb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Inland area 
####[rgn_area_inland1km](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/rgn_area_inland1km.csv) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_area_inland1km.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Inland coastal population 
####[mar_coastalpopn_inland25mi](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/mar_coastalpopn_inland25mi.csv) {-} 
```{r, child = '../../global_supplement/layers_info/mar_coastalpopn_inland25mi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of people

 
#Inland coastal protected areas 
####[lsp_prot_area_inland1km](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/lsp_prot_area_inland1km.csv) {-} 
```{r, child = '../../global_supplement/layers_info/lsp_prot_area_inland1km.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Intertidal habitat destruction 
####[hd_intertidal](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hd_intertidal.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hd_intertidal.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#ISO country codes 
####[cntry_rgn](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cntry_rgn.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cntry_rgn.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 region id

 
#IUCN extinction risk 
####[ico_spp_iucn_status](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/ico_spp_iucn_status.csv) {-} 
```{r, child = '../../global_supplement/layers_info/ico_spp_iucn_status.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 IUCN risk category

 
#Jobs for each sector and year 
####[le_jobs_sector_year](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_jobs_sector_year.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_sector_year.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of jobs

 
#Jobs, most current value 
####[le_jobs_cur_base_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_jobs_cur_base_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_cur_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Jobs, reference value 
####[le_jobs_ref_base_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_jobs_ref_base_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_ref_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Low bycatch due to artisanal fishing 
####[fp_art_lb](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_art_lb.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_art_lb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Low bycatch due to commercial fishing 
####[fp_com_lb](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_com_lb.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_com_lb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of habitat to protect fisheries biodiversity  
####[fp_habitat](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_habitat.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_habitat.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of habitat to protect habitat biodiversity 
####[hd_habitat](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hd_habitat.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hd_habitat.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of mariculture  to preserve biodiversity 
####[g_mariculture](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/g_mariculture.csv) {-} 
```{r, child = '../../global_supplement/layers_info/g_mariculture.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of nonindigenous species 
####[sp_alien_species](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/sp_alien_species.csv) {-} 
```{r, child = '../../global_supplement/layers_info/sp_alien_species.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of tourism to preserve biodiversity 
####[g_tourism](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/g_tourism.csv) {-} 
```{r, child = '../../global_supplement/layers_info/g_tourism.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of waters to preserve biodiversity 
####[po_water](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_water.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_water.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Mariculture harvest 
####[mar_harvest_tonnes](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/mar_harvest_tonnes.csv) {-} 
```{r, child = '../../global_supplement/layers_info/mar_harvest_tonnes.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 tonnes

 
#Mariculture Sustainability Index 
####[g_msi_gov](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/g_msi_gov.csv) {-} 
```{r, child = '../../global_supplement/layers_info/g_msi_gov.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Mariculture sustainability score 
####[mar_sustainability_score](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/mar_sustainability_score.csv) {-} 
```{r, child = '../../global_supplement/layers_info/mar_sustainability_score.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Marine plastics 
####[po_trash](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_trash.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_trash.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Measure of coastal ecological integrity 
####[species_diversity_3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/species_diversity_3nm.csv) {-} 
```{r, child = '../../global_supplement/layers_info/species_diversity_3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Measure of ecological integrity 
####[species_diversity_eez](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/species_diversity_eez.csv) {-} 
```{r, child = '../../global_supplement/layers_info/species_diversity_eez.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Natural product harvest 
####[np_harvest_tonnes](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/np_harvest_tonnes.csv) {-} 
```{r, child = '../../global_supplement/layers_info/np_harvest_tonnes.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 tonnes

 
#Nonindigenous species 
####[sp_alien](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/sp_alien.csv) {-} 
```{r, child = '../../global_supplement/layers_info/sp_alien.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Nutrient pollution 
####[po_nutrients](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_nutrients.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_nutrients.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Nutrient pollution trend 
####[cw_nutrient_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cw_nutrient_trend.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cw_nutrient_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Ocean acidification 
####[cc_acid](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cc_acid.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cc_acid.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Offshore area 
####[rgn_area_offshore3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/rgn_area_offshore3nm.csv) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_area_offshore3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Offshore coastal protected areas 
####[lsp_prot_area_offshore3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/lsp_prot_area_offshore3nm.csv) {-} 
```{r, child = '../../global_supplement/layers_info/lsp_prot_area_offshore3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#OHI regions 
####[rgn_global](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/rgn_global.csv) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_global.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 label

 
#Pathogen pollution 
####[po_pathogens](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/po_pathogens.csv) {-} 
```{r, child = '../../global_supplement/layers_info/po_pathogens.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Pathogen pollution trend 
####[cw_pathogen_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cw_pathogen_trend.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cw_pathogen_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Percent direct employment in tourism 
####[tr_jobs_pct_tourism](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/tr_jobs_pct_tourism.csv) {-} 
```{r, child = '../../global_supplement/layers_info/tr_jobs_pct_tourism.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Plastic trash trends 
####[cw_trash_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cw_trash_trend.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cw_trash_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Region areas based on EEZ boundaries 
####[rgn_area](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/rgn_area.csv) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_area.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Regions 
####[rgn_labels](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/rgn_labels.csv) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_labels.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 label

 
#Relative harvest tonnes 
####[np_harvest_tonnes_relative](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/np_harvest_tonnes_relative.csv) {-} 
```{r, child = '../../global_supplement/layers_info/np_harvest_tonnes_relative.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Relative harvest value 
####[np_harvest_product_weight](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/np_harvest_product_weight.csv) {-} 
```{r, child = '../../global_supplement/layers_info/np_harvest_product_weight.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Revenue adjustment (GDP) 
####[le_revenue_adj](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_revenue_adj.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_revenue_adj.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 USD

 
#Revenue for each sector and year 
####[le_rev_sector_year](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_rev_sector_year.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_sector_year.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 2010 USD

 
#Revenue, most current value 
####[le_rev_cur_base_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_rev_cur_base_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_cur_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Revenue, reference value 
####[le_rev_ref_base_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_rev_ref_base_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_ref_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Sea level rise 
####[cc_slr](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cc_slr.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cc_slr.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Sea surface temperature 
####[cc_sst](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cc_sst.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cc_sst.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Sectors in each region 
####[le_sector_weight](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_sector_weight.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_sector_weight.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Social Progress Index 
####[res_spi](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/res_spi.csv) {-} 
```{r, child = '../../global_supplement/layers_info/res_spi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Strength of governance 
####[wgi_all](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/wgi_all.csv) {-} 
```{r, child = '../../global_supplement/layers_info/wgi_all.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Subtidal hardbottom habitat destruction 
####[hd_subtidal_hb](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hd_subtidal_hb.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hd_subtidal_hb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Subtidal softbottom habitat destruction 
####[hd_subtidal_sb](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/hd_subtidal_sb.csv) {-} 
```{r, child = '../../global_supplement/layers_info/hd_subtidal_sb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Targeted harvest of cetaceans and marine turtles 
####[fp_targetharvest](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/fp_targetharvest.csv) {-} 
```{r, child = '../../global_supplement/layers_info/fp_targetharvest.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Total human population 
####[le_popn](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_popn.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_popn.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of people

 
#Tourism sustainability index 
####[tr_sustainability](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/tr_sustainability.csv) {-} 
```{r, child = '../../global_supplement/layers_info/tr_sustainability.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Unemployment 
####[le_unemployment](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_unemployment.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_unemployment.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#UN geopolitical region classifications 
####[rgn_georegions](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/rgn_georegions.csv) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_georegions.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 UN regions

 
#US State Department travel warnings 
####[tr_travelwarnings](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/tr_travelwarnings.csv) {-} 
```{r, child = '../../global_supplement/layers_info/tr_travelwarnings.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#UV radiation 
####[cc_uv](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/cc_uv.csv) {-} 
```{r, child = '../../global_supplement/layers_info/cc_uv.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Wages, current value 
####[le_wage_cur_base_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_wage_cur_base_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_cur_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Wages for each sector and year 
####[le_wage_sector_year](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_wage_sector_year.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_sector_year.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 2010 USD

 
#Wages, reference value 
####[le_wage_ref_base_value](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/le_wage_ref_base_value.csv) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_ref_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Weakness of governance 
####[ss_wgi](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/ss_wgi.csv) {-} 
```{r, child = '../../global_supplement/layers_info/ss_wgi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Weakness of social progress 
####[ss_spi](https://github.com/OHI-Science/ohi-global/tree/draft/eez2016/layers/ss_spi.csv) {-} 
```{r, child = '../../global_supplement/layers_info/ss_spi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1
