---
output: html_document
---

```{r set up, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}

library(dplyr)
library(tidyr)

# setwd('eez/conf/web')

# data with information
layers <- read.csv("../../../eez_layers_meta_data/layers_eez_base.csv")
targets <- read.csv("../../../eez_layers_meta_data/layers_eez_targets.csv")
layers_web <- "http://ohi-science.org/ohi-global/layers.html"


# function to grab the info needed for the data layers
data_grab <- function(goal_code = "FIS", dims = c("status", "trend")){

st <- targets %>%
  filter(goal==goal_code, dimension %in% dims) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))
}

```


## Food Provision: Fisheries

```{r, child='../../../global_supplement/goal_descriptions_short/FIS.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "FIS", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "FIS", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "FIS", dims = "resilience")

```

---- 

## Food Provision: Mariculture

```{r, child='../../../global_supplement/goal_descriptions_short/MAR.Rmd', results='asis', echo=FALSE}
```

### Data used in model
**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "MAR", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "MAR", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "MAR", dims = "resilience")

```


---- 

## Artisanal Fishing Opportunity 

```{r, child='../../../global_supplement/goal_descriptions_short/AO.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "AO", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "AO", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "AO", dims = "resilience")

```

---- 

## Natural Products

```{r, child='../../../global_supplement/goal_descriptions_short/NP.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "NP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "NP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "NP", dims = "resilience")

```

---- 

## Carbon Storage

```{r, child='../../../global_supplement/goal_descriptions_short/CS.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CS", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CS", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CS", dims = "resilience")

```



---- 

## Coastal Protection

```{r, child='../../../global_supplement/goal_descriptions_short/CP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CP", dims = "resilience")

```


---- 

## Tourism & Recreation

```{r, child='../../../global_supplement/goal_descriptions_short/TR.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "TR", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "TR", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "TR", dims = "resilience")

```



---- 

## Livelihoods & Economies: Livelihoods

```{r, child='../../../global_supplement/goal_descriptions_short/LIV.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LIV", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LIV", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LIV", dims = "resilience")

```

---- 

## Livelihoods & Economies: Economies

```{r, child='../../../global_supplement/goal_descriptions_short/ECO.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ECO", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ECO", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ECO", dims = "resilience")

```


---- 

## Sense of Place: Iconic Species

```{r, child='../../../global_supplement/goal_descriptions_short/ICO.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ICO", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ICO", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "ICO", dims = "resilience")

```


---- 

## Sense of Place: Lasting Special Places

```{r, child='../../../global_supplement/goal_descriptions_short/LSP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LSP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LSP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "LSP", dims = "resilience")

```



---- 

## Clean Waters

```{r, child='../../../global_supplement/goal_descriptions_short/CW.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CW", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CW", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "CW", dims = "resilience")

```



---- 

## Biodiversity: Species

```{r, child='../../../global_supplement/goal_descriptions_short/SPP.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "SPP", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "SPP", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "SPP", dims = "resilience")

```


---- 

## Biodiversity: Habitats

```{r, child='../../../global_supplement/goal_descriptions_short/HAB.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "HAB", dims = c("status", "trend"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "HAB", dims = "pressure")

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

data_grab(goal_code = "HAB", dims = "resilience")

```

