---
title: "Goals"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```

OHI assessments categorize and score goals representing ocean-derived benefits to people.

**Global assessments score 10 goals, some of which have sub-goals**.  
Here you will find information about how goals were represented, including how they are affected by pressures and resilience measures, and the underlying data and data processing.  

See [the goals page](http://ohi-science.org/) to learn how other OHI assessments have have approached each goal.  
See [the global data page](http://ohi-science.org/ohi-global/layers.html) for a complete list of data and data processing.  
<!--- TODO: link to supplement --->



```{r, child=sprintf('%s/conf/goals.Rmd', dir_scenario)}
```

----

**TO CONSIDER** (and see [SEASIDE CHAT NOTES](https://github.com/OHI-Science/issues/issues/665#issuecomment-261118749))

- remove layers page and instead list layers and links to data prep below the goals
- show Mel's pie chart
- [little icon figures!]
- Tiny figures showing relative contributions?
