---
title: "Goals in global OHI assessments"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```
 
<!---From http://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown:
Put in your css file or directly in rmarkdown--->
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>
 
<br> 
**Global Ocean Health Index assessments score 10 goals, some of which have sub-goals**. Here you will find a description about how goals are represented in global assessments. Goal-by-goal, you can explore the data used to model status and trend, as well as the pressures and resilience measures contributing to goal scores.    

![](https://docs.google.com/drawings/d/1P2srN6mcimxVgurWMVooFiI2kIgltz_q8e02FG296Ww/pub?w=1344&h=432)

----

<div class="col2">
![](https://docs.google.com/drawings/d/1O08iEoo3qxOZRoK6Ohv-jdouTBsN_kafJjIhEEqb-yg/pub?w=960&h=720)

<br>
**Goal scores are calculated by modeling data first as Present Status and Likely Future State.**  
Likely Future State is a combination of status, trend, pressures and resilience calculations, all of which require the best available data but ultimately contribute to goals scores unequally. Scroll down and click on a data set to access metadata and data processing information, or explore [the complete list of global data](http://ohi-science.org/ohi-global/layers.html), or [OHI+ goal approaches](http://ohi-science.org/goals).
<!--- TODO: link to supplement --->

</div>
----

```{r, child=sprintf('%s/conf/goals.Rmd', dir_scenario)}
```

----
<br>
<br>
[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)
