---
title: "Goals in global OHI assessments"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```

**Global Ocean Health Index assessments score 10 goals, some of which have sub-goals**.  
Here you will find information about how goals were represented, including how they are affected by pressures and resilience measures, and the underlying data and data processing.  

- [Explore a complete list of global data](http://ohi-science.org/ohi-global/layers.html)  
- [Explore OHI+ goal approaches](http://ohi-science.org/goals)
<!--- TODO: link to supplement --->

![](https://docs.google.com/drawings/d/e/2PACX-1vQr-cykqFsiuUZ-XuSv4qxL5FjztCNztfb98ryLg0hHDn3eU6e-febTqJuMARZAvH-eZNMig3484DC_/pub?w=1344&h=432)


```{r, child=sprintf('%s/conf/goals.Rmd', dir_scenario)}
```

----

**TO CONSIDER** (and see [SEASIDE CHAT NOTES](https://github.com/OHI-Science/issues/issues/665#issuecomment-261118749))

- remove layers page and instead list layers and links to data prep below the goals
- show Mel's pie chart
- [little icon figures!]
- Tiny figures showing relative contributions?
