---
title: "Goals in global OHI assessments"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```
 
<!---From http://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown:
Put in your css file or directly in rmarkdown--->
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>
 
**Global Ocean Health Index assessments score 10 goals, some of which have sub-goals**. Here you will find a description about how goals are represented in global assessments.   

![](https://docs.google.com/drawings/d/e/2PACX-1vQr-cykqFsiuUZ-XuSv4qxL5FjztCNztfb98ryLg0hHDn3eU6e-febTqJuMARZAvH-eZNMig3484DC_/pub?w=1344&h=432)

Scroll down and click on a data set to access metadata and data processing information. Goal-by-goal, you can explore the data used to model status and trend, as well as the pressures and resilience measures contributing to goal scores. Data are modeled, and contribute to goals scores unequally, as the figure below shows.

<div class="col2">
<br>
<br>
<br>
<br>
<br>

- [Explore the complete list of global data](http://ohi-science.org/ohi-global/layers.html)  
- [Explore OHI+ goal approaches](http://ohi-science.org/goals)
<!--- TODO: link to supplement --->

![](https://docs.google.com/drawings/d/1O08iEoo3qxOZRoK6Ohv-jdouTBsN_kafJjIhEEqb-yg/pub?w=960&h=720)

</div>
----

```{r, child=sprintf('%s/conf/goals.Rmd', dir_scenario)}
```

----
<br>
<br>
[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)
