---
title: "Goals"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```

**TO BE REDONE WITHOUT EQUATIONS, LIKE <http://ohi-science.org/bhi/goals>.** This has a separate .md file for each goal that is a knit-child here, as well as wherever else (in the prep files? or SOM perhaps?)  

[SEASIDE CHAT NOTES](https://github.com/OHI-Science/issues/issues/665#issuecomment-261118749)

- remove layers page and instead list layers and links to data prep below the goals
- show Mel's pie chart

```{r, child=sprintf('%s/conf/goals.Rmd', dir_scenario)}
```


Artisanal Opportunity [little icon figures!]

afjldkajfdl

Data sets: 

Status and Trend: 
- [Artisanal fisheries management effectiveness and opportunity](go to the layers.html#ao_need, where there's more description, info about gapfilling, whether it was updated in that year)
Accompanying text: The opportunity for artisanal and recreational fishing based on the quality of management of the small-scale fishing sector

Pressures: (be explicit about how this ties to goals)

Resilience: 

Tiny figures showing relative contributions

