---
title: "Goals in global OHI assessments"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
source("./_site.R")
```

<!---From http://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown:
Put in your css file or directly in rmarkdown--->
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>
 
<br> 
**Global Ocean Health Index assessments score 10 goals, some of which have sub-goals**. The Ocean Health Index measures the ability of oceans to sustainably provide 10 products or services (called "goals") that are important to humans. Here you will find a description of the goals used in global assessments. Goal-by-goal, you can explore the data used to model status and trend, as well as the pressures and resilience measures contributing to goal scores.     

![](https://docs.google.com/drawings/d/17N97_cydibY4QM79tnVf-hLDii0NNm3VhBJ2hhkKKkM/pub?w=1344&h=192)

----
<br>
<br>
<br>
<div class="col2">
![](https://docs.google.com/drawings/d/1O08iEoo3qxOZRoK6Ohv-jdouTBsN_kafJjIhEEqb-yg/pub?w=960&h=720)
<br>
<br>
<br>
<br>
<br>
**Goal scores are calculated by modeling data first as Present Status and Likely Future State.**  
Likely Future State is a combination of status, trend, pressures and resilience calculations, which unequally contribute to goal scores.  

Scroll down for a description of each goal as well as the model and data used to calculate the goal (blue text links to descriptions of the specific data used in the calculation of each goal).

A complete list of the data used in the calculations is [available](http://ohi-science.org/ohi-global/layers.html), and complete methods are also [available](http://ohi-science.org/ohi-global/downloads). You can also explore [OHI+ goal approaches](http://ohi-science.org/goals).

</div>
----

```{r, child="local_goals.Rmd"}
```

----
<br>
<br>
<!---[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  --->
[ohi-science.org home](http://ohi-science.org)
