---
title: "Goals in global OHI assessments"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```
 
**Global Ocean Health Index assessments score 10 goals, some of which have sub-goals**.  
Here you will find a description about how goals are represented in global assessments. Goal-by-goal, you can explore the data used to model status and trend, as well as the pressures and resilience measures contributing to goal scores. Click on a data set to access metadata and data processing information.  

- [Explore the complete list of global data](http://ohi-science.org/ohi-global/layers.html)  
- [Explore OHI+ goal approaches](http://ohi-science.org/goals)
<!--- TODO: link to supplement --->

![](https://docs.google.com/drawings/d/e/2PACX-1vQr-cykqFsiuUZ-XuSv4qxL5FjztCNztfb98ryLg0hHDn3eU6e-febTqJuMARZAvH-eZNMig3484DC_/pub?w=1344&h=432)

----

```{r, child=sprintf('%s/conf/goals.Rmd', dir_scenario)}
```

----
<br>
<br>
[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="100px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)
