---
title: "Five years of global OHI assessments"
output:
  html_document:
    fig_width: 1
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```

<!---From http://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown:
Put in your css file or directly in rmarkdown--->
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
</style>

<br>
2016 marks the fifth year of annual global Ocean Health Index (OHI) assessments, with scores representing ocean health for 220 coastal nations and territories.  

Completing the fifth consecutive year of the global ocean health assessment provided an opportunity to explore trends and trajectories in ocean health as well as assess how well the Ocean Health Index has performed as an indicator.  An Open Channels [webinar](https://www.openchannels.org/webinars/2017/drivers-and-implications-change-global-ocean-health-demonstrated-ocean-health-index) describes our conclusions from the 2016 assessment.    

----

<div class="col2">
```{r fig.width=5, fig.height=5,echo=FALSE}
library(png)
library(grid)
img <- readPNG(sprintf('%s/figures/FlowerPlots/flower_GLOBAL_2016.png', dir_report))
grid.raster(img)
```
<br>
<br>
<br>
<br>
<br>
<br>
**The average 2016 Index score was 71 out of 100**.  
Average Index scores have not dramatically changed over five years, which could be expected at a global scale. However, some individual goals and regions have had significant changes.   
<br> 

- [Learn about the goals](http://ohi-science.org/ohi-global/goals)    
- [Explore scores by region and goal](http://ohi-science.org/ohi-global/scores)    
- [Download data](http://ohi-science.org/ohi-global/download) 
- [Learn more at oceanhealthindex.org](http://www.oceanhealthindex.org/)
</div>

The OHI framework has not changed since its inception in 2012 ([*Halpern et al. 2012*](http://www.nature.com/nature/journal/v488/n7413/full/nature11397.html)). We continue to assess ocean health based on the sustainable delivery of 10 goals that are of importance to humans.  We score each goal on a scale of 0-100 based on current status, trend, and external pressures and resilience measures.  Scores are calculated for each coastal nation before being combined together. However, the OHI benefits from constant evaluation and improvement aimed at incorporating new knowledge, data and understanding, and underlying methods for some goals have been upgraded.  
For further information, see [*Halpern et al. 2015*](http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0117863) and [*Lowndes et al. 2015*](https://peerj.com/articles/1503).
<br>
<br>
[<img src="https://docs.google.com/drawings/d/1633uvIYgsBhiKBddQAaTlvYDJgOK1uiDB6wkooNyhFc/pub?w=576&h=288" width="150px">](http://ohi-science.org)  
[ohi-science.org home](http://ohi-science.org)

<!--- TODO:
Show a static map of 2016 scores instead of the regions. 

Explore more on the Data Explorer page
Download on the download page...
--->
