--- 
title: Layers descriptions 
output: 
  html_document: 
    toc: true 
    toc_depth: 1 
    number_sections: false 
    toc_float: yes 
---

```{r, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE} 
 library(dplyr) 
 library(tidyr) 
 library(knitr) 
 
 layer_meta <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/layers_eez_base.csv', stringsAsFactors = FALSE) 
 layer_path <- 'https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers' 
 
 
```

 
# Artisanal fisheries management effectiveness 
#### [fp_mora_artisanal](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_mora_artisanal.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_mora_artisanal.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Artisanal fisheries opportunity 
#### [ao_access](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/ao_access.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/ao_access.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Average species condition 
#### [spp_status](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/spp_status.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/spp_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 status score

 
# Average species condition trend 
#### [spp_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/spp_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/spp_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend score

 
# B/Bmsy estimates 
#### [fis_b_bmsy](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fis_b_bmsy.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fis_b_bmsy.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 B/Bmsy

 
# Blast fishing 
#### [np_blast](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/np_blast.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/np_blast.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Carbon storage weights 
#### [element_wts_cs_km2_x_storage](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/element_wts_cs_km2_x_storage.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/element_wts_cs_km2_x_storage.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 extent*carbon_storage

 
# Chemical pollution 
#### [po_chemicals](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_chemicals.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_chemicals.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Chemical pollution trend 
#### [cw_chemical_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cw_chemical_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cw_chemical_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# CITES signatories 
#### [g_cites](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/g_cites.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/g_cites.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 0 or 1

 
# Coastal chemical pollution 
#### [po_chemicals_3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_chemicals_3nm.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_chemicals_3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Coastal nutrient pollution 
#### [po_nutrients_3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_nutrients_3nm.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_nutrients_3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Coastal protected marine areas (fishing preservation) 
#### [fp_mpa_coast](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_mpa_coast.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_mpa_coast.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Coastal protected marine areas (habitat preservation) 
#### [hd_mpa_coast](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hd_mpa_coast.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hd_mpa_coast.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Coastal protection weights 
#### [element_wts_cp_km2_x_protection](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/element_wts_cp_km2_x_protection.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/element_wts_cp_km2_x_protection.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 extent*rank_protection

 
# Economic diversity 
#### [li_sector_evenness](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/li_sector_evenness.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/li_sector_evenness.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Economic need for artisanal fishing 
#### [ao_need](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/ao_need.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/ao_need.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Economic status scores 
#### [eco_status](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/eco_status.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/eco_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 status 0-100

 
# Economic trend scores 
#### [eco_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/eco_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/eco_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend -1 to 1

 
# EEZ protected marine areas (fishing preservation) 
#### [fp_mpa_eez](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_mpa_eez.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_mpa_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# EEZ protected marine areas (habitat preservation) 
#### [hd_mpa_eez](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hd_mpa_eez.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hd_mpa_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Fisheries management index 
#### [fp_fish_management](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_fish_management.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_fish_management.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Fishery catch data 
#### [fis_meancatch](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fis_meancatch.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fis_meancatch.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 tonnes

 
# Food provision weights 
#### [fp_wildcaught_weight](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_wildcaught_weight.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_wildcaught_weight.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Genetic escapes 
#### [sp_genetic](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/sp_genetic.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/sp_genetic.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Global Competitiveness Index (GCI) 
#### [li_gci](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/li_gci.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/li_gci.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Habitat condition of coral 
#### [hab_coral_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_coral_health.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_coral_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Habitat condition of mangrove 
#### [hab_mangrove_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_mangrove_health.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_mangrove_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Habitat condition of saltmarsh 
#### [hab_saltmarsh_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_saltmarsh_health.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_saltmarsh_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Habitat condition of seagrass 
#### [hab_seagrass_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_seagrass_health.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_seagrass_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Habitat condition of seaice 
#### [hab_seaice_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_seaice_health.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_seaice_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Habitat condition of softbottom 
#### [hab_softbottom_health](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_softbottom_health.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_softbottom_health.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Habitat condition trend of coral 
#### [hab_coral_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_coral_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_coral_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Habitat condition trend of mangrove 
#### [hab_mangrove_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_mangrove_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_mangrove_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Habitat condition trend of saltmarsh 
#### [hab_saltmarsh_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_saltmarsh_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_saltmarsh_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Habitat condition trend of seagrass 
#### [hab_seagrass_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_seagrass_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_seagrass_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Habitat condition trend of seaice 
#### [hab_seaice_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_seaice_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_seaice_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Habitat condition trend of softbottom 
#### [hab_softbottom_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_softbottom_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_softbottom_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Habitat extent of coral 
#### [hab_coral_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_coral_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_coral_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat extent of mangrove 
#### [hab_mangrove_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_mangrove_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_mangrove_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat extent of rocky reef 
#### [hab_rockyreef_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_rockyreef_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_rockyreef_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat extent of saltmarsh 
#### [hab_saltmarsh_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_saltmarsh_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_saltmarsh_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat extent of seagrass 
#### [hab_seagrass_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_seagrass_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_seagrass_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat extent of seaice 
#### [hab_seaice_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_seaice_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_seaice_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat extent of softbottom 
#### [hab_softbottom_extent](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hab_softbottom_extent.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hab_softbottom_extent.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Habitat presence/absence 
#### [element_wts_hab_pres_abs](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/element_wts_hab_pres_abs.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/element_wts_hab_pres_abs.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 0 or 1

 
# High bycatch due to artisanal fishing 
#### [fp_art_hb](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_art_hb.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_art_hb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# High bycatch due to commercial fishing 
#### [fp_com_hb](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_com_hb.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_com_hb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Inland 1km area 
#### [rgn_area_inland1km](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/rgn_area_inland1km.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/rgn_area_inland1km.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Inland coastal protected areas 
#### [lsp_prot_area_inland1km](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/lsp_prot_area_inland1km.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/lsp_prot_area_inland1km.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Intertidal habitat destruction 
#### [hd_intertidal](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hd_intertidal.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hd_intertidal.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# IUCN extinction risk 
#### [ico_spp_iucn_status](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/ico_spp_iucn_status.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/ico_spp_iucn_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 IUCN risk category

 
# Livelihood status scores 
#### [liv_status](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/liv_status.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/liv_status.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 status 0-100

 
# Livelihood trend scores 
#### [liv_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/liv_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/liv_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend -1 to 1

 
# Low bycatch due to artisanal fishing 
#### [fp_art_lb](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_art_lb.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_art_lb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Low bycatch due to commercial fishing 
#### [fp_com_lb](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_com_lb.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_com_lb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Management of habitat to protect fisheries biodiversity  
#### [fp_habitat](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_habitat.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_habitat.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Management of habitat to protect habitat biodiversity 
#### [hd_habitat](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hd_habitat.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hd_habitat.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Management of mariculture  to preserve biodiversity 
#### [g_mariculture](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/g_mariculture.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/g_mariculture.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Management of nonindigenous species 
#### [sp_alien_species](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/sp_alien_species.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/sp_alien_species.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Management of tourism to preserve biodiversity 
#### [g_tourism](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/g_tourism.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/g_tourism.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Management of waters to preserve biodiversity 
#### [po_water](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_water.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_water.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Mariculture harvest 
#### [mar_harvest_tonnes](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/mar_harvest_tonnes.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/mar_harvest_tonnes.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 tonnes

 
# Mariculture Sustainability Index 
#### [g_msi_gov](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/g_msi_gov.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/g_msi_gov.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Mariculture sustainability score 
#### [mar_sustainability_score](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/mar_sustainability_score.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/mar_sustainability_score.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Marine plastics 
#### [po_trash](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_trash.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_trash.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Measure of coastal ecological integrity 
#### [species_diversity_3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/species_diversity_3nm.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/species_diversity_3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Measure of ecological integrity 
#### [species_diversity_eez](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/species_diversity_eez.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/species_diversity_eez.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Natural product harvest 
#### [np_harvest_tonnes](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/np_harvest_tonnes.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/np_harvest_tonnes.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 tonnes

 
# Nonindigenous species 
#### [sp_alien](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/sp_alien.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/sp_alien.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Nutrient pollution 
#### [po_nutrients](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_nutrients.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_nutrients.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Nutrient pollution trend 
#### [cw_nutrient_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cw_nutrient_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cw_nutrient_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Ocean acidification 
#### [cc_acid](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cc_acid.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cc_acid.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Offshore 3nm area 
#### [rgn_area_offshore3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/rgn_area_offshore3nm.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/rgn_area_offshore3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Offshore coastal protected areas 
#### [lsp_prot_area_offshore3nm](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/lsp_prot_area_offshore3nm.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/lsp_prot_area_offshore3nm.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# OHI region id 
#### [rgn_global](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/rgn_global.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/rgn_global.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 label

 
# Pathogen pollution 
#### [po_pathogens](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/po_pathogens.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/po_pathogens.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Pathogen pollution trend 
#### [cw_pathogen_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cw_pathogen_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cw_pathogen_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Percent direct employment in tourism 
#### [tr_jobs_pct_tourism](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/tr_jobs_pct_tourism.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/tr_jobs_pct_tourism.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Plastic trash trends 
#### [cw_trash_trend](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cw_trash_trend.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cw_trash_trend.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 trend

 
# Poison fishing 
#### [np_cyanide](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/np_cyanide.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/np_cyanide.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Potential tonnes of mariculture harvest 
#### [mar_capacity](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/mar_capacity.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/mar_capacity.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 tonnes

 
# Region areas based on EEZ boundaries 
#### [rgn_area](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/rgn_area.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/rgn_area.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 km2

 
# Regions 
#### [rgn_labels](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/rgn_labels.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/rgn_labels.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 label

 
# Relative natural product harvest tonnes 
#### [np_harvest_tonnes_relative](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/np_harvest_tonnes_relative.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/np_harvest_tonnes_relative.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Relative natural product harvest value 
#### [np_harvest_product_weight](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/np_harvest_product_weight.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/np_harvest_product_weight.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 proportion

 
# Sea level rise 
#### [cc_slr](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cc_slr.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cc_slr.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Sea surface temperature 
#### [cc_sst](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cc_sst.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cc_sst.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Sectors in each region 
#### [le_sector_weight](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/le_sector_weight.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/le_sector_weight.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 value

 
# Social Progress Index 
#### [res_spi](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/res_spi.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/res_spi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Strength of governance 
#### [wgi_all](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/wgi_all.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/wgi_all.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Subtidal hardbottom habitat destruction 
#### [hd_subtidal_hb](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hd_subtidal_hb.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hd_subtidal_hb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Subtidal soft bottom habitat destruction 
#### [hd_subtidal_sb](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/hd_subtidal_sb.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/hd_subtidal_sb.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Targeted harvest of cetaceans and marine turtles 
#### [fp_targetharvest](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/fp_targetharvest.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/fp_targetharvest.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Tourism sustainability index 
#### [tr_sustainability](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/tr_sustainability.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/tr_sustainability.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Uninhabited regions 
#### [uninhabited](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/uninhabited.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/uninhabited.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 population

 
# US State Department travel warnings 
#### [tr_travelwarnings](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/tr_travelwarnings.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/tr_travelwarnings.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# UV radiation 
#### [cc_uv](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/cc_uv.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/cc_uv.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Weakness of governance 
#### [ss_wgi](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/ss_wgi.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/ss_wgi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1

 
# Weakness of social progress 
#### [ss_spi](https://github.com/OHI-Science/ohi-global/tree/draft/eez/layers/ss_spi.csv) {-} 
```{r, echo=FALSE, results='hide'}

                                  x <- tempfile(fileext = 'Rmd')

                                 on.exit(unlink(x))

                                 download.file("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/metadata_documentation/ohi_model/layers_info/ss_spi.Rmd", x)
```
 
```{r, child = x, echo=FALSE, results='asis'} 
 
``` 
 
#### Units {-} 
 scaled 0-1
