---
title: "Global Assessments"
---

```{r setup, echo=F, warning=FALSE, message=F}
source("./_site.R")
```


BACKGROUND ABOUT 5 ASSESSMENTS, WHAT CHANGED, ETC


Regions are the fundamental spatial units of analysis for the Ocean Health Index. Scores are calculated for each region individually and then combined (with an offshore area-weighted average) to produce scores for the entire study area, `r study_area`. These template regions can be modified with some effort. They were identified as the largest subcountry division within `r study_area`.

Show a static map of 2016 scores instead of the regions 


```{r}
if (!'geojson' %in% names(config)) stop(sprintf('Missing geojson path variable in %s/conf/config.R', dir_scenario))
geojson = normalizePath(file.path(dir_scenario, config$geojson))

# read spatial (can simplify with R package rmapshaper)
if (!file.exists(geojson)) stop(sprintf('GeoJSON file specified in %s/conf/config.R not found: %s', dir_scenario, geojson))
cat(file=stderr(), 'read rgns from geojson\n')
rgns = geojsonio::geojson_read(geojson, what="sp")
if ('rgn_nam' %in% names(rgns@data) & !'rgn_name' %in% names(rgns@data)) rgns@data = rgns@data %>% mutate(rgn_name = rgn_nam)

# get bbox to shrink
bbox_shrink = function(p, pct){
  b = bbox(p)
  dx = (b[3] - b[1]) * (pct/100)
  dy = (b[4] - b[2]) * (pct/100)
  c(b[1] + dx, b[2] + dy, b[3] - dx, b[4] - dy)
}
b = bbox_shrink(rgns, map_shrink_pct)

leaflet() %>%
  addProviderTiles('Stamen.TonerLite') %>%
  addPolygons(
    data = rgns, 
    layerId = ~rgn_id,
    label = mapply(function(n) {
      HTML(sprintf("<em>%s</em>", htmlEscape(n)))},
      rgns$rgn_name, SIMPLIFY = F),
    stroke = TRUE, opacity=0.5, weight=2, fillOpacity = 0.5, smoothFactor = 0.5,
    color = ~colorNumeric('RdYlBu', rgns$rgn_id)(rgn_id)) %>%
  fitBounds(lng1 = b[1], lat1 = b[2], lng2 = b[3], lat2 = b[4]) %>%
  htmlwidgets::onRender("
  function(el, t) {
    var defaultStyle = {
      // stroke, ie polygon border
        opacity:     0.5,
        weight:      2,
      // fill, ie polygon interior
        fillOpacity: 0.5,
    };
    var highlightStyle = {
      // stroke, ie polygon border
        opacity:     0.9,
        weight:      6,
      // fill, ie polygon interior
        fillOpacity: 0.9,
    };

    var myMap = this;
    var layers = myMap._layers;
    for(var i in layers) {
      var layer = layers[i];
      if(layer.label) {
        layer.on('mouseover',
          function(e) {
            this.setStyle(highlightStyle);
            // this.bringToFront();
        });
        layer.on('mouseout',
          function(e) {
            this.setStyle(defaultStyle);
            // this.bringToBack();
        });
      }
    }
  }")
```



IDs for subcountry regions were assigned geographically by increasing longitude. The entire study area `r study_area` has a special region ID of 0.

Exclusive economic zones (EEZs) were identified by [MarineRegions.org](http://www.marineregions.org) and the largest subcountry regions were identified by the generalized administrative boundary database [GADM.org](http://www.gadm.org). Region boundaries were extended offshore to divide the EEZ of `r study_area` into offshore regions. It is possible to use different regions than the ones provided here. See [Create Regions](http://ohi-science.org/pages/create_regions.html) for more details.

