### Mariculture (subgoal of food provision)

The mariculture subgoal attempts to measure each region's food production from mariculture relative to its capacity. A basic problem facing assessments of mariculture is the lack of an ecologically- and socially-based reference point for the potential yield of every suitable mariculture species for every type of geographic habitat and location. Determining such reference points for every country at the global scale is a daunting challenge, not only because so much information is lacking, but also because species, genotypes and habitats are likely to change. Consequently, the reference point is based on a comparison of country performance of the harvested tonnes per coastal inhabitant. 


#### Current status
The status of the mariculture subgoal, $x_{mar}$, was defined as production of strictly marine taxa from both the marine and brackish water FAO categories, excluding species that were not used as a source of food for human consumption. The data reported by FAO does not always clearly describe whether harvest is derived through mariculture or from land-based facilities. Wherever possible, we excluded species that could not have been harvested from coastal waters, such as freshwater cyclids. Mariculture status was therefore assessed as the current sustainably-harvested yield, $Y_{c}$, within each country, such that:

$$
x_{mar}= \frac {Y_c}{Y_{c, ref}},   (Eq. 5.10)
$$
where, $Y_{c,ref}$ is the $Y_c$ value that corresponds to the 95th quantile across all regions and years (including and prior to the year of the assessment year data), and $Y_c$ is: 

$$
Y_{c}  = \frac { \displaystyle\sum _{ k=1 }^{ N }{ { Y }_{ k }{ S }_{ k,r } }  }{ { P }_{ r } }, (Eq. 5.11)
$$


where, $Y_{k}$ is the 4-year moving window average of tonnes of production [@united_nations_fao_2016] for each ${k}$ mariculture species that is currently or at one time cultured within a country, $S_{k,r}$ is the sustainability score for each $k$ mariculture species and region, and $P_{r}$ is the population within 25 miles of the region's coast.

Sustainable harvest data is adjusted for coastal population within a country given the assumption that production depends on the presence of coastal communities that can provide the labor force, infrastructures, and economic demand to support the development and economic viability of mariculture facilities. Thus, two regions with an equal number of coastal inhabitants harvesting an equal tonnage of cultured seafood will score the same, as productivity is commensurate to each region’s socio-economic potential to develop mariculture. Stated another way, mariculture development is assumed to scale proportionally with coastal population, which is a proxy for potential logistic limitations to farm development, e.g., presence of infrastructures, coastal access, and locally available workforce. 

The reference point was the $Y_c$ value of the region scoring in 95th percentile across all years of data, with all regions scoring above that value given a status score of 1.0.

The sustainability score, $S_{k,r}$, for each species in each region is based on the Mariculture Sustainability Index (MSI, -@summerson_recruitment_1990). We used the three sub-indices that directly measured long-term renewability of a given mariculture practice: the wastewater treatment index, the origin of feed index (i.e., fishmeal or other) and the origin of seed (i.e., hatchery or wild caught). These scores are country and species-specific, and we require each species’ yield, $Y_{k}$, to have a corresponding sustainability score, $S_{k,r}$. However, if a country farms a species that was not assessed by the MSI for that country, but it was assessed in other countries, a global average score is used for that species and country. If a country farms a species that was not assessed at all by the MSI but a species within the same genus was assessed, a global average for the genus was used. Finally, if these scores were not available for the categories above, we used the global average for broad taxonomic grouping (e.g., crustaceans, algae, bivalves, etc.). We are aware that there is some bias associated with using scores derived as averages across countries because they were originally assigned to specific species-country pairs, nevertheless this is preferable to applying a sustainability score solely based on a subset of the species harvested.

#### Trend
Trend was calculated as described in section 4.3.1.

#### Data
_Status and trend_

```{r MAR data st, results="asis", echo=FALSE}
data_layers(goal="MAR", dimension=c("status", "trend"))
```

_Pressure_

```{r MAR data p, results="asis", echo=FALSE}
data_layers(goal="MAR", dimension=c("pressure"))
```

_Resilience_

```{r MAR r, results="asis", echo=FALSE}
data_layers(goal="MAR", dimension=c("resilience"))

```
