---
title: 'OHI 2016 Supplement: results'
author: "*Compiled on `r date()` by `r Sys.info()['user']`*"
output: 
  html_document:
    code_folding: show
    toc: true
    toc_depth: 3
    toc_float: yes
    number_sections: false
    theme: cerulean
    highlight: haddock
    includes: 
      in_header: '../../../ohiprep/src/templates/ohi_hdr.html'
  pdf_document:
    toc: true
---


```{r data set up, include=FALSE}

#load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(hwriter)
library(RColorBrewer)
library(knitr)
library(googleVis)
library(ohicore)
library(sp)
library(rgdal)
library(DT)
library(broom)
library(nlme)

# Set working directory when not knitting:
# setwd("global2016/Reporting")

goals <- c('Index', 'AO', 'SPP', 'BD', 'HAB', 'CP', 'CS', 'CW', 'ECO', 'LE', 'LIV', 'FIS', 'FP', 'MAR', 'ICO', 'SP', 'LSP', 'NP', 'TR')
goal_names <- data.frame(goal=goals, long_goal=c("Index", 
                                                  "Artisanal opportunities",
                                                  "Species condition\n(Biodiversity)",
                                                  "Biodiversity",
                                                  "Habitat\n(Biodiversity)",
                                                  "Coastal protection",
                                                  "Carbon storage",
                                                  "Clean water",
                                                  "Economies",
                                                  "Livelihoods & economies",
                                                  "Livelihoods",
                                                  "Fisheries\n(Food provisioning)",
                                                  "Food provisioning",
                                                  "Mariculture\n(Food provisioning)",
                                                  "Iconic species\nSense of place)",
                                                  "Sense of place",
                                                  "Lasting special places\n(Sense of place)",
                                                  "Natural products",
                                                  "Tourism & recreation"))

## General settings to control
scenario <- "2016" #identify scenario of focus (this can be changed to obtain data for other years)
benchmark = 2015  # year that is used for old vs. new OHI analyses
oldCommit = '1d4dcb1abb82dc1d20817acca33c7e7d2ef1b52f' # '4da6b4a1d69d694264ea68456359a939b0c03f9c' = commit for 2014 analysis
colorScheme <- 'new'  # color scheme to use on flower plots ("new" = color reflects size score and is not the original rainbow)
saveFile <- 'global2016' #location where files that are created are to be saved

## General files to load
rgn_names <- read.csv(sprintf('../../eez%s/layers/rgn_global.csv', scenario)) %>%
  dplyr::select(region_id = rgn_id, country = label) %>%
  dplyr::mutate(country = as.character(country))

rgn_names$country[rgn_names$region_id == 212] <- "Gilbert Islands (Kiribati)"
rgn_names$country[rgn_names$region_id == 148] <- "Line Islands (Kiribati)"
rgn_names$country[rgn_names$region_id == 157] <- "Phoenix Islands (Kiribati)"


radicalFile = '2016-11-17' #date extension on the radical data files that are used for all tables/figures

```

### Trend vs scores
(figure out which regions to label)

```{r trend vs score}

index <- read.csv("data/scores_eez2016.csv") %>%
  select(region_id, country, Index)

vaxis <- index$Index[index$region_id==0]

trend <- read.csv(sprintf("data/trends_%s.csv", scenario)) %>%
  select(region_id, index_trend = Index) %>%
  left_join(index, by= "region_id") %>%
  filter(region_id != 0)


  p <- ggplot2::ggplot(trend, aes(x=Index, y=index_trend)) +
    geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=2, color="gray", alpha = 0.5) +
    geom_hline(yintercept = 0, color="red", size=.5, linetype=3) +
    geom_vline(xintercept = vaxis, color="red", size=.5, linetype=3) +
    theme_bw() + 
    labs(y="Trend (change OHI per year)", x="OHI score (2016)") 

plot(p)   
ggsave("figures/trend vs score.jpg")

  plotly_fig <- plotly::ggplotly(p)
  plotly_fig
  
### adding labels
  labels1 <- c("Bosnia and Herzegovina", "Vietnam", "Philippines",
              "Eritrea", "Equatorial Guinea", "Nicaragua", "Republique du Congo", "Turkey", "Somalia", "Costa Rica",
          "Glorioso Islands", "American Samoa", "Croatia",
              "Estonia", "New Zealand", "Bahamas")
  
  labels2 <- c("South Georgia and the South Sandwich Islands")
  
setdiff(labels1, trend$country)

trend <- trend %>%
  mutate(label1 = ifelse(country %in% labels1, as.character(country), NA)) %>%
  mutate(label2 = ifelse(country %in% labels2, as.character(country), NA)) 
  

  p <- ggplot2::ggplot(trend, aes(x=Index, y=index_trend)) +
    geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=2, color="gray", alpha = 0.5) +
    geom_text(aes(label=label1), hjust=0, nudge_x=0.4, size=2.7) + 
    geom_text(aes(label=label2), vjust=0, nudge_y=0.1, nudge_x=-5, size=2.7) + 
    geom_hline(yintercept = 0, color="red", size=.5, linetype=3) +
    geom_vline(xintercept = vaxis, color="red", size=.5, linetype=3) +
    theme_bw() + 
    labs(y="Trend (change OHI per year)", x="OHI score (2016)") 

plot(p)   
ggsave("figures/trend vs score.jpg")

```

### Comparison of ranks

```{r rank analysis}

index_2016 <- read.csv("data/scores_eez2016.csv") %>%
  select(region_id, country, index2016 = Index) %>%
  filter(region_id != 0) %>%
  arrange(index2016) %>%
  mutate(rank_2016 = min_rank(desc(index2016)))

index_2012 <- read.csv("data/scores_eez2012.csv") %>%
  select(region_id, country, index2012 = Index) %>%
  filter(region_id != 0) %>%
  arrange(index2012) %>%
  mutate(rank_2012 = min_rank(desc(index2012))) %>%
  left_join(index_2016, by=c("region_id", "country")) %>%
  mutate(index_delta = index2016 - index2012) %>%
  mutate(rank_delta = rank_2016 - rank_2012)
  

## compare 2012 vs 2016 ranks
  p <- ggplot2::ggplot(index_2012, aes(x=rank_2012, y=rank_2016)) +
    geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=2, color="gray", alpha = 0.5) +
    theme_bw()  + 
    geom_abline(slope = 1, intercept=0, color="red", size=0.5) + 
    labs(y="2016 rank of OHI scores", x="2012 rank of OHI scores") 

plot(p)   
ggsave("figures/ranks_2012_2016.jpg")

  plotly_fig <- plotly::ggplotly(p)
  plotly_fig

## compare change in ranks vs change in scores
  p <- ggplot2::ggplot(index_2012, aes(x= index_delta, y=rank_delta)) +
    geom_point(aes(text=paste0("rgn = ", country)), shape=19, size=2, color="gray", alpha = 0.5) +
    theme_bw()  + 
   labs(y="change in rank (2016-2012)", x="change in score (2016-2012)") 

plot(p)   
ggsave("figures/delta_ranks_scores.jpg")

  plotly_fig <- plotly::ggplotly(p)
  plotly_fig

```

## pairwise comparison of goal scores
```{r pairwise comparisons}
index_2016 <- read.csv("data/scores_eez2016.csv") %>%
  filter(region_id != 0) %>%
  select(-c(country, region_id)) %>%
  select(-c(SPP, HAB, ECO, LIV, FIS, MAR, ICO, LSP, Index))

panel.cor <- function(x, y, digits=2, prefix="", cex.cor, ...){
  usr <- par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  r <- abs(cor(x, y, use="na.or.complete"))
  txt <- format(c(r, 0.123456789), digits=digits)[1]
  txt <- paste(prefix, txt, sep="")
  if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
  text(0.5, 0.5, txt, cex = (cex.cor * r + .15)*3)
}

pairs(index_2016,
      lower.panel=panel.smooth, upper.panel=panel.cor, 
      pch=16, cex=.5)
## export as png with 700 x 700 dimensions



#seeing ones were significant
# panel.cor <- function(x, y, digits=2, prefix="", cex.cor) 
# {
#   usr <- par("usr"); on.exit(par(usr)) 
#   par(usr = c(0, 1, 0, 1)) 
#   r <- abs(cor(x, y)) 
#   txt <- format(c(r, 0.123456789), digits=digits)[1] 
#   txt <- paste(prefix, txt, sep="") 
#   if(missing(cex.cor)) cex <- 0.8/strwidth(txt) 
#   
#   test <- cor.test(x,y) 
#   # borrowed from printCoefmat
#   Signif <- symnum(test$p.value, corr = FALSE, na = FALSE, 
#                    cutpoints = c(0, 0.001, 0.01, 0.05, 0.1, 1),
#                    symbols = c("***", "**", "*", ".", " ")) 
#   
#   text(0.5, 0.5, txt, cex = cex * r) 
#   text(.8, .8, Signif, cex=cex, col=2) 
# }
# pairs(index_2016,
#       lower.panel=panel.smooth, upper.panel=panel.cor)


```

### Carpet plot of trends

```{r carpplot trend}

data <- read.csv(sprintf('../radical_%s.csv', radicalFile)) 

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  %>%
  mutate(value = round(value, 0)) %>%
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(country = ifelse(is.na(country), "eez_weighted_avg", as.character(country))) %>%
  group_by(region_id) %>% 
  mutate(meanIndex=mean(value[goal=="Index"])) %>%
  ungroup() %>%
  data.frame()
  

trends <- read.csv(sprintf("data/trends_%s.csv", scenario)) %>%
  gather(goal, "value", -(1:2)) %>%
  select(-region_id, region = country) %>%
  filter(region != "eez_weighted_avg")

region_order <- trends %>%
  filter(goal=="Index") %>%
  arrange(value)

values <-   brewer.pal(11, "RdYlBu")
col.values <- colorRampPalette(values, space = 'Lab')(12)
col.brks  <- c(-100, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 100)

trends$goal <- factor(trends$goal, levels = goals)
trends$region <- factor(trends$region, levels=region_order$region)
trends$trend_category <- cut(trends$value, breaks = col.brks)
  

p <- ggplot(trends, aes(y=region, x=goal, fill=trend_category)) +   
  geom_tile(aes(text = paste0("trend = ", value))) +
  scale_fill_manual(values = col.values, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5)) +
  ylab("") + 
  xlab("") +
  theme_bw()
plot(p)

ggsave("figures/trend_heatplot.png", width = 20, height=25, units="in")
ggplotly(p)

```


### Scores vs. population, HDI, and CHI

```{r pop hdi chi}

index <- read.csv("data/scores_eez2016.csv") %>%
  select(rgn_id = region_id, country, Index) %>%
  filter(rgn_id != 0) 

hdi <- read.csv("../../../ohiprep/globalprep/supplementary_information/v2016/HDI_data.csv") %>%
  select(rgn_id, hdi=value)

# coastal population
pop <- read.csv("../../../ohiprep/globalprep/mar_prs_population/v2016/output/mar_pop_25mi.csv") %>%
  filter(year == 2015) %>%
  select(rgn_id, coastal_pop = popsum) %>%
  mutate(log_coastal_pop = log(coastal_pop + 1))

## chi data
chi <- read.csv("../../../ohiprep/globalprep/supplementary_information/v2016/CHI_data.csv") %>%
  filter(sp_type == "eez") %>%
  select(rgn_id, chi=mean)


data <- index %>%
  left_join(pop, by="rgn_id") %>%
  left_join(chi, by="rgn_id") %>%
  left_join(hdi, by="rgn_id")

data_noNA <- na.omit(data)

mod1 <- lm(Index ~ chi, data=data_noNA)
summary(mod1)
mod2 <- lm(Index ~ hdi, data=data_noNA)
summary(mod2)
mod3 <- lm(Index ~ log_coastal_pop, data=data_noNA)
summary(mod3)
mod4 <- lm(Index ~ chi + hdi, data=data_noNA)
summary(mod4)
mod5 <- lm(Index ~ log_coastal_pop + hdi, data=data_noNA)
summary(mod5)
mod6 <- lm(Index ~ log_coastal_pop + chi, data=data_noNA)
summary(mod6)
mod7 <- lm(Index ~ log_coastal_pop + chi + hdi, data=data_noNA)
summary(mod7)

AIC(mod1, mod2, mod3, mod4, mod5, mod6, mod7)

mod8 <- lm(chi ~ log_coastal_pop, data=data)
summary(mod8)

mod9 <- lm(hdi ~ log_coastal_pop, data=data)
summary(mod9)

p <- ggplot2::ggplot(data, aes(y=Index, x=hdi)) +
    geom_point(shape=19, size=2, color="gray", alpha = 0.5) +
    theme_bw()  + 
    stat_smooth(method=lm, se=FALSE, color="black", size = 0.5)+
    labs(y="Human Development Index", x="OHI index score") 

plot(p)   
ggsave("figures/OHIvsHDI.png", height=4, width=4.5)

p <- ggplot2::ggplot(data, aes(y=Index, x=chi)) +
    geom_point(shape=19, size=2, color="gray", alpha = 0.5) +
    theme_bw()  + 
    stat_smooth(method=lm, se=FALSE, color="black", size = 0.5)+
    labs(y="Cumulative Human Impact", x="OHI index score") 

plot(p)   
ggsave("figures/OHIvsCHI.png", height=4, width=4.5)

p <- ggplot2::ggplot(data, aes(y=Index, x=log_coastal_pop)) +
    geom_point(shape=19, size=2, color="gray", alpha = 0.5) +
    theme_bw()  + 
    stat_smooth(method=lm, se=FALSE, color="black", size = 0.5)+
    labs(y="Coastal population (ln)", x="OHI index score") 

plot(p)   
ggsave("figures/OHIvsCoastalPop.png", height=4, width=4.5)

p <- ggplot2::ggplot(data, aes(x=chi, y=log_coastal_pop)) +
    geom_point(shape=19, size=2, color="gray", alpha = 0.5) +
    theme_bw()  + 
    stat_smooth(method=lm, se=FALSE, color="black", size = 0.5)+
    labs(y="Coastal population (ln)", x="Cumulative Human Impact") 

plot(p)   
ggsave("figures/CHIvsCoastalPop.png", height=4, width=4.5)


```


### Trend analysis
```{r trend analysis}
### prepare data:
data <- read.csv(sprintf('../radical_%s.csv', radicalFile)) 

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213) %>%
  filter(!is.na(value))

```

```{r trend calcs}
## Analysis of overall region index scores

data_lm <- data %>%
  group_by(goal, region_id) %>%
  do(mdl = lm(value ~ scenario, data = .))

#data.frame(glance(data_lm, mdl))
results_lm <- tidy(data_lm, mdl) %>%
  ungroup() %>%
  filter(term == "scenario") %>%
  arrange(goal, estimate) %>%
  left_join(goal_names) %>%
  left_join(rgn_names) %>%
  select(goal=goal, goal_long=long_goal, region_name = country, region_id, average_change_per_year = estimate, p.value) %>%
  data.frame()

weights <- read.csv("../../eez2016/layers/rgn_area.csv") %>%
  select(region_id=rgn_id, area_km2)

results_lm <- results_lm %>%
  left_join(weights, by="region_id")

summary_lm <- results_lm %>%
  group_by(goal, goal_long) %>%
  summarize(mean=mean(average_change_per_year),
            mean_wt=weighted.mean(average_change_per_year, w=area_km2))

g <- ggplot(filter(results_lm, goal == "Index"), aes(x=average_change_per_year)) +
  geom_histogram(color = "gray", fill="gray") +
  labs(y="Number of regions", x="Trend (avg. change in score per year)") + 
  geom_vline(xintercept=0, color="red") + 
  theme_bw()

plot(g)

# color coded histogram


# trends_hist <- trends %>%
#   filter(goal=="Index") %>%
#   filter(region_id != 0) %>%
#   arrange(trend)
# 
# values <-   brewer.pal(11, "RdYlBu")
# values <- colorRampPalette(values, space = 'Lab')(13)[2:13]
# col.brks  <- c(-100, -5, -4, -3, -2, -1, 0, 1, 2, 3, 4, 5, 100)
# 
# trends_hist$colors <- cut(trends_hist$trend, breaks=col.brks, include.lowest=TRUE, labels=values)
# cols <- as.character(unique(trends_hist$colors))
# 
# 
# g <- ggplot(trends_hist, aes(x=trend)) +
# geom_histogram(aes(fill=colors), bins=25, center=1.01, col="gray") +
# scale_fill_manual("", breaks=colors, values=cols, guide=FALSE) +
# labs(y="Number of regions", x="Index scores: 5 year trend") + 
# geom_vline(xintercept=0, color="red") +  
# theme_bw()
# 
# print(g)
# 
# ggsave("figures/trend_histogram_color.png", width=5, height=4)
# 

```

## Comparing random effect models
The following analyses indicate that adding the region as a random effect is a good idea, according to AIC.

```{r model check}

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="Index"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="Index"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="AO"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="AO"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="BD"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="BD"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)


model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="CP"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="CP"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)


model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="CS"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="CS"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)


model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="CW"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="CW"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="FIS"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="FIS"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="FP"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="FP"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="HAB"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="HAB"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)


model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="ICO"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="ICO"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="MAR"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="MAR"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)


model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="LSP"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="LSP"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="NP"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="NP"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="SP"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="SP"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="SPP"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="SPP"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

model0 <- gls(value ~ 1 + scenario,  data = filter(data, goal=="TR"), method="REML")
model1 <- lme(value ~ 1 + scenario, random = ~1 | region_id, data = filter(data, goal=="TR"), method="REML")
# ctrl <- lmeControl(opt='optim')
# model2 <- lme(value ~ 1 + scenario, random = ~1 + scenario | region_id, data = filter(data, goal=="Index"), 
#               method="REML", control=ctrl)
AIC(model0, model1)
summary(model1)

```

### Random effects model for global trend patterns (data for figure)

```{r trend calcs}
## Analysis of overall region index scores

nlme_results <- data.frame(goal=goals, trend=NA, p_value=NA)

for(goal in goals){ # goal = "AO"
  mod_data <- data[data$goal == goal, ]
  mdl = lme(value ~ 1 + scenario, random = ~1 | region_id, data = mod_data, method="REML")
  nlme_results$trend[nlme_results$goal == goal] <- mdl$coefficients$fixed[2]
  nlme_results$p_value[nlme_results$goal==goal] <- summary(mdl)$tTable[2,"p-value"]
}

results_lm_summary <- results_lm %>%
  group_by(goal, goal_long) %>%
  summarize(quant_5 = quantile(average_change_per_year, c(0.05)),
            quant_95 = quantile(average_change_per_year, c(0.95)))


nlme_results <- nlme_results %>%
  left_join(results_lm_summary, by="goal") %>%
  arrange(trend) %>%
  mutate(sig = ifelse(p_value < 0.05, "1", "0")) 

### nlme model with eez area weights
eez_area <- read.csv("../../eez2016/layers/rgn_area.csv") %>%
  select(region_id=rgn_id, area_km2) %>%
  mutate(region_id = as.character(region_id))

data_wts <- data %>%
  mutate(region_id = as.character(region_id)) %>%
  left_join(eez_area, by="region_id")

nlme_results_wts <- data.frame(goal=goals, trend_wts=NA, p_value_wts=NA)

for(goal in goals){ # goal = "AO"
  mod_data <- data_wts[data_wts$goal == goal, ]
  mdl = lme(value ~ 1 + scenario, random = ~1 | region_id, data = mod_data, method="REML", weights=~1/area_km2)
  nlme_results_wts$trend_wts[nlme_results_wts$goal == goal] <- mdl$coefficients$fixed[2]
  nlme_results_wts$p_value_wts[nlme_results_wts$goal==goal] <- summary(mdl)$tTable[2,"p-value"]
}

nlme_results <- nlme_results %>%
  left_join(nlme_results_wts, by="goal") %>%
  arrange(trend) %>%
  mutate(sig_wts = ifelse(p_value_wts < 0.05, "1", "0")) %>%
  left_join(goal_names) %>%
  mutate(goal_long = as.factor(long_goal))


## plot the data:

ggplot(filter(nlme_results, !(goal %in% c("ECO","LIV", "LE"))), 
       aes(x=trend, y=reorder(goal_long, trend))) +
  geom_point(size=3, color="#313695") +
  theme_bw() +
  geom_vline(xintercept = 0, color="red", linetype=3) + 
  labs(y="", x="trend (average change in score per year)") +
#  scale_colour_manual(values = c("#313695", "grey80"), limits=c(1, 0), guide=FALSE) +
  theme(axis.text.y = element_text(angle=0, hjust=1),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_line(color="grey60", linetype="dashed")) + 
  geom_point(data=filter(nlme_results, !(goal %in% c("ECO","LIV", "LE"))), 
       aes(x=trend_wts, y=goal_long), size=3, color="orange")



## another plot of the data
order_goal <- filter(nlme_results, !(goal %in% c("ECO","LIV", "LE"))) %>%
  arrange(-trend)

data_trend <- data %>%
  group_by(scenario, goal, dimension) %>%
  summarize(min_score = min(value, na.rm=TRUE),
            max_score = max(value, na.rm=TRUE),
            mean_score = mean(value, na.rm=TRUE)) %>%
  ungroup() %>%
  mutate(goal = factor(goal, levels=order_goal$goal)) %>%
  filter(!is.na(goal))


ggplot(data_trend, aes(x=scenario, y=mean_score)) +
  geom_line() + 
  facet_grid(goal ~ ., scales="free") + 
  theme_bw() +
    theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        strip.text.y = element_text(size = 8, angle = 0))
  
ggsave("figures/scores_scenario_grid.png", height=6, width=2)

```

```{r save model results}

nlme_table <- nlme_results %>%
  select(goal, trend, p_value, quant_5, quant_95)

write.csv(nlme_table, "data/nlme_results_goal_summary.csv", row.names=FALSE)

```

