---
title: "ESM 270 Ocean Health Index Lab"
output: html_document
---

# Introduction

The Ocean Health Index (OHI) framework measures health of coupled human-ocean ecosystems in different contexts by accommodating differences in local environmental characteristics, cultural priorities, and information availability and quality. The OHI framework assesses a suite of benefits the ocean provides humans using the best available information. It distills complex socio-ecological relationships and context-specific targets into scores that can be repeated so that management can track and respond through time. 

In this assignment you will explore how Ocean Health Index (OHI) scores would respond to 1) changing how goals are weighted, and 2) changing the reference point of a goal. You will be using the OHI Toolbox software


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, root.dir = 'eez2015')
```

# Install the OHI package `ohicore`

Run the following code to install the OHI package `ohicore`. 

If you have any problems, check that R and RStudio are up-to-date. The most recent version of R is 3.3 and RStudio is 0.99. If needed, update R [here](Find the latest version at http://cran.r-project.org) and RStudio [here](http://www.rstudio.com/products/rstudio/download). 

```{r install ohicore}

# remove old packages
for (p in c('ohicore', 'ohigui', 'rCharts')){
  if (p %in% rownames(installed.packages())){
    lib = subset(as.data.frame(installed.packages()), Package==p, LibPath, drop=T)
    remove.packages(p, lib)
  }
}

# install dependencies
for (p in c('devtools', 'zoo', 'psych', 'tidyr')){
  if (!require(p, character.only=T)){
    install.packages(p)
    require(p, character.only=T)
  }
}

# install packages
install_github('ohi-science/rCharts')
install_github('ohi-science/ohicore')
library(ohicore)

```

# Work within the repo


```{r tailored repo}

# our working directory is ohi-global. 
setwd('eez2015')
source('calculate_scores.r')

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
