---
output: html_document
---

```{r set up, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(dplyr)
library(tidyr)

# data with information
layers <- read.csv("../../../eez_layers_meta_data/layers_eez_base.csv")
targets <- read.csv("../../../eez_layers_meta_data/layers_eez_targets.csv")
layers_web <- "http://ohi-science.org/ohi-global/layers.html"
# setwd('eez2016/conf/')
```


## Food Provision: Fisheries

```{r, child='../../../global_supplement/goal_descriptions_short/FIS.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="FIS", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
  mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="FIS", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="FIS", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

---- 

## Food Provision: Mariculture

```{r, child='../../../global_supplement/goal_descriptions_short/MAR.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="MAR", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="MAR", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="MAR", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Artisanal Fishing Opportunity 

```{r, child='../../../global_supplement/goal_descriptions_short/AO.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="AO", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="AO", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="AO", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

---- 

## Natural Products

```{r, child='../../../global_supplement/goal_descriptions_short/NP.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="NP", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="NP", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="NP", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Carbon Storage

```{r, child='../../../global_supplement/goal_descriptions_short/CS.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CS", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CS", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CS", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Coastal Protection

```{r, child='../../../global_supplement/goal_descriptions_short/CP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CP", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CP", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CP", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Tourism & Recreation

```{r, child='../../../global_supplement/goal_descriptions_short/TR.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="TR", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="TR", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="TR", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Livelihoods & Economies: Livelihoods

```{r, child='../../../global_supplement/goal_descriptions_short/LIV.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="LIV", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="LIV", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="LIV", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

---- 

## Livelihoods & Economies: Economies

```{r, child='../../../global_supplement/goal_descriptions_short/ECO.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="ECO", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="ECO", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="ECO", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

---- 

## Sense of Place: Iconic Species

```{r, child='../../../global_supplement/goal_descriptions_short/ICO.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="ICO", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="ICO", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="ICO", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

---- 

## Sense of Place: Lasting Special Places

```{r, child='../../../global_supplement/goal_descriptions_short/LSP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="LSP", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="LSP", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="LSP", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Clean Waters

```{r, child='../../../global_supplement/goal_descriptions_short/CW.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CW", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CW", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="CW", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


---- 

## Biodiversity: Species

```{r, child='../../../global_supplement/goal_descriptions_short/SPP.Rmd', results='asis', echo=FALSE}
```


### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="SPP", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="SPP", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="SPP", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

---- 

## Biodiversity: Habitats

```{r, child='../../../global_supplement/goal_descriptions_short/HAB.Rmd', results='asis', echo=FALSE}
```

### Data used in model

**Status & trend**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="HAB", dimension %in% c("status", "trend")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```


**Pressure**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="HAB", dimension %in% c("pressure")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```

**Resilience**

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
st <- targets %>%
  filter(goal=="HAB", dimension %in% c("resilience")) %>%
  select(layer) %>%
  unique()

st_layers <- filter(layers, layer %in% st$layer) %>%
 mutate(web_name = gsub(" ", "_", name)) %>%
  mutate(web_name = tolower(web_name)) %>%
  mutate(web_name = gsub("/", "", web_name)) %>%
  mutate(info = sprintf("[%s](%s#%s) (%s): %s", name, layers_web, web_name, layer, description))

cat(paste(st_layers$info, collapse="\n\n"))

```
