---
title: "LSP explore"
author: "Gage Clawson"
date: "7/19/2021"
output: html_document
---

## Explore the LSP data after new data updates

```{r setup, include=FALSE, message = F, warning = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)

library(tidyverse)
library(here)
source('http://ohi-science.org/ohiprep_v2021/workflow/R/common.R')
region_data()
```

```{r}

lsp_scores <- read_csv(file.path(here(), "yearly_results/global2021/scores_2021-11-17.csv"))

lsp_scores <- read_csv(file.path(here(), "yearly_results/global2021/OHI_final_formatted_scores_2021-11-17.csv"))


lsp_status <- lsp_scores %>%
  filter(goal == "LSP", dimension == "status", region_id != 0) %>%
  left_join(rgns_eez, by = c("region_id" = "rgn_id"))
  

## get top ten and bottom ten scores for 2021

DT::datatable(lsp_status %>%
  filter(scenario == 2021) %>%
  arrange(-score) %>%
    dplyr::select(goal, dimension, rgn_name, scenario, score))


reds <-  colorRampPalette(c("#A50026", "#D73027", "#F46D43", "#FDAE61", "#FEE090"), space="Lab")(65)
blues <-  colorRampPalette(c("#E0F3F8", "#ABD9E9", "#74ADD1", "#4575B4", "#313695"))(35)
myPalette <-   c(reds, blues)
```


**Some interesting possible comparisons**

Within country, over time:
 - Pitcairn; 
    - implemented one of the biggest protected areas in world.
    - https://www.theguardian.com/environment/2015/mar/18/pitcairn-islands-marine-reserve-budget-2015
    
    
Pitcairn's score has increased dramatically over the past 10 years. Until 2015, Pitcairn did not have any protected areas in it's surrounding areas, and recieved a score 0. However, in 2015, the United Kingdom government implemeted the largest single marine reserve in the world (at the time), and it's score jumped to 71/100 in 2016, when the change was realized in the global OHI scores. In recent years, the protected area has become smaller, and it's current score is 54 for 2021. 
    

```{r}
data <- lsp_status %>%
  filter(dimension == "status") %>%   # focus only on score data
  filter(region_id != 213)  %>% # eliminate Antarctica
  mutate(value = round(value, 0)) %>%
  mutate(rgn_name = as.character(rgn_name)) %>%
  group_by(region_id) %>% 
  mutate(meanIndex=mean(value[goal=="Index"])) %>%
  ungroup() %>%
  data.frame() %>%
  filter(goal == "LSP")
  


data_pit <- data %>%
  filter(rgn_name == "Pitcairn")

data_pit


ggplot(data_pit, aes(y=rgn_name, x=year, fill=value)) + 
  geom_tile() +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), axis.text.y=element_text(size=10)) +
  ylab("") + 
  xlab("")
```
    
    

 - New Zealand; 
    - implementing a huge protected area? 
    - https://www.pewtrusts.org/en/research-and-analysis/articles/2020/11/02/new-zealand-could-soon-protect-one-of-worlds-most-biodiverse-marine-areas
 - Canada;
    - has the worlds largest coastline, but still isn't reaching the 30% target... They have agreed to protect at least 10% of their coastline by 2020.. did they do it? In 2019 they announced they protected 13.8% of its oceans.
    - https://storymaps.arcgis.com/stories/0ab9b72c6351401480e20c8e921c270e
 
Across countries for 2021: 
 - Australia (great score) vs. India/China/Canada (not great scores)
     - 
 - USA vs. Canada; why is Canada so much worse? 
 - IRL vs. NZL; similar pretty progressive island nations. 
 - South Africa, Mozambique, Namibia all have GREAT scores. Counter to the general public perception. Could be cool to explore why. 

Future trends: 
  - Expect Christmas Islands and Cocos (Keeling) to increase in the 2022 assessment
  - https://news.mongabay.com/2021/05/two-new-australian-marine-parks-protect-area-twice-the-size-the-great-barrier-reef/


```{r}
ggplot(data %>% filter(rgn_name %in% c("Canada", "Pitcairn", "New Zealand", "Australia", "South Africa", "Mozambique", "Tanzania", "Namibia", "Ireland", "Thailand", "Seychelles", "India", "China")), aes(y=rgn_name, x=scenario, fill=value)) + 
  geom_tile() +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), axis.text.y=element_text(size=10)) +
  ylab("") + 
  xlab("") 


data %>% filter(rgn_name %in% c("Canada", "Pitcairn", "New Zealand", "Australia", "South Africa", "Mozambique", "Tanzania", "Namibia", "Ireland", "Thailand", "Seychelles", "India", "China")) %>%
                  dplyr::select(rgn_name, scenario, value)
```


Seychelles: 

Seychelles had a LSP status score of 53.23 from 2012 to 2020, however, in 2021 the status score jumped to 100. Why did this occur? 
Seychelles completed its commitment to increase it’s marine protection to a full 30 percent of its exclusive economic zone (EEZ) in 2020. This major accomplishment is realized in the 2021 OHI LSP status score for Seychelles. It’s new marine protected area now covers an area larger than Germany. 
Source: https://www.nature.org/en-us/about-us/where-we-work/africa/stories-in-africa/seychelles-conservation-commitment-comes-to-life/

```{r}
data <- lsp_status %>%
  filter(dimension == "status") %>%   # focus only on score data
  filter(region_id != 213)  %>% # eliminate Antarctica
  mutate(value = round(score, 0)) %>%
  mutate(rgn_name = as.character(rgn_name)) %>%
  group_by(region_id) %>% 
  mutate(meanIndex=mean(value[goal=="Index"])) %>%
  ungroup() %>%
  data.frame() %>%
  filter(goal == "LSP")
  


data_sey <- data %>%
  filter(rgn_name == "Seychelles")

data_sey


ggplot(data_sey, aes(y=rgn_name, x=year, fill=value)) + 
  geom_tile() +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), axis.text.y=element_text(size=10)) +
  ylab("") + 
  xlab("")
```


Take the below stats from this folder: https://github.com/OHI-Science/ohiprep_v2021/tree/gh-pages/globalprep/lsp/v2021/int

Determine proportion of ocean/land areas that are protected

```{r}
prot_3nm <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2021/gh-pages/globalprep/lsp/v2021/int/area_protected_3nm.csv')

prot_3nm_2020 <- prot_3nm %>%
  filter(year == 2020) %>%
  mutate(type = "3nm")

sum(prot_3nm_2020$a_prot_km2) # 1091838
sum(prot_3nm_2020$a_tot_km2) # 4995189

1091838/4995189 # 0.2185779 ; ~22% of 3nm areas are protected 


prot_1km <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2021/gh-pages/globalprep/lsp/v2021/int/area_protected_1km.csv')

prot_1km_2020 <- prot_1km %>%
  filter(year == 2020) %>%
  mutate(type = "1km")

sum(prot_1km_2020$a_prot_km2) # 293256.5
sum(prot_1km_2020$a_tot_km2) # 1133638

293256.5/1133638 # 0.2586862 ; ~26% of 1km areas are protected 


prot_eez <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2021/gh-pages/globalprep/lsp/v2021/int/area_protected_eez.csv')

prot_eez_2020 <- prot_eez %>%
  filter(year == 2020) %>%
  mutate(type = "eez")

sum(prot_eez_2020$a_prot_km2) # 26241770
sum(prot_eez_2020$a_tot_km2) # 359482664

26241770/359482664 # 0.07299871 ; ~7% of eez areas are protected 


all_prot <- rbind(prot_eez_2020, prot_1km_2020, prot_3nm_2020) %>%
  group_by(type) %>%
  summarise(total_area = sum(a_tot_km2),
            total_prot_area = sum(a_prot_km2)) %>%
  mutate(percent_prot = (total_prot_area/total_area)*100)

kable(all_prot)

# |type | total_area| total_prot_area| percent_prot|
# |:----|----------:|---------------:|------------:|
# |1km  |    1133638|        293256.5|    25.868631|
# |3nm  |    4995189|       1091838.0|    21.857792|
# |eez  |  359482664|      26241770.2|     7.299871|
```




 
