---
title: "MAR explore"
author: "Gage Clawson"
date: "7/20/2021"
output: html_document
---

## Explore the MAR data after new data updates

```{r setup, include=FALSE, message = F, warning = F}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)

library(tidyverse)
library(here)
source('http://ohi-science.org/ohiprep_v2021/workflow/R/common.R')
region_data()
```

```{r}

mar_scores <- read.csv(file.path(here(), "yearly_results/global2021/scores_2021-11-17.csv"))


mar_status <- mar_scores %>%
  filter(goal == "MAR", dimension == "score", region_id != 0)

tmp <- mar_status %>%
  filter(region_id %in% c(224,223))

## get top ten and bottom ten scores for 2021

DT::datatable(mar_status %>%
  filter(year == 2021) %>%
  arrange(-score) %>%
    dplyr::select(goal, dimension, year, score, score))

## make a carpet plot to view the changes across years 

data <- mar_status %>%
  filter(dimension == "status") %>%   # focus only on score data
  filter(rgn_id != 213)  %>% # eliminate Antarctica
  group_by(rgn_id) %>% 
  mutate(meanIndex=mean(value[goal=="Index"])) %>%
  ungroup() %>%
  data.frame()
  

global <- data %>%
  select(rgn_name, meanIndex) %>%
  filter(rgn_name == "Region") %>%
  unique()

order_rgn <- data %>%
  filter(rgn_name != "Region") %>%
  select(rgn_name, meanIndex) %>%
  unique() %>%
  arrange(meanIndex)
  
order_rgn <- rbind(order_rgn, global)

goals <- c('Index', 'AO', 'SPP', 'BD', 'HAB', 'CP', 'CS', 'CW', 'ECO', 'LE', 'LIV', 'FIS', 'FP', 'MAR', 'ICO', 'SP', 'LSP', 'NP', 'TR')

data$goal <- factor(data$goal, levels = goals)
data$rgn_name <- factor(data$rgn_name, levels=order_rgn$rgn_name)

reds <-  colorRampPalette(c("#A50026", "#D73027", "#F46D43", "#FDAE61", "#FEE090"), space="Lab")(65)
blues <-  colorRampPalette(c("#E0F3F8", "#ABD9E9", "#74ADD1", "#4575B4", "#313695"))(35)
myPalette <-   c(reds, blues)

scenario <- 2021

data_mar <- data %>%
  filter(goal == "MAR")
  

ggplot(data_mar, aes(y=rgn_name, x=year, fill=value)) + 
  geom_tile() +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), axis.text.y=element_text(size=10)) +
  ylab("") + 
  xlab("")
ggsave(here("yearly_results/global2021/data_check/mar_status_carpet.png"), width=20, height=35)

```


**Some interesting possible comparisons**

Within country, over time:
 - Germany; 
    - huge increase over whole time period
    
    
Germany's mariculture status score has increased dramatically over the past 10 years. 
    

```{r}
data <- mar_scores %>%
  filter(dimension == "status") %>%   # focus only on score data
  filter(region_id != 213)  %>% # eliminate Antarctica
  mutate(value = round(score, 0),
         value_old = round(old_score, 0)) %>%
  mutate(rgn_name = as.character(rgn_name)) %>%
  group_by(region_id) %>% 
  mutate(meanIndex=mean(value[goal=="Index"])) %>%
  ungroup() %>%
  data.frame() %>%
  filter(goal == "MAR")
  


data_deu <- data %>%
  filter(rgn_name == "Germany")

data_deu


ggplot(data_deu, aes(y=rgn_name, x=year, fill=value)) + 
  geom_tile() +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), axis.text.y=element_text(size=10)) +
  ylab("") + 
  xlab("")
```

```{r}
ggplot(data %>% filter(rgn_name %in% c("Germany", "Denmark", "China", "Greece", "Egypt", "Italy", "Malta", "North Korea", "Norway", "Chile")), aes(y=rgn_name, x=year, fill=value)) + 
  geom_tile() +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette, na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), axis.text.y=element_text(size=10)) +
  ylab("") + 
  xlab("") 


data %>% filter(rgn_name %in% c("Germany", "Denmark", "China")) %>%
                  dplyr::select(rgn_name, year, value)
```


Chile and Norway production/status comparison: 

```{r}

tonnes_prod <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2021/gh-pages/globalprep/mar/v2021/output/mar_harvest_tonnes.csv")

chile_tonnes <- tonnes_prod %>%
  filter(rgn_id %in% c(223,224)) %>%
  filter(year == 2019) %>%
  group_by(rgn_id) %>%
  summarise(tonnes = sum(tonnes))

```


## Some global stats:


Total tonnes produced
```{r}
tonnes_prod <- read_csv("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2021/gh-pages/globalprep/mar/v2021/output/mar_harvest_tonnes.csv")

tonnes_prod_2019 <- tonnes_prod %>%
  filter(year == 2019)
sum(tonnes_prod_2019$tonnes) # 49330043


tonnes_chn <- tonnes_prod_2019 %>%
  filter(rgn_id == 209)
sum(tonnes_chn$tonnes) # 32994779

32994779/49330043

tonnes_prod_spp <- tonnes_prod_2019 %>%
  mutate(spp = gsub("_.*", "", taxa_code))


most_common <- tonnes_prod_spp %>%
  filter(tonnes > 0 ) %>%
  group_by(spp) %>%
  summarise(count_most_common = n()) %>%
  arrange(-count_most_common)

kable(head(most_common,15))

most_common_prod <- tonnes_prod_spp %>%
  filter(tonnes > 0) %>%
  group_by(spp) %>%
  summarise(total_prod = sum(tonnes)) %>%
  arrange(-total_prod)

kable(head(most_common_prod,15))
```

Look at Norway and China sustainability scores

```{r}
mar_sust <- read.csv(file.path(here(), "eez/layers/mar_sustainability_score.csv")) %>%
  left_join(rgns_eez) %>%
  dplyr::select(1:5)


write.csv(mar_sust, file.path(here(), "yearly_results/global2021/data_check/mariculture_sustainability.csv"))

mar_tonnes <- read.csv(file.path(here(), "eez/layers/mar_harvest_tonnes.csv")) %>%
  left_join(rgns_eez) %>%
  dplyr::select(1:7)

write.csv(mar_tonnes, file.path(here(), "yearly_results/global2021/data_check/mariculture_production.csv"))


pot_tonnes <- read.csv(file.path(here(), "eez/layers/mar_capacity.csv"))   %>%
  left_join(rgns_eez) %>%
  dplyr::select(1:4)

write.csv(pot_tonnes, file.path(here(), "yearly_results/global2021/data_check/mariculture_potential.csv"))


mar_all <- mar_tonnes %>%
  left_join(mar_sust, by = c("rgn_id", "taxa_code", "rgn_name")) %>%
  left_join(pot_tonnes, by = c("rgn_id", "rgn_name")) %>%
  dplyr::rename("production_year" = "year.x", "sustainability_year" = "year.y", "gentry_year" = "year")

write.csv(mar_all, file.path(here(), "yearly_results/global2021/data_check/combined_mariculture_layers.csv"))


summarized_mar <- mar_all %>%
  tidyr::spread(production_year, tonnes) %>%
  tidyr::gather("production_year", "tonnes",-(1:9)) %>%
    dplyr::mutate(scenario_year = as.numeric(production_year)) %>%
  filter(scenario_year >= 2001) %>%
  dplyr::select(-taxa_group)

  m <- summarized_mar %>%
    dplyr::group_by(rgn_id, taxa_code, sust_coeff) %>%
    dplyr::arrange(rgn_id, taxa_code, scenario_year) %>%
    dplyr::mutate(rolling_mean_4_year_tonnes = zoo::rollapply(tonnes, 4, mean, na.rm = TRUE, partial =
                                        TRUE, align = "right")) %>%
    dplyr::ungroup() %>%
    mutate(rolling_mean_4_year_tonnes = ifelse(rolling_mean_4_year_tonnes == "NaN", 0, rolling_mean_4_year_tonnes))
 
   tonnes_pot_div <- m %>%
    dplyr::group_by(rgn_id, rgn_name, scenario_year) %>%
    dplyr::summarize(tonnes_sum = sum(rolling_mean_4_year_tonnes, na.rm = TRUE)) %>%  #na.rm = TRUE assumes that NA values are 0
    dplyr::left_join(pot_tonnes, by = c('rgn_id', 'rgn_name')) %>%
    dplyr::mutate(tonnes_score = tonnes_sum / potential_mar_tonnes) %>%
    dplyr::ungroup() 
    
    sustainability <- m %>%
    dplyr::group_by(rgn_id, rgn_name, scenario_year) %>%
    dplyr::summarise(sust_rgn = weighted.mean(x = sust_coeff, w = rolling_mean_4_year_tonnes, na.rm = TRUE)) %>%
    dplyr::ungroup()
  
    ry <- sustainability %>%
      dplyr::left_join(tonnes_pot_div) %>%
      # dplyr::mutate(mar_score = sust_rgn*tonnes_score) %>%
      dplyr::mutate(tonnes_score_rescale = ifelse(tonnes_score > 1,
                                    1,
                                    tonnes_score)) %>%
      dplyr::mutate(sust_times_tonnes_score = sust_rgn*tonnes_score_rescale) %>%
      dplyr::select(-year)
    
    write.csv(ry, file.path(here(), "yearly_results/global2021/data_check/summarized_mariculture_layers.csv"))
  

mar_tonnes_chn_nor <- mar_tonnes %>% 
  filter(rgn_id %in% c(209, 223, 137, 216))

mar_sust_chn_nor <- mar_sust %>%
  dplyr::select(-year) %>%
  filter(rgn_id %in% c(209, 223, 137, 216, 224)) %>%
  left_join(mar_tonnes, by = c("rgn_id", "taxa_code")) %>%
  arrange(rgn_id, taxa_code, year) %>%
  filter(year > 2005)

tmp <- mar_sust_chn_nor %>%
  group_by(rgn_id, year) %>%
  summarise(avg_sust = mean(sust_coeff))


tmp <- mar_sust_chn_nor %>%
  filter(year == 2019) %>%
  arrange(rgn_id, -tonnes)

## potential tonnes of mar for Norway
204374.5

## produced tonnes of mar for Norway 
tmp <- mar_sust_chn_nor %>%
  filter(rgn_id %in% c(223, 137)) %>%
  filter(year == 2019)
sum(tmp$tonnes) # 1452774


1452774/204374.5
# norway produces 7x more mariculture than their potential 

tmp <- mar_sust_chn_nor %>%
  filter(rgn_id == 223, year == 2019) %>%
  mutate(total_tonnes = sum(tonnes)) %>%
  mutate(percent = tonnes/total_tonnes)


test <- read.csv(file.path(here(), "eez/score_check/mar_new_methods_diff_data_2021-11-16.csv")) %>%
  filter(goal == "MAR", year == 2021, dimension == "score")


```


```{r}
mar_sust_chn_nor <- mar_sust %>%
  dplyr::select(-year) %>%
  filter(rgn_id %in% c(224)) %>%
  left_join(mar_tonnes, by = c("rgn_id", "taxa_code")) %>%
  arrange(rgn_id, taxa_code, year) %>%
  filter(year == 2019)
```



 
