---
title: "Region_summary"
author: "Melanie Frazier (UCSB, NCEAS, OHI)"
date: "April 4, 2018"
output: html_document
---

# Extracting data for Moore region proposal.

```{r prep, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

library(dplyr)
library(tidyr)
library(DT)
library(knitr)


regions <- c(112, 210, 7, 163, 162, 16)
rgn_names <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/spatial/regions_list.csv")

rgns <- filter(rgn_names, rgn_id %in% regions) %>%
  select(rgn_id, rgn_name)
```


##Social indicators

These are slightly modified versions of data from the Social Progress Index (https://www.socialprogressindex.com/) and the Worldwide Governance Indicators (http://info.worldbank.org/governance/wgi/#home).

```{r social, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

spi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/res_spi.csv") %>%
  filter(year == 2017) %>%
  select(rgn_id, SPI = resilience_score)

social_res <- rgns %>%
  left_join(spi)


wgi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/wgi_all.csv") %>%
  filter(year == 2015) %>%
  select(rgn_id, WGI = resilience_score)

social_res <- social_res %>%
  left_join(wgi)

kable(social_res)

```


## Marine Protected Areas

This describes the amount of marine protected area (km2) within 3nm of the coastline.

IUCN and UNEP-WCMC (2016), The World Database on Protected Areas (WDPA) [On-line], May 2016. Cambridge, UK: UNEP-WCMC. Available at: www.protectedplanet.net.

NOTE: This is the protected area for the entire US, not the Gaviota Coast.
```{r mpa, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

mpa <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/lsp_prot_area_offshore3nm.csv") %>%
  filter(year == 2017) %>%
  select(rgn_id, MPA = a_prot_3nm)

protected <- rgns %>%
  left_join(mpa)


area <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/rgn_area_offshore3nm.csv") %>%
  select(rgn_id, rgn_area_3nm = area)

protected <- protected %>%
  left_join(area) %>%
  mutate(percent_mpa = round(MPA/rgn_area_3nm * 100))

kable(protected)

```


##Cumulative Human Impact

These are the eez summarized [Cumulative Human Impacts](https://www.nature.com/articles/ncomms8615) data.  This summary includes only the Cumulative Impact values for the regions of interest.  The full data is available [here](https://github.com/OHI-Science/ohi-global/blob/draft/global2017/Moore_regions/oneYearNorm_2013_eez_zeroData.csv).

NOTE: This is based on the full US extraction!  It will take a bit of work to extract the Gavioata Coast region.  I will do this, but I wanted to provide these data so we could begin thinking about it.

```{r chi, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

chi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/global2017/Moore_regions/oneYearNorm_2013_eez_zeroData.csv") %>%
  filter(eez_nam %in% rgns$rgn_name) %>%
  select(region = eez_nam, Cumulative_impact = global_cumulative_impact_2013_all_layers.gri)

kable(chi)

```


