---
title: "Region_summary"
author: "Melanie Frazier (UCSB, NCEAS, OHI)"
date: "April 4, 2018"
output: html_document
---

Extracting data for Moore regions.

```{r prep}

library(dplyr)
library(tidyr)
library(DT)
library(knitr)


regions <- c(112, 210, 7, 163, 162, 16)
rgn_names <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/spatial/regions_list.csv")

rgns <- filter(rgn_names, rgn_id %in% regions) %>%
  select(rgn_id, rgn_name)
```


##Social indicators

These are slightly modified versions of data from the Social Progress Index (https://www.socialprogressindex.com/) and the Worldwide Governance Indicators (http://info.worldbank.org/governance/wgi/#home).

```{r prep, echo=FALSE, warning=FALSE}

spi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/res_spi.csv") %>%
  filter(year == 2017) %>%
  select(rgn_id, SPI = resilience_score)

social_res <- rgns %>%
  left_join(spi)


wgi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/wgi_all.csv") %>%
  filter(year == 2015) %>%
  select(rgn_id, WGI = resilience_score)

social_res <- social_res %>%
  left_join(wgi)

kable(social_res)

```


##Cumulative Human Impact

These are the eez summarized [Cumulative Human Impacts](https://www.nature.com/articles/ncomms8615) data.  This summary includes only the Cumulative Impact values for the regions of interest.  The full data is available [here]().

```{r prep, echo=FALSE, warning=FALSE}

spi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/res_spi.csv") %>%
  filter(year == 2017) %>%
  select(rgn_id, SPI = resilience_score)

social_res <- rgns %>%
  left_join(spi)


wgi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/wgi_all.csv") %>%
  filter(year == 2015) %>%
  select(rgn_id, WGI = resilience_score)

social_res <- social_res %>%
  left_join(wgi)

kable(social_res)

```


