---
title: "Region_summary"
author: "Melanie Frazier (UCSB, NCEAS, OHI)"
date: "April 4, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

# Extracting data for Moore region proposal.

```{r prep, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

library(dplyr)
library(tidyr)
library(DT)
library(knitr)

regions <- c(112, 210, 7, 163, 162, 16)
rgn_names <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/spatial/regions_list.csv")

rgns <- filter(rgn_names, rgn_id %in% regions) %>%
  dplyr::select(rgn_id, rgn_name)

#setwd("global2017/Moore_regions")

```



##Social indicators

These are slightly modified versions of data from the Social Progress Index (https://www.socialprogressindex.com/) and the Worldwide Governance Indicators (http://info.worldbank.org/governance/wgi/#home).

```{r social, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

spi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/res_spi.csv") %>%
  filter(year == 2017) %>%
  select(rgn_id, SPI = resilience_score)

social_res <- rgns %>%
  left_join(spi)


wgi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/wgi_all.csv") %>%
  filter(year == 2015) %>%
  select(rgn_id, WGI = resilience_score)

social_res <- social_res %>%
  left_join(wgi)

kable(social_res)

```


##Climate pressures

Extracting the climate pressure layers.

```{r social, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

slr <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/cc_slr.csv") %>%
  dplyr::select(rgn_id, year, SLR = pressure_score)

acid <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/cc_acid.csv") %>%
  dplyr::select(rgn_id, year, OA = pressure_score)

sst <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/cc_sst.csv") %>%
  dplyr::select(rgn_id, year, SST = pressure_score)

uv <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/cc_uv.csv") %>%
  dplyr::select(rgn_id, year, UV = pressure_score)


pressure <- left_join(slr, acid) %>%
  left_join(uv) %>%
  left_join(sst) %>%
  filter(year %in% 2012:2016)

pressures <- rgns %>%
  left_join(pressure) 

pressure <- function(location){ # location = "Japan"
  output <- pressures %>%
    filter(rgn_name == location) %>%
    dplyr::select(-rgn_id) %>%
    gather("pressure", "score", 3:6)
  
  average <- output %>%
    group_by(year) %>%
    summarize(score = mean(score)) %>%
    mutate(rgn_name = location) %>%
    mutate(pressure = "average pressure") %>%
    dplyr::select(rgn_name, year, pressure, score)

output <- bind_rows(output, average)  %>%
  spread(year, score)

write.csv(output, sprintf("data/%s_climate_prs.csv", location), row.names=FALSE)

}

pressure("Japan")
pressure("United States")
pressure("Cuba")
pressure("New Zealand")


```


## Marine Protected Areas

This describes the amount of marine protected area (km2) within 3nm of the coastline.

IUCN and UNEP-WCMC (2016), The World Database on Protected Areas (WDPA) [On-line], May 2016. Cambridge, UK: UNEP-WCMC. Available at: www.protectedplanet.net.

NOTE: This is the protected area for the entire US, not the Gaviota Coast.
```{r mpa, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

mpa <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/lsp_prot_area_offshore3nm.csv") %>%
  filter(year == 2017) %>%
  select(rgn_id, MPA = a_prot_3nm)

protected <- rgns %>%
  left_join(mpa)


area <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/eez/layers/rgn_area_offshore3nm.csv") %>%
  select(rgn_id, rgn_area_3nm = area)

protected <- protected %>%
  left_join(area) %>%
  mutate(percent_mpa = round(MPA/rgn_area_3nm * 100))

kable(protected)

```
##Region map
```{r gaviota, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE, eval=FALSE}

# prepare Gaviota coast data
# data from: https://www.sciencebase.gov/catalog/item/589a2585e4b0efcedb71a5bc
library(rgdal)
library(raster)
library(sf)

source("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2017/master/src/R/spatial_common.R")

source('../../global2016/Reporting/map_fxns.R')

### set scenario and desired map projection
prj      <- 'mol'    ### note: 'gcs' is way faster.

# brewer.pal(10, "RdYlBu")
reds <-  colorRampPalette(c("#A50026", "#D73027", "#F46D43", "#FDAE61", "#FEE090"), space="Lab")(65)
blues <-  colorRampPalette(c("#E0F3F8", "#ABD9E9", "#74ADD1", "#4575B4", "#313695"))(35)
colors <-   c(reds, blues)


### get OHI data and rename column headings

for(year in 2012:scenario){ #year=2012

if(year != scenario){
  if(sum(grepl(sprintf("year_%s", year), list.files("figures/maps_by_goal_mol"))) == 0){
  dir.create(sprintf("figures/maps_by_goal_mol/year_%s", year))
  }
  }
    
scores_df <- read.csv(sprintf('data/scores_eez%s.csv', year), stringsAsFactors = FALSE) %>%
  rename(rgn_name = region_name, rgn_id = region_id) %>%
  mutate(rgn_id = as.character(rgn_id))

### load region data frame, so doesn't need to reload every time through the loop.  Also
### load the land data frame, if plotting in Mollweide projection.
rgn_df <- get_rgn_df(prj = prj)
if(prj == 'mol' & !exists('land_poly')) {
  land_poly  <- get_land_df()
  ocean_poly <- get_ocean_df() ### assume if land_poly doesn't exist, ocean_poly doesn't either...
}


### establish list of fields for mapping
mapFlds   <- names(scores_df %>% select(-rgn_name, -rgn_id))

### Loop over each field, plotting each map in turn and saving to file.
for (fld in mapFlds) { # fld <- mapFlds[1]

  if(year==scenario){
   fig_save = sprintf('figures/maps_by_goal_%s/global_map_%s_%s_%s.png', prj, fld, year, prj)
} else{ 
    fig_save = sprintf('figures/maps_by_goal_%s/year_%s/global_map_%s_%s_%s.png', prj, year, fld, year, prj)
    }
  
   ohiplot <- plot_scores_easy(scores_df, fld, rgn_df, title = title, prj = prj, fig_save = fig_save,
                                 colors_spec = colors, leg_on = TRUE)
   
   #print(ohiplot)
}
}



```

##Cumulative Human Impact

These are the eez summarized [Cumulative Human Impacts](https://www.nature.com/articles/ncomms8615) data.  This summary includes only the Cumulative Impact values for the regions of interest.  The full data is available [here](https://github.com/OHI-Science/ohi-global/blob/draft/global2017/Moore_regions/oneYearNorm_2013_eez_zeroData.csv).

NOTE: This is based on the full US extraction!  It will take a bit of work to extract the Gavioata Coast region.  I will do this, but I wanted to provide these data so we could begin thinking about it.

```{r gaviota, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE, eval=FALSE}

# prepare Gaviota coast data
# data from: https://www.sciencebase.gov/catalog/item/589a2585e4b0efcedb71a5bc
library(rgdal)
library(raster)
library(sf)

source("https://raw.githubusercontent.com/OHI-Science/ohiprep_v2017/master/src/R/spatial_common.R")

gav <- sf::st_read(dsn = file.path(dir_M, "git-annex/globalprep/_raw_data/Geology_OffshoreGaviota"), layer = "Geology_OffshoreGaviota")

gav_rgn <- gav %>%
  mutate(MapUnit = 1) %>%
  group_by(MapUnit) %>%
  summarize(area = sum(Shape_area))

gav_rgn <- sf::as_Spatial(gav_rgn$geom)
gav_rgn <- st_zm(gav_rgn)

gav_rgn <- as(gav_rgn, "Spatial")

gav_mol <- spTransform(gav_rgn, CRS(proj4string(ocean)))

regions <- as(regions, "Spatial")
plot(regions)
plot(gav_mol, add=TRUE, col="red")

writeOGR(gav_mol, dsn=file.path(dir_M, "git-annex/globalprep/_raw_data/Geology_OffshoreGaviota"), layer = "Geology_OffshoreGaviota_mol",
         driver="ESRI Shapefile")
```


### Cumulative Human Impacts
```{r chi, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

chi <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/global2017/Moore_regions/oneYearNorm_2013_eez_zeroData.csv") %>%
  filter(eez_nam %in% rgns$rgn_name) %>%
  select(region = eez_nam, Cumulative_impact = global_cumulative_impact_2013_all_layers.gri)

kable(chi)

```


### Stressor summary
```{r stresors, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

stressors <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/global2017/Moore_regions/oneYearNorm_2013_eez_zeroData.csv") %>%
  dplyr::filter(eez_nam %in% rgns$rgn_name) %>%
  dplyr::rename(region = eez_nam) %>%
  dplyr::select(-global_cumulative_impact_2013_all_layers.gri)

stressors <- data.frame(t(stressors))
colnames(stressors) <- as.character(unlist(stressors[1,]))
stressors <- stressors[-1, ]

DT::datatable(stressors, options = list(
  pageLength = 19))

```

### CHI maps
```{r maps, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

stressors <- read.csv("https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/global2017/Moore_regions/oneYearNorm_2013_eez_zeroData.csv") %>%
  dplyr::filter(eez_nam %in% rgns$rgn_name) %>%
  dplyr::rename(region = eez_nam) %>%
  dplyr::select(-global_cumulative_impact_2013_all_layers.gri)

stressors <- data.frame(t(stressors))
colnames(stressors) <- as.character(unlist(stressors[1,]))
stressors <- stressors[-1, ]

DT::datatable(stressors, options = list(
  pageLength = 19))

```

