---
title: "Capping resiliences"
author: "Gage Clawson"
date: "8/5/2021"
output: html_document
---

```{r}
## load packages:
library(ohicore)
library(zoo)
library(stringr)
library(readr)
library(here)
library(tidyverse)

## source file path info depending on operating system
source('http://ohi-science.org/ohiprep_v2021/workflow/R/common.R')
```


# Update resilience and pressure calculations for Likely Future State

Resilience is generally quite high relative to pressures.  The idea of resilience is that legal, social, and ecological systems are in place to address pressures, so once pressures are addressed, these systems should not further be counted toward improving OHI scores.

This chunk manually recalculates Likely Future State by capping resilience values such that they do not exceed pressure values.  This is done after all pressures and resilience measures have been combined and weighted.

``` {r cap resilience}
scores_all <- read_csv(file.path("scores.csv"))

beta <- .67; delta <- 1

scores_wide <- scores_all %>%
  filter(region_id != 0) %>%
  spread(dimension, score) %>%
  filter(!is.na(resilience) & !is.na(pressures)) %>%
    ### note: this drops supragoals, intentionally
  rename(future_orig = future, res_orig = resilience) %>%
 # mutate(res_orig = res_orig*0.5) %>%
  mutate(trend = ifelse(is.na(trend), 0, trend),
           ### NA trends convert to 0 for calculating future state?
         resilience = ifelse(res_orig > pressures, pressures, res_orig)) %>%
 # mutate(resilience = 0.5*resilience) %>%
  mutate(future = status * (1 + beta * trend + (1 - beta) * (resilience - pressures)/100),
         future = ifelse(future > 100, 100, future)) %>%
  mutate(score_orig = score,
         score = (status + future) / 2)


# x <- scores_wide %>%
#   filter(score_orig < score)
ggplot(scores_wide, aes(x = res_orig, y = resilience, color = goal)) +
  geom_abline(intercept = 0, slope = 1, color = 'red') +
  geom_point() 
ggplot(scores_wide, aes(x = future_orig, y = future, color = goal)) +
  geom_abline(intercept = 0, slope = 1, color = 'red') +
  geom_point() 
ggplot(scores_wide, aes(x = score_orig, y = score, color = goal)) +
  geom_abline(intercept = 0, slope = 1, color = 'red') +
  geom_point() 
```

## gather supragoals; attach to subgoals and complete goals

``` {r}
scores_long <- scores_wide %>%
  select(-ends_with('orig')) %>%
  gather(dimension, score, pressures:future)
### recalculate supragoals 
fp <- scores_long %>%
  filter(goal %in% c('MAR', 'FIS', 'SAL')) %>%
  group_by(year, region_id, dimension) %>%
  summarize(score = mean(score, na.rm = TRUE)) %>%
  filter(!dimension %in% c('pressures', 'resilience')) %>%
  mutate(goal = 'FP')
  
sp <- scores_long %>%
  filter(goal %in% c('LSP', 'ICO')) %>%
  group_by(year, region_id, dimension) %>%
  summarize(score = mean(score, na.rm = TRUE)) %>%
  filter(!dimension %in% c('pressures', 'resilience')) %>%
  mutate(goal = 'SP')
bd <- scores_long %>%
  filter(goal %in% c('SPP', 'HAB')) %>%
  group_by(year, region_id, dimension) %>%
  summarize(score = mean(score, na.rm = TRUE)) %>%
  filter(!dimension %in% c('pressures', 'resilience')) %>%
  mutate(goal = 'BD')
 
hs <- scores_long %>%
  filter(goal %in% c('CPP', 'CSS')) %>%
  group_by(year, region_id, dimension) %>%
  summarize(score = mean(score, na.rm = TRUE)) %>%
  filter(!dimension %in% c('pressures', 'resilience')) %>%
  mutate(goal = 'HS')
lv <- scores_long %>%
  filter(goal %in% c('LVF', 'LVO')) %>%
  group_by(year, region_id, dimension) %>%
  summarize(score = mean(score, na.rm = TRUE)) %>%
  filter(!dimension %in% c('pressures', 'resilience')) %>%
  mutate(goal = 'LV')
scores_w_supra <- scores_long %>%
  bind_rows(fp, sp, bd, hs, lv)
### generate index scores for each region
scores_rgn_index <- scores_w_supra %>%
  filter(nchar(goal) == 2) %>%
  filter(dimension %in% c('status', 'future', 'score')) %>%
  group_by(region_id, year, dimension) %>%
  summarize(score = mean(score, na.rm = TRUE),
            goal = 'Index')
scores_w_index <- scores_w_supra %>%
  bind_rows(scores_rgn_index)


# write_csv(scores_new_res, file.path(dir_calc, 'scores_all.csv'))
```
