---
title: "Reporting for 2015 OHI global"
author: "Casey and Mel"
date: "9/1/2015"
output: html_document
---

This document summarizes the data for the OHI 2015 global analysis.  Shortcuts to:

* [Saving data files for websites](#saving)
* [Human-readable tables](#tables)
* [Figures:](#figures)
    * [Carpet plot](#carpet)
    * [Maps](#maps) by goal and subgoal
    * [Scatter plots](#scatter) showing 2015 analysis vs 2014 analysis (using 2013 benchmark year)
    * [GoogleVis plots](#googlevis)
    * [Flower plots](#flower) for every region

```{r data set up, include=FALSE}

#load libraries
library(dplyr)
library(tidyr)
library(ggplot2)
library(hwriter)
library(RColorBrewer)
library(knitr)
library(googleVis)
library(ohicore)
library(sp)
library(rgdal)

dir_global <- ifelse(dir.exists('~/github'), '~/github/ohi-global', '~/ohi-global')
setwd(dir_global)

goals <- c('Index', 'AO', 'SPP', 'BD', 'HAB', 'CP', 'CS', 'CW', 'ECO', 'LE', 'LIV', 'FIS', 'FP', 'MAR', 'ICO', 'SP', 'LSP', 'NP', 'TR')

#---------------------------
## General settings to control
scenario <- "2015" #identify scenario of focus (this can be changed to obtain data for other years)
radicalFile = '2015-08-20' #date extension on the radical data files that are used for all tables/figures
benchmark = 2013  # year that is used for old vs. new OHI analyses
oldCommit = '4da6b4a1d69d694264ea68456359a939b0c03f9c' # '4da6b4a1d69d694264ea68456359a939b0c03f9c' = commit for 2014 analysis
colorScheme <- 'new'  # color scheme to use on flower plots ("new" = color reflects size score and is not the original rainbow)
saveFile <- 'global2015' #location where files that are created are to be saved

# if the ohi-global data is updated these should be changed to TRUE
# (note: these files are then read in for all subsequent tables/figures)
radical1 <- FALSE
radical2 <- FALSE

## General files to load
rgn_names <- read.csv(sprintf('eez%s/layers/rgn_global.csv', scenario)) %>%
  select(region_id = rgn_id, country = label)
#-----------------------------------------
```

#<a name="saving"></a>Saving data files for website

Data files to generate content for http://www.oceanhealthindex.org/.

Output files: 

* [radical_*date*.csv](`r sprintf('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/%s/radical_%s.csv', saveFile, radicalFile)`). This file is also used to generate the tables and figures in this document.
* [`r sprintf('radicalv2_eez%s_*date*.csv', scenario)`](`r sprintf('https://raw.githubusercontent.com/OHI-Science/ohi-global/draft/%s/radicalv2_eez2015_%s.csv', saveFile, radicalFile)`)
 
 (**NOTE:** The code in the following code chunks will need to be modified when new scenarios are added)

```{r websites data, include=FALSE}

setwd(dir_global)


## These are run and saved if radical1 and radical2 arguments are TRUE
# NOTE: radical_scores.R, compiles all scenarios using the following combinations:
# 2012 = eez2012
# 2013 = eez2013
# 2014 = eez2014 and antarctica2014 and highseas2014
# 2015 = eez2015 and antarctica2014 and highseas2014
# this function needs to be updated when these scenarios are updated
source('global2015/radical_scores.R')

## This calls a file called layers_2015.csv that includes information about
## the metadata for each layer file.  This will need to be updated if any of the 
## layers change in future analyses.
source('global2015/Radical_scores_v2.R')


```


#<a name="tables"></a>Human readable tables
Tables of the results are saved to this location (github:ohi-global/`r saveFile`/data).

###EEZ scores for 2015
Outputs (include both csv and html formatted tables): 
*scores_...*.csv and .html 

```{r score table, include=FALSE}

setwd(dir_global)

data <- read.csv(sprintf('global2015/radical_%s.csv', radicalFile)) 

data <- data[data$scenario == scenario, ]

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  %>%         # Antarctica (calculated in a very different way)
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(country = ifelse(is.na(country), "eez_weighted_avg", as.character(country))) %>%
  mutate(value = round(value, 0))

data <- spread(data, goal, value)

index <- data %>%
  filter(country == 'eez_weighted_avg')

data <- data %>%
  arrange(-Index) %>%
  filter(country != 'eez_weighted_avg')

data <- rbind(index, data) %>%
    select(scenario, dimension, country, region_id, Index, AO, SPP, BD, HAB, CP, CS, CW, ECO, LE, LIV, FIS, FP, MAR, ICO, SP, LSP, NP, TR)

write.csv(data, sprintf("%s/Reporting/data/scores_eez%s.csv", saveFile, scenario), row.names = FALSE, na='')

## make an html file that is color coded:
pal = brewer.pal(10, 'RdYlBu')

cols <- data.frame(country=data$country)
for(goal in goals){ #goal="Index"
  tmp <- data[, goal]
  tmp <- assign(goal, cut(tmp, breaks=c(0,10,20,30,40,50,60,70,80,90,100), include.lowest = TRUE, labels=pal))
  tmp <- data.frame(goal=tmp)
  names(tmp) <- goal
  cols <- cbind(cols, tmp)
}


hwrite(data, sprintf('%s/Reporting/data/scores_eez%s.html', saveFile, scenario), br=TRUE, center=TRUE, border=0, 
       row.style=list(goal='text-align:center'), table.style='padding: 10px; margin:20px;', 
       col.bgcolor=list(scenario='#fff',dimension='#fff',country='#fff', region_id='#fff', Index = cols$Index, 
                        AO = cols$AO, SPP = cols$SPP, BD = cols$BD, HAB = cols$HAB, CP = cols$CP, CS = cols$CS, CW = cols$CW, 
                        ECO = cols$ECO, LE = cols$LE, LIV = cols$LIV, FIS = cols$FIS, FP = cols$FP, MAR = cols$MAR, ICO = cols$ICO, 
                        SP = cols$SP, LSP = cols$LSP, NP = cols$NP, TR = cols$TR))


```

###Difference between old and new scores using 2013 benchmark
Outputs (include both csv and html formatted tables): 
*change_in_scores_benchmark...*.csv and .html 

 
```{r difference table, include=FALSE}

setwd(dir_global)

data <- read.csv(sprintf('%s/radical_%s.csv', saveFile, radicalFile)) 

data <- data[data$scenario == benchmark, ]

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  

# get the older data
oldDataAddress <- paste0('https://raw.githubusercontent.com/',
                         'OHI-Science/ohi-global/', oldCommit,
                        sprintf('/eez%s/scores.csv', benchmark))

oldData <- repmis::source_data(oldDataAddress) %>%
  filter(dimension == "score") %>%
  filter(region_id != 213) %>%
  select(goal, dimension, region_id, old_value=score)

oldData$scenario <- benchmark

compare <- data %>%
  left_join(oldData) %>%
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(country = ifelse(is.na(country), "eez_weighted_avg", as.character(country))) 

compare_wide <- compare %>%
  mutate(change_in_score = round((value - old_value), 2)) %>%
  select(scenario, goal, dimension, country, region_id, change_in_score) %>%
  spread(goal, change_in_score)

index <- compare_wide %>%
  filter(country == 'eez_weighted_avg')

compare_wide <- compare_wide %>%
  arrange(-Index) %>%
  filter(country != 'eez_weighted_avg')

compare_wide <- rbind(index, compare_wide) %>%
    select(scenario, dimension, country, region_id, Index, AO, SPP, BD, HAB, CP, CS, CW, ECO, LE, LIV, FIS, FP, MAR, ICO, SP, LSP, NP, TR)

write.csv(compare_wide, sprintf("%s/Reporting/data/change_in_scores_benchmark%s_eez%s.csv", saveFile, benchmark, scenario), row.names = FALSE, na='')

## make an html file that is color coded:
pal = brewer.pal(10, 'RdYlBu')

cols <- data.frame(country=compare_wide$country)
for(goal in goals){ #goal="CW"
  tmp <- compare_wide[, goal]
   tmp <- assign(goal, cut(tmp, breaks=c(-100, -50, -30, -20, -10, 0, 10, 20, 30, 50, 100), include.lowest = TRUE, labels=pal))
  tmp <- data.frame(goal=tmp)
  names(tmp) <- goal
  cols <- cbind(cols, tmp)
}


hwrite(compare_wide, sprintf('%s/Reporting/data/change_in_scores_benchmark%s_eez%s.html', saveFile, benchmark, scenario), br=TRUE, center=TRUE, border=0, 
       row.style=list(goal='text-align:center'), table.style='padding: 10px; margin:20px;', 
       col.bgcolor=list(scenario='#fff',dimension='#fff',country='#fff', region_id='#fff', Index = cols$Index, 
                        AO = cols$AO, SPP = cols$SPP, BD = cols$BD, HAB = cols$HAB, CP = cols$CP, CS = cols$CS, CW = cols$CW, 
                        ECO = cols$ECO, LE = cols$LE, LIV = cols$LIV, FIS = cols$FIS, FP = cols$FP, MAR = cols$MAR, ICO = cols$ICO, 
                        SP = cols$SP, LSP = cols$LSP, NP = cols$NP, TR = cols$TR))


```

###Trend data from 2012 to 2015 scenarios
Outputs (include both csv and html formatted tables): 
*trends...*.csv and .html 

```{r trends, include=FALSE}

setwd(dir_global)

data <- read.csv(sprintf('%s/radical_%s.csv', saveFile, radicalFile)) 

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  

trends <- data %>%
  filter(!is.na(value)) %>%
  mutate(goal = as.character(goal)) %>%
  group_by(goal, region_id) %>%
  do(mdl = lm(value ~ scenario, data = .)) %>%
  summarize(goal = goal, region_id = region_id,
            trend = coef(mdl)['scenario']) %>%
  ungroup()


trends <- trends %>%  
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(country = ifelse(is.na(country), "eez_weighted_avg", as.character(country))) %>%
  mutate(trend = round(trend, 2)) %>%
  select(goal, country, region_id, trend) %>%
  data.frame()

trends <- spread(trends, goal, trend)

index <- trends %>%
  filter(country == 'eez_weighted_avg')

trends <- trends %>%
  arrange(-Index) %>%
  filter(country != 'eez_weighted_avg')

trends <- rbind(index, trends) %>%
    select(country, Index, region_id, AO, SPP, BD, HAB, CP, CS, CW, ECO, LE, LIV, FIS, FP, MAR, ICO, SP, LSP, NP, TR)

write.csv(trends, sprintf("%s/Reporting/data/trends.csv", saveFile, benchmark, scenario), row.names = FALSE, na='')

## make an html file that is color coded:
pal = brewer.pal(10, 'RdYlBu')

cols <- data.frame(country=trends$country)
for(goal in goals){ #goal="CW"
  tmp <- trends[, goal]
  tmp <- assign(goal, cut(tmp, breaks=c(-1000, -10, -5, -2, -1, 0, 1, 2, 5, 10, 1000), include.lowest = TRUE, labels=pal))
  tmp <- data.frame(goal=tmp)
  names(tmp) <- goal
  cols <- cbind(cols, tmp)
}


hwrite(trends, sprintf('%s/Reporting/data/trends.html', saveFile), br=TRUE, center=TRUE, border=0, 
       row.style=list(goal='text-align:center'), table.style='padding: 10px; margin:20px;', 
       col.bgcolor=list(scenario='#fff',dimension='#fff',country='#fff', region_id='#fff', Index = cols$Index, 
                        AO = cols$AO, SPP = cols$SPP, BD = cols$BD, HAB = cols$HAB, CP = cols$CP, CS = cols$CS, CW = cols$CW, 
                        ECO = cols$ECO, LE = cols$LE, LIV = cols$LIV, FIS = cols$FIS, FP = cols$FP, MAR = cols$MAR, ICO = cols$ICO, 
                        SP = cols$SP, LSP = cols$LSP, NP = cols$NP, TR = cols$TR))


```

###Status years used in the 2012 to 2015 scenarios

```{r status years, warning=FALSE, error=FALSE, message=FALSE, echo=FALSE}

setwd(dir_global)

scenarios <- 2012:scenario

data <- data.frame(goals = goals[-1])

for (scenarioYear in scenarios){ # scenarioYear = 2015

    f <-  read.csv(sprintf('eez%s/conf/goals.csv', scenarioYear)) %>%
      select(goal, preindex_function)

goalsYears <- c()    
    for(goal in goals[-1]){ # goal = "FIS"  goal = "AO"
    g <- f[f$goal == goal, ]
    year <- as.numeric(gsub("[^\\d]+", "", g$preindex_function, perl=TRUE))
    
    year <- ifelse(length(year)==0, NA, year)
    goalsYears <- c(goalsYears, year)
    }

goalsYears <- data.frame(goalsYears)
names(goalsYears) <- paste('eez', scenarioYear, sep="_")
data <- cbind(data, goalsYears)
}

kable(data,format="pandoc",caption="Years used in analysis")

```

#<a name="figures"></a>Figures
###<a name="carpet"></a>Carpet plot from 2012 to 2015 scenarios
Outputs (see png file for details): 
*carpetPlot.png* 

```{r carpet plot, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE, fig.width=14, fig.height=23}

setwd(dir_global)

data <- read.csv(sprintf('%s/radical_%s.csv', saveFile, radicalFile)) 

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  %>%
  mutate(value = round(value, 0)) %>%
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(country = ifelse(is.na(country), "eez_weighted_avg", as.character(country))) %>%
  group_by(region_id) %>% 
  mutate(meanIndex=mean(value[goal=="Index"])) %>%
  ungroup() %>%
  data.frame()
  
data$goal <- factor(data$goal, levels = goals)

myPalette <- colorRampPalette(brewer.pal(10, "RdYlBu"))
ggplot(data, aes(y=factor(country, levels=(country)[order(meanIndex)]), x=scenario, fill=value)) + 
  geom_tile(aes(order=meanIndex)) +
  facet_grid(~goal) + 
  scale_fill_gradientn(colours=myPalette(100), na.value="black") +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5)) +
  ylab("") + 
  xlab("")
ggsave(sprintf("%s/Reporting/figures/carpetPlot.png", saveFile), width=20, height=25, units="in")


```

###<a name="maps"></a>Maps

``` {r Maps, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}

dir_rept <- sprintf('%s/global2015/Reporting', dir_global)
source(file.path(dir_rept, 'map_fxns.R'))

### set scenario and desired map projection
scenario <- 2015
prj      <- 'mol'    ### note: 'gcs' is way faster.

### get OHI data and rename column headings
scores_df <- read.csv(file.path(dir_rept, sprintf('data/scores_eez%s.csv', scenario)), stringsAsFactors = FALSE) %>%
  rename(rgn_name = country, rgn_id = region_id)

### load region data frame, so doesn't need to reload every time through the loop.  Also
### load the land data frame, if plotting in Mollweide projection.
rgn_df <- get_rgn_df(prj = prj)
if(prj == 'mol' & !exists('land_poly')) {
  land_poly  <- get_land_df()
  ocean_poly <- get_ocean_df() ### assume if land_poly doesn't exist, ocean_poly doesn't either...
}


### establish list of fields for mapping
mapFlds   <- names(scores_df %>% select(-rgn_name, -rgn_id, -scenario, -dimension))

### Loop over each field, plotting each map in turn and saving to file.
for (fld in mapFlds) { # fld <- mapFlds[1]

   fig_save = file.path(dir_rept, sprintf('figures/maps_by_goal_%s/global_map_%s_%s_%s.png', prj, fld, scenario, prj))
   ohiplot <- plot_scores_easy(scores_df, fld, rgn_df, title = title, prj = prj, fig_save = fig_save)
   
   print(ohiplot)
}

```

###<a name="scatter"></a>Scatterplots comparing the current analysis and the 2014 analysis

```{r scatter plot: old vs new, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}
#-------------------------
  criteria <- ~dimension == score
#-------------------------

# uses compare data calculated above

setwd(dir_global)

for(goal in goals){ # goal = "AO"

data_new <- compare %>%
    mutate(change = value - old_value) %>%
    group_by(goal) %>% 
    mutate(mean = mean(change, na.rm=TRUE),
           sd =  sd(change, na.rm=TRUE)) %>%
    ungroup() %>%
    mutate(z_score = (change - mean)/sd) %>%
    mutate(z_greater_1 = ifelse(abs(z_score) > 1, "yes", "no")) %>%
    filter(region_id != 0) %>%
    mutate(plotLabel = ifelse(z_greater_1=="yes", as.character(country), NA))
  
  data_new <- data_new[data_new$goal==goal,]  

p <-   ggplot(data_new, aes(x=old_value, y=value)) +
    geom_point(shape=19) +
    theme_bw() + 
    labs(title=paste(benchmark, goal, sep=": "), y="New scores", x="Old scores") +
    geom_abline(slope=1, intercept=0, color="red") +
    geom_text(aes(label=plotLabel), vjust=1.5, size=2) +
  xlim(0, 100) +
  ylim(0, 100)

print(p)
}

```

###<a name="googlevis"></a>GoogleVis plot

```{r GoogleVis, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE}

setwd(dir_global)

data <- read.csv(sprintf('%s/radical_%s.csv', saveFile, radicalFile)) 

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)  %>%
  mutate(value = round(value, 2)) %>%
  left_join(rgn_names, by=c('region_id')) %>%
  mutate(country = ifelse(is.na(country), "eez_weighted_avg", as.character(country))) %>%
  select(year=scenario, goal, country, score=value)

data <- spread(data, goal, score)

Motion=gvisMotionChart(data, 
                       idvar="country", 
                       timevar="year")
#plot(Motion)

print(Motion, file=sprintf('%s/Reporting/figures/GoogleVisScores.html', saveFile))


```

###<a name="flower"></a>Flower plots

```{r Flower plots, message=FALSE, warning=FALSE, error=FALSE, echo=FALSE, fig.width=4, fig.height=4}

setwd(dir_global)

## weights for FIS vs. MAR
weights <- read.csv(sprintf("eez%s/layers/fp_wildcaught_weight.csv", scenario), stringsAsFactors=FALSE)
weights_global <- data.frame(rgn_id=0, w_fis=mean(weights$w_fis))
weights <- rbind(weights_global, weights)

# getting the goals that will be plotted:
conf <-  read.csv(sprintf("eez%s/conf/goals.csv", scenario), stringsAsFactors=FALSE) 

goals_supra = na.omit(unique(conf$parent)) # goals comprised of subgoals, not included in plot

conf <- conf %>%
  filter(!(goal %in% goals_supra)) %>%
  select(goal, order_color, order_hierarchy, weight, name_flower) %>%
  mutate(name_flower = gsub("\\n", "\n", name_flower, fixed = TRUE)) %>%
  arrange(order_hierarchy)


data <- read.csv(sprintf('%s/radical_%s.csv', saveFile, radicalFile), stringsAsFactors=FALSE) 
data <- data[data$scenario == scenario, ]

data <- data %>%
  filter(dimension == "score") %>%   # focus only on score data
  filter(region_id != 0) %>%         # this weighted mean includes high seas and Antarctica
  mutate(region_id = ifelse(region_id==300, 0, region_id)) %>%   #convert the 300 (i.e., only eez's averaged to zero)
  filter(region_id <= 250) %>%       # get rid of high seas regions
  filter(region_id != 213)

# region names, ordered by GLOBAL and alphabetical
rgn_names2 = rbind(
  data.frame(
    region_id=0, 
    country='GLOBAL'),
  rgn_names) %>%
    arrange(country) %>%
  filter(region_id != 213)

# loop through regions to plot flowers
for (rgn_id in unique(rgn_names2$region_id)){  #rgn_id=0
   
  # header md
  rgn_name = subset(rgn_names2, region_id==rgn_id, country, drop=T)
  message(sprintf('\n## %s (%d)\n\n', rgn_name, rgn_id))
  
    # region scores    
  g_x <- subset(data, region_id==rgn_id) %>%
         inner_join(conf, by="goal") %>%
         arrange(order_color)
  x <-  subset(data, region_id==rgn_id & goal == 'Index', value, drop=T)

    # get colors for aster, based on 10 colors, but extended to all goals. subselect for goals.wts
if(colorScheme == "new"){
  g_x$cols.goals.all = cut(g_x$value, breaks=seq(0, 100, by=10), include.lowest=TRUE, 
                       labels=RColorBrewer::brewer.pal(10, 'RdYlBu')) } else {
    g_x$cols.goals.all = colorRampPalette(RColorBrewer::brewer.pal(11, 'Spectral'), space='Lab')(length(goals.all))
   }

       #weights after correcting for fisheries/mariculture contributions
  g_x$weight[g_x$goal == "FIS"] <-   weights$w_fis[weights$rgn_id == rgn_id]
  g_x$weight[g_x$goal == "MAR"] <- 1 - weights$w_fis[weights$rgn_id == rgn_id]
  
        
  # res=72
      
  res=150
   ## start plot
   png(sprintf('%s/Reporting/figures/FlowerPlots/flower_%s.png', saveFile, rgn_name),
          width=res*6, height=res*6, bg = "transparent")
#par(oma=c(0,0,3,0), mar=c(6, 4, 0, 2) + 0.1)
   PlotFlower(main = rgn_name,
                 lengths=ifelse(
                   is.na(g_x$value),
                   100,
                   g_x$value),
                 widths=g_x$weight,
                 fill.col=ifelse(
                   is.na(g_x$cols.goals.all), 
                   'grey80', 
                   as.character(g_x$cols.goals.all)),
                 labels  =ifelse(
                   is.na(g_x$value), 
                   paste(g_x$name_flower, '-', sep='\n'), 
                   paste(as.character(g_x$name_flower), round(g_x$value), sep='\n')),
                 center=round(x),
               #  max.length = 100, disk=0.4, label.cex=0.9, label.offset=0.155, cex=2.2, cex.main=2.5)
           max.length = 100, disk=0.3, label.cex=1.5, label.offset=0.15, cex=3, cex.main=3)

      dev.off()      
      #system(sprintf('convert -density 150x150 %s %s', fig_pdf, fig_png)) # imagemagick's convert
  
    
PlotFlower(main = rgn_name,
                 lengths=ifelse(
                   is.na(g_x$value),
                   100,
                   g_x$value),
                 widths=g_x$weight,
                 fill.col=ifelse(
                   is.na(g_x$cols.goals.all), 
                   'grey80', 
                   as.character(g_x$cols.goals.all)),
                 labels  =ifelse(
                   is.na(g_x$value), 
                   paste(g_x$name_flower, '-', sep='\n'), 
                   paste(as.character(g_x$name_flower), round(g_x$value), sep='\n')),
                 center=round(x),
                max.length = 100, disk=0.4, label.cex=0.5, label.offset=0.19, cex=1.2, cex.main=1.2, uin=1)
  }
  

```