---
title: "Score Checking"
author: "Mel"
date: "9/16/2015"
output: html_document
---

```{r, echo=FALSE}
library(tidyr)
library(dplyr)
library("RCurl", lib.loc="~/R/x86_64-pc-linux-gnu-library/3.2")
library(curl)
```


The purpose of this document is to explore the questions we have about particular scores.  

Question 1: Why the change in UK HAB/CP scores?
Answer: Appears to be due to sea ice (edge and shoreline)
```{r}

region <- 180 #United Kingdom
tmp <- data.frame()

for (scenario in 2012:2015){ #scenario <- 2015

extent <- read.csv(sprintf('eez%s/layers/hab_extent.csv', scenario)) %>%
  mutate(variable = 'extent') %>%
  select(rgn_id, variable, habitat, score=km2)
health <- read.csv(sprintf('eez%s/layers/hab_health.csv', scenario))%>%
  mutate(variable = 'health') %>%
  select(rgn_id, variable, habitat, score=health)
trend <- read.csv(sprintf('eez%s/layers/hab_trend.csv', scenario)) %>%
  mutate(variable = 'trend') %>%
  select(rgn_id, variable, habitat, score=trend)

allHab <- rbind(extent, health, trend) 
allHab$scenario = scenario

tmp <- rbind(tmp, allHab[allHab$rgn_id==region, ])

}

tmp2 <- tmp %>%
  filter(!(variable=="extent" & score == 0)) %>%
  arrange(variable, habitat, scenario) %>%
  filter(variable != "extent")



```



Question 2: What caused Mozambique to have increased NP scores?
Answer: Appears to be due to sea ice (edge and shoreline)
```{r}

region <- 41 #Mozambique

np <- read.csv(sprintf('eez%s/layers/np_harvest_tonnes_relative.csv', scenario)) %>%
  filter(year>2005) %>%
  spread(year, tonnes_rel)

np <- np[np$rgn_id==region, ]
  
np_t <- read.csv(sprintf('eez%s/layers/np_harvest_tonnes.csv', scenario)) %>%
  filter(year>2005) %>%
  spread(year, tonnes)

np_t[np_t$rgn_id==region, ]
  

```

Question 3: Why are Israel's CW scores so low?
Answer: Appears to be due to sea ice (edge and shoreline)
```{r}

region <- 79 #Israel

read.csv('eez2014/scores.csv') %>%
  filter(region_id == region) %>%
  filter(goal == "CW")

read.csv('eez2014/layers/po_pathogens.csv') %>%
  filter(rgn_id == region) %>%
  mutate(score = 1- pressure_score)

read.csv('eez2014/layers/po_trash.csv') %>%
  filter(rgn_id == region)%>%
  mutate(score = 1- pressure_score)

read.csv('eez2014/layers/po_chemicals_3nm.csv') %>%
  filter(rgn_id == region)%>%
  mutate(score = 1- pressure_score)

read.csv('eez2014/layers/po_nutrients_3nm.csv') %>%
  filter(rgn_id == region)%>%
  mutate(score = 1- pressure_score)

### compare to 2014 analysis:

v2014.3_url = 'https://raw.githubusercontent.com/OHI-Science/ohi-global/4da6b4a1d69d694264ea68456359a939b0c03f9c/eez2014/'
read.csv(curl(file.path(v2014.3_url, 'layers/po_pathogens.csv'))) %>%
  filter(rgn_id==region)%>%
  mutate(score = 1- pressure_score)

read.csv(curl(file.path(v2014.3_url, 'layers/po_trash.csv'))) %>%
  filter(rgn_id==region)%>%
  mutate(score = 1- pressure_score)


### Note these measurements are based on the entire eez! rather than 3nm as we did in 2015:
read.csv(curl(file.path(v2014.3_url, 'layers/po_chemicals.csv'))) %>%
  filter(rgn_id==region)%>%
  mutate(score = 1- pressure_score)

read.csv(curl(file.path(v2014.3_url, 'layers/po_nutrients.csv'))) %>%
  filter(rgn_id==region)%>%
  mutate(score = 1- pressure_score)

```


Question 4: Brazil + Trinidade Goal score for FIS is 1000 (rgn = 171)?
Answer: Not sure what is going on...data looks correct on my end....
```{r}

data1 <- read.csv('global2015/radicalv2_2015_2015-09-30.csv')
region <- 171 #Brazil and Trinidade

data1 %>%
  filter(region_id==171) %>%
  filter(goal=="FIS") %>%
  select(-source)

```
