---
title: "Calculating % contribution of gapfilling to status/trend"
author: "Mel"
date: "9/4/2015"
output: html_document
---

```{r, warning=FALSE, message=FALSE}
# load libraries
library(tidyr)
library(dplyr)

setwd('/home/frazier/ohi-global/global2015/gapFilling') # comment this out when knitting!!!

# list of regions:
regions <- read.csv('../../../ohiprep/src/LookupTables/eez_rgn_2013master.csv') %>%
  select(rgn_id = rgn_id_2013) %>%
  filter(rgn_id < 255) %>%  # Disputed regions
  filter(rgn_id != 213) %>% # Antarctica
  arrange(rgn_id) %>%
  unique()

# create empty scores.csv file for gap-filling data
tmp <- data.frame("goal" = NA,"dimension" = NA,"region_id" = NA,"score" = NA)

write.csv(tmp, 'scores.csv', row.names=FALSE)

```


## General notes
This document calculates the proportion of each goal's status and trend scores that are based on gap-filled data.  All gap-filling is weighted equally.  

I am only focusing on the 2015 data, although some layers have additional years.

I ignore LE/ECO/LIV because we will be changing these data.

I haven't done the pressures and resilience yet - but I am going to work on this next.  Once I have that, I can calculate the proportion of each goal's score that is based on gap-filled data.

Eventually, I want to do these calculations using the error introduced by gap-filling based on cross-validation methods.

## Species Diversity
There is no gap-filling for status calculations of this subgoal.  I believe there are many species that lack trend data (but are included in the status calculation).  This may be a form of gap-filling because the species that are not included are functionally given the average trend of the species that do have trend data.  However, at this point, I am assuming no gapfilling for trend. I think this is defensible because it is a random sample of the species data that do not have trends.

```{r spp, warning=FALSE, message=FALSE}
scores_SPP <- read.csv('../../eez2015/scores.csv') %>%
  filter(goal == 'SPP') %>%
  filter(dimension %in% c('status', 'trend')) %>%
  filter(region_id != 0) %>%
  mutate(score = ifelse(!is.na(score), 0, NA)) 

tmp <- read.csv('scores.csv')
write.csv(rbind(tmp, scores_SPP), 'scores.csv', row.names=FALSE, na="")

```


## Iconic species
See Species goal.

```{r ico, warning=FALSE, message=FALSE}

scores_ICO <- read.csv('../../eez2015/scores.csv') %>%
  filter(goal == 'ICO') %>%
  filter(dimension %in% c('status', 'trend')) %>%
  filter(region_id != 0) %>%
  mutate(score = ifelse(!is.na(score), 0, NA)) 

tmp <- read.csv('scores.csv')
tmp <- na.omit(tmp) ## get rid of NA values when dataframe was created
write.csv(rbind(tmp, scores_ICO), 'scores.csv', row.names=FALSE, na="")

```


## Livelihoods and Economies
I do not gapfill this goal (or corresponding subgoals) because the source data have been discontinued and we are revising the model.  However, I realized I should put in a place holder for these to make it clear that these are not estimated.

```{r LE, warning=FALSE, message=FALSE}

scores_LIV <- read.csv('../../eez2015/scores.csv') %>%
  filter(goal == 'LIV') %>%
  filter(dimension %in% c('status', 'trend')) %>%
  filter(region_id != 0) %>%
  mutate(score = NA) 

scores_ECO <- read.csv('../../eez2015/scores.csv') %>%
  filter(goal == 'ECO') %>%
  filter(dimension %in% c('status', 'trend')) %>%
  filter(region_id != 0) %>%
  mutate(score = NA) 

tmp <- read.csv('scores.csv')
write.csv(rbind(tmp, scores_LIV, scores_ECO), 'scores.csv', row.names=FALSE, na="")

```


## Lasting Special Places
There is no gap-filling for status calculations of this subgoal.  

```{r lsp, warning=FALSE, message=FALSE}

scores_LSP <- read.csv('../../eez2015/scores.csv') %>%
  filter(goal == 'LSP') %>%
  filter(dimension %in% c('status', 'trend')) %>%
  filter(region_id != 0) %>%
  mutate(score = ifelse(!is.na(score), 0, NA)) 

tmp <- read.csv('scores.csv')
write.csv(rbind(tmp, scores_LSP), 'scores.csv', row.names=FALSE, na="")

```


## Artisanal Opportunities
Need and access equally contribute to the status calculation of this goal.  Gap-filling was calculated as:
$x_{ao}=\frac{(access_{gf} + need_{gf})}{2}$
where, 
$access_{gp}$ = 1, if gap-filled; 0, if not gap-filled
$need_{gp}$ = 1, if gap-filled; 0, if not gap-filled

NOTES: 
- spatial gapfilling based on the UN r2 designations and dissagregation from 2012 to 2013
- assume status and trend have the same gap-filling

```{r ao, warning=FALSE, message=FALSE}

scores_AO <- read.csv('../../eez2015/scores.csv') %>%
   filter(goal == 'AO') %>%
   filter(dimension == "score") %>%
   filter(region_id != 0) %>%
   select(region_id, goal, score)
 
access <- read.csv('layers/ao_access.csv') %>%
   select(region_id = rgn_id, gapfill=value)
  
need <- read.csv('layers/ao_need.csv') %>%
  select(region_id = rgn_id, gapfill)

status_AO <- rbind(access, need) %>%
  group_by(region_id) %>%
  summarize(status_gf = sum(gapfill)/2) %>% ## if either variable has an NA, these should drop
  left_join(scores_AO) %>%
  filter(!is.na(score)) %>%
  mutate(dimension = 'status') %>%
  mutate(year = 2015) %>%
  select(goal, dimension, region_id, score=status_gf)

trend_AO <- status_AO %>%
  mutate(dimension = "trend")

scores_AO <- rbind(status_AO, trend_AO)

tmp <- read.csv('scores.csv')
write.csv(rbind(tmp, scores_AO), 'scores.csv', row.names=FALSE, na="")
 
``` 


## Habitat (extent, trend, condition)

These data are used for: CP, CS, HAB, and some pressures

The habitat gap-filling has some documentation at: Neptune:\GL-NCEAS_Habitat_health-v2013a\tmp\Habitat_whence.  However, one type of gap-filling that was not accounted for in the previous analysis was the "dissaggregation" of data that occurred when new regions were added for the 2013 analysis.  

When a habitat is present in a region, but does not have corresponding trend data, this habitat is excluded from the calculation which is functionally a form of gap-filling because the trend is assumed to be the average of the other habitats.  If only one habitat is relevant to the goal calculation within a region, and doesn't have a trend value, when final scores are calculated, the trend is given a zero.  There are many examples of this for seagrass and mangrove.  This suggests we should really fill in these gaps in a more sensible way prior to the analysis.  Given this, I consider the trend for these habitats to be gap-filled.

Summary of gap-filling for each habitat

Habitat      | Variable                  | Notes
------------- | ------------------------ | -------------
soft_bottom   | extent                | none
--  | trend, condition  | disaggregation from 2012 to 2013
coral        | extent                    | none
--             | trend                     | disaggregation
--             | condition                 | adjacent, georegion, prediction (considered actual), disaggregation
seagrass     | extent                    | none
--             | trend                     | georegion, disaggregation
--               condition                 | actuals-mixed (considered actual), prediction (considered actual, but this might be wrong), adjacent, adjacent-georegion, georegion, disaggregation
salt_marsh   | extent  | none
--   | trend, condition  | disaggregation
sea_ice      | extent, trend, condition  | none
mangrove     | extent                    | none
--             | trend                     | 3 regions reported as one, regional (r2 mean)
--             | condition                 | disaggregation, regional (r1 and r2 means)

Sea grass description for SOM 2012: 
'Seagrass Status and Trend data were calculated on a per-site basis from ref 90, which provides seagrass habitat extent data for several sites around the world over several years. Habitat condition (health) data came from these data, where the reference condition is the mean of the three oldest years between 1975-1985, or the two earliest years if needed. If data responding to these conditions was not available, we fitted a linear model to all data points, and then used the mean of the predicted values for 1979-1981 as the reference condition. For the current condition we used the mean of the three most recent years after 2000 or the two most recent years. If condition data satisfying these constraints were still not available, we fitted a linear model to all data points, provided that there were at least three data points and then used the mean of the predicted values for 2008-2010 as the current condition and the mean of the predicted values for 1979-1981 as the reference condition. Otherwise, we used neighboring (adjacent) regional averages, weighted by habitat area, or averages weighted by habitat area using seagrass geographical regions as defined by Hemminga and Duarte91. We did not project beyond a 15-year timeframe.'


* disaggregation occurred during the 2013 analysis when many additional countries were added to the analysis.  In these cases, trend and health were given the same scores as the sovereign country. Often disaggregation is paired with another type of gap-filling.  These regions will tend to have even more uncertainty, but I don't account for this here.

All forms of gap-filling will be considered equal for habitat extent, trend, condition.

### Coastal Protection

This calculates the relative proportion of the status value estimated using gap-filled data for each country, based on the following equation:

$x_{cp}=\frac{\sum_{i=1}^{k}A * w*{E_{p}}}{\sum_{1=1}^{k}A * w}$
where, 
$i$ = habitats (coral, mangrove, saltmarsh, seagrass, sea ice (shoreline))
$A$ = extent area (km2)
$w$ = rank protective ability of the habitat
$E_{p}$ = proportion of variables estimated (area and health can be estimated)

The same method was used to calculate trend, by replacing condition (C) with trend (T). 


```{r coastal protection, warning=FALSE, message=FALSE}
 
 # I think i might need to convert NA trend/health to 1 for gap-filling....
 
# habitat rank data 
habitat_rank <- data.frame(habitat =c('coral', 'mangrove', 'saltmarsh', 'seagrass', 'seaice_shoreline'),
                   rank =c(4, 4, 3, 1, 4))
  
# gap-fill data 
extent_gf <- read.csv('layers/hab_extent.csv') %>%
  filter(habitat %in% habitat_rank$habitat) %>%
  select(rgn_id, habitat, gap_fill_extent=gap_fill) %>%
  filter(!is.na(gap_fill_extent))

condition_gf <- read.csv('layers/hab_health.csv') %>%
  filter(habitat %in% habitat_rank$habitat) %>%
  select(rgn_id, habitat, gap_fill_health=gap_fill)
  
trend_gf <-  read.csv('layers/hab_trend.csv') %>%
  filter(habitat %in% habitat_rank$habitat) %>%
  select(rgn_id, habitat, gap_fill_trend = gap_fill)

# extent/condition/trend data for 2015
extent <- read.csv('../../eez2015/layers/hab_extent.csv') %>%
  filter(km2 > 0)%>%
  filter(habitat %in% habitat_rank$habitat) 
condition <- read.csv('../../eez2015/layers/hab_health.csv')%>%
  filter(habitat %in% habitat_rank$habitat) 
trend <- read.csv('../../eez2015/layers/hab_trend.csv')%>%
  filter(habitat %in% habitat_rank$habitat) 

data <- extent %>%
  left_join(condition) %>%
  left_join(trend) %>%
  left_join(extent_gf) %>%
  left_join(condition_gf) %>%
  left_join(trend_gf) %>%
  left_join(habitat_rank) %>%
  filter(rgn_id < 255) %>%
  filter(!is.na(health) & !is.na(km2)) %>%
  mutate(gap_fill_extent = ifelse(gap_fill_extent==0, 0, 1)) %>%
  mutate(gap_fill_health = ifelse(gap_fill_health==0, 0, 1)) %>%
  mutate(gap_fill_trend = ifelse(gap_fill_trend==0, 0, 1))


## calculate status:
status_CP <- data %>%
  mutate(prop_gf_status = (gap_fill_extent + gap_fill_health)/2) %>%
  mutate(a_p_est = km2 * rank * prop_gf_status) %>%
  mutate(a_p = km2 * rank)
  
status_CP <- status_CP %>%
  group_by(rgn_id) %>%
  summarize(sum_a_p_est = sum(a_p_est),
            sum_a_p = sum(a_p)) %>%
  ungroup() %>%
  mutate(status_gf = sum_a_p_est/sum_a_p)

status_CP <- status_CP %>%
  mutate(goal = "CP") %>%
  mutate(dimension = "status") %>%
  mutate(year = 2015) %>%
  select(goal, dimension, region_id = rgn_id, score=status_gf)

## calculate trend: 
trend_CP <- data %>%
  mutate(prop_gf_trend = (gap_fill_extent + gap_fill_trend)/2) %>%
  mutate(a_p_est = km2 * rank * prop_gf_trend) %>%
  mutate(a_p = km2 * rank)
  
trend_CP <- trend_CP %>%
  group_by(rgn_id) %>%
  summarize(sum_a_p_est = sum(a_p_est),
            sum_a_p = sum(a_p)) %>%
  ungroup() %>%
  mutate(trend_gf = sum_a_p_est/sum_a_p)

trend_CP <- trend_CP %>%
  mutate(goal = "CP") %>%
  mutate(dimension = "trend") %>%
  mutate(year = 2015) %>%
  select(goal, dimension, region_id = rgn_id, score=trend_gf)

scores_CP <- rbind(status_CP, trend_CP)

tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_CP), 'scores.csv', row.names=FALSE, na="")


```

### Carbon Storage

This calculates the relative proportion of the status value estimated using gap-filled data for each country, based on the following equation:

$x_{cs}=\frac{\sum_{i=1}^{k}A * w*{E_{p}}}{\sum_{1=1}^{k}A * w}$
where, 
$i$ = habitats (mangrove, saltmarsh, seagrass)
$A$ = extent area (km2)
$w$ = carbon storage capacity
$E_{p}$ = proportion of variables estimated (area and health can be estimated)

The same method was used to calculate trend, by replacing condition (C) with trend (T). 



```{r carbon storage, warning=FALSE, message=FALSE}
 

# habitat rank data 
habitat_rank <- data.frame(habitat = c('mangrove', 'saltmarsh', 'seagrass'),  
                           rank = c(139, 210, 83))
    
# gap-fill data 
extent_gf <- read.csv('layers/hab_extent.csv') %>%
  filter(habitat %in% habitat_rank$habitat) %>%
  select(rgn_id, habitat, gap_fill_extent=gap_fill) %>%
  filter(!is.na(gap_fill_extent))

condition_gf <- read.csv('layers/hab_health.csv') %>%
  filter(habitat %in% habitat_rank$habitat) %>%
  select(rgn_id, habitat, gap_fill_health=gap_fill)
  
trend_gf <-  read.csv('layers/hab_trend.csv') %>%
  filter(habitat %in% habitat_rank$habitat) %>%
  select(rgn_id, habitat, gap_fill_trend = gap_fill)

# extent/condition/trend data for 2015
extent <- read.csv('../../eez2015/layers/hab_extent.csv') %>%
  filter(km2 > 0)%>%
  filter(habitat %in% habitat_rank$habitat) 
condition <- read.csv('../../eez2015/layers/hab_health.csv')%>%
  filter(habitat %in% habitat_rank$habitat) 
trend <- read.csv('../../eez2015/layers/hab_trend.csv')%>%
  filter(habitat %in% habitat_rank$habitat) 

data <- extent %>%
  left_join(condition) %>%
  left_join(trend) %>%
  left_join(extent_gf) %>%
  left_join(condition_gf) %>%
  left_join(trend_gf) %>%
  left_join(habitat_rank) %>%
  filter(rgn_id < 255) %>%
  filter(!is.na(health) & !is.na(km2)) %>%
  mutate(gap_fill_extent = ifelse(gap_fill_extent==0, 0, 1)) %>%
  mutate(gap_fill_health = ifelse(gap_fill_health==0, 0, 1)) %>%
  mutate(gap_fill_trend = ifelse(gap_fill_trend==0, 0, 1))


## calculate status:
status_CS <- data %>%
  mutate(prop_gf_status = (gap_fill_extent + gap_fill_health)/2) %>%
  mutate(a_p_est = km2 * rank * prop_gf_status) %>%
  mutate(a_p = km2 * rank)
  
status_CS <- status_CS %>%
  group_by(rgn_id) %>%
  summarize(sum_a_p_est = sum(a_p_est),
            sum_a_p = sum(a_p)) %>%
  ungroup() %>%
  mutate(status_gf = sum_a_p_est/sum_a_p)

status_CS <- status_CS %>%
  mutate(goal = "CS") %>%
  mutate(dimension = "status") %>%
  mutate(year = 2015) %>%
  select(goal, dimension, region_id = rgn_id, score=status_gf)

## calculate trend: 
trend_CS <- data %>%
  mutate(prop_gf_trend = (gap_fill_extent + gap_fill_trend)/2) %>%
  mutate(a_p_est = km2 * rank * prop_gf_trend) %>%
  mutate(a_p = km2 * rank)
  
trend_CS <- trend_CS %>%
  group_by(rgn_id) %>%
  summarize(sum_a_p_est = sum(a_p_est),
            sum_a_p = sum(a_p)) %>%
  ungroup() %>%
  mutate(trend_gf = sum_a_p_est/sum_a_p)

trend_CS <- trend_CS %>%
  mutate(goal = "CS") %>%
  mutate(dimension = "trend") %>%
  mutate(year = 2015) %>%
  select(goal, dimension, region_id = rgn_id, score=trend_gf)

scores_CS <- rbind(status_CS, trend_CS)
tmp <- read.csv('scores.csv')
write.csv(rbind(tmp, scores_CS), 'scores.csv', row.names=FALSE, na="")


```

### Habitat

For each region, the relative proportion of the status based on gap-filled data, is calculated as:

$x_{hab}=\frac{# gap-filled health values}{total # habitats}$
where habitats include: coral, mangrove, saltmarsh, seagrass, seaice (edge and shoreline), and soft bottom).

The same method was used to calculate trend gap-filling. 

```{r habitat, warning=FALSE, message=FALSE}
 
# gap-fill data 
extent_gf <- read.csv('layers/hab_extent.csv') %>%
  select(rgn_id, habitat, gap_fill_extent=gap_fill) %>%
  filter(!is.na(gap_fill_extent))

condition_gf <- read.csv('layers/hab_health.csv') %>%
  select(rgn_id, habitat, gap_fill_health=gap_fill)
  
trend_gf <-  read.csv('layers/hab_trend.csv') %>%
  select(rgn_id, habitat, gap_fill_trend = gap_fill)

# extent/condition/trend data for 2015
extent <- read.csv('../../eez2015/layers/hab_extent.csv') %>%
  filter(km2 > 0) 
condition <- read.csv('../../eez2015/layers/hab_health.csv')
trend <- read.csv('../../eez2015/layers/hab_trend.csv')

data <- extent %>%
  left_join(condition) %>%
  left_join(trend) %>%
  left_join(extent_gf) %>%
  left_join(condition_gf) %>%
  left_join(trend_gf) %>%
  filter(rgn_id < 255) %>%
  filter(!is.na(health) & !is.na(km2)) %>%
  mutate(gap_fill_extent = ifelse(gap_fill_extent==0, 0, 1)) %>%
  mutate(gap_fill_health = ifelse(gap_fill_health==0, 0, 1)) %>%
  mutate(gap_fill_trend = ifelse(gap_fill_trend==0, 0, 1))


## calculate status:
status_HAB <- data %>%
  group_by(rgn_id) %>%
  summarize(score = sum(gap_fill_health)/length(gap_fill_health)) %>%
  ungroup() %>%
  mutate(goal = "HAB") %>%
  mutate(dimension = "status") %>%
  select(goal, dimension, region_id=rgn_id, score)
  
## calculate trend:
trend_HAB <- data %>%
  group_by(rgn_id) %>%
  summarize(score = sum(gap_fill_trend)/length(gap_fill_trend)) %>%
  ungroup() %>%
  mutate(goal = "HAB") %>%
  mutate(dimension = "trend") %>%
  select(goal, dimension, region_id=rgn_id, score)
  
scores_HAB <- rbind(status_HAB, trend_HAB)
tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_HAB), 'scores.csv', row.names=FALSE, na="")


```

### Clean Waters

For each region, the relative proportion of the status score that is calculated using gap-filled data, is calculated as:

$x_{cw}=\frac{# gap-filled cw indices}{total # indices}$
where indices include the one minus the following pressures: pathogens, nutrients(within 3 nm of shore), chemicals (within 3 nm of shore), trash.

The same method was used to calculate trend gap-filling. 

There are 4 pressures datasets used to calculate CW:

dataset   | description    |  gap-filling 
---------- | -------------
pathogens  | proportion of people without access to sanitation scaled by population density | v1 and v2 regional averages within a year for proportion of people without sanitation access, if there was no population data, it just got an NA
fertilizers | modeled based on FAO data  | No gap-filling (?)
chemicals | combined of three data layers: pesticides (proxy for organic pollution) based on modeled FAO data; ocean pollution (shipping and port data); inorganic pollution (based on impervious surface area data)  | pesticide gapfilling, but assume no gapfilling for other variables (read CHI paper, may need to update this).
trash   | pressure is based on global plastics raster data and trend is based on population  | no gap-filling for pressure, 


NOTES: 
- status is calculated using the geometric mean of (1 minus the pressure) values. 
- I don't think there was gap-filling for the chemical and nutrient pressures - but check on this!

```{r clean waters, warning=FALSE, message=FALSE}

##########################
### Pathogens

## status
pathogen_status <- read.csv('layers/po_pathogens.csv') %>% 
  select(region_id = rgn_id, pressure_score)

## trend: determine proportion of years with no data
pathogen_trend <- read.csv('layers/cw_pathogen_trend.csv') %>%
  select(region_id = rgn_id, trend)


###########################
### Nutrients
nutrients_status <- read.csv('layers/po_nutrients_3nm.csv') %>%
  select(region_id = rgn_id, pressure_score = gapfill)

## repeat for trend, given that there was no gapfilling at my level based on below test:
nutrients_trend <- read.csv('layers/cw_fertilizer_trend.csv') %>%
  select(region_id = rgn_id, trend=gapfill)


#################################
## Chemical
## Several variables go into the Chemical trend calculation, none of these have gap-filling....

chemicals_status <- read.csv('layers/po_chemicals_3nm.csv') %>%
  select(region_id = rgn_id, pressure_score=gapfill)

chemicals_trend <- read.csv('layers/cw_pesticide_trend.csv') %>%
  select(region_id = rgn_id, trend=gapfill)


#################################
## Trash
## status is based on global plastics dataset and trend is based on population data

trash_status <- read.csv('layers/po_trash.csv') %>%
  select(region_id = rgn_id, pressure_score)

trash_trend <- read.csv('layers/cw_coastalpopn_trend.csv') %>%
  select(region_id = rgn_id, trend)



## calculate overall CW status gap-filling:
status_CW <- rbind(pathogen_status, nutrients_status, chemicals_status, trash_status)

status_CW <- status_CW %>%
  group_by(region_id) %>%
  summarize(score = sum(pressure_score, na.rm=TRUE)/length(na.omit(pressure_score))) %>%
  ungroup() %>%
  mutate(goal = "CW") %>%
  mutate(dimension = "status") %>%
  select(goal, dimension, region_id, score) %>%
  data.frame()

## calculate overall CW trend gap-filling:
trend_CW <- rbind(pathogen_trend, nutrients_trend, chemicals_trend, trash_trend)
trend_CW <- trend_CW %>%
  group_by(region_id) %>%
  summarize(score = sum(trend, na.rm=TRUE)/length(na.omit(trend))) %>%
  ungroup() %>%
  mutate(goal = "CW") %>%
  mutate(dimension = "trend") %>%
  select(goal, dimension, region_id, score) %>%
  data.frame()


### putting the data together
scores_CW <- rbind(status_CW, trend_CW)
tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_CW), 'scores.csv', row.names=FALSE, na="")


```


### Fisheries

Fishery status scores are calculated within each region by taking a geometric mean of the stock status scores (b/bmsy --> stock status) weighted by the stock's proportion of the total catch.  For example,

Variable      |  Stock A   | Stock B
------------- | ---------- | ----------
stock status  | 0.1        | 1
proportion of catch | 0.1  | 0.9

The status is calculated as:
0.1^0.1 * 1^0.9  = 0.79

The geometric mean gives more weight to lower stock status scores than a normal weighted mean (for reference, if this were a weighted mean, the score would be 0.91).

Another example is: 0.1^.5 * 1^.5 = ```0.1^.5 * 1^.5```

Stocks that didn't have b/bmsy values because they were not identified to species or had inadequate data are gap-filled using the median of the other stocks in their region/year.  A penalty is also applied to stocks not identified to species level, as this is considered an indicator of a poorly managed stock.  

To calculate the proportion of gap-filling, I thought I would code gap-filled taxa as 1 and non-gapfilled taxa as 0.0001 (a near zero value, because you can't use a 0 score for the geometric mean, 0^0.1 = 0).  The next step would be to take the geometric mean of these values weighted by the relative proportion of catch.  When I used this method, the scores tended to suggest there was very little gap-filling because the geometric mean tends toward the lower scores.  

This is not correct.  Instead, I think I will just calculate the proportion of the catch that did not have directly estimated b/bmsy values.

Final method: Proportion of catch that is gap-filled for b/bmsy.

```{r fisheries, warning=FALSE, message=FALSE}

bmsy <- read.csv('../../eez2015/layers/fis_b_bmsy.csv')

catch <- read.csv('../../eez2015/layers/fis_meancatch.csv') %>%
  separate(fao_saup_id, c("fao_id", "saup_id"), sep="_") %>%
  separate(taxon_name_key, c("taxon_name", "taxon_key"), sep="_") %>%
  mutate(fao_id = as.numeric(fao_id)) %>%
  mutate(saup_id = as.numeric(saup_id)) %>%
  mutate(taxon_key = as.numeric(taxon_key)) %>%
  left_join(bmsy, by=c("fao_id", "taxon_name", "year"))

saup2rgn <- read.csv('../../eez2015/layers/fis_proparea_saup2rgn.csv')

fis_gapfill_saup <- catch %>%
  mutate(gap_fill = ifelse(is.na(b_bmsy), 1, 0)) %>%
    group_by(year, saup_id) %>%
    summarize(score = weighted.mean(gap_fill, mean_catch)) %>%
    ungroup() %>%
    data.frame() 
 
# ## check: looks good (change summarize above to mutate to test this)
# tmp <- filter(fis_gapfill_saup, saup_id==166 & year ==2011) 
# gf <- sum(tmp$mean_catch[tmp$gap_fill==1])
# non_gf <- sum(tmp$mean_catch[tmp$gap_fill==0])
# 844/(844+1013) 
# ##

  # ------------------------------------------------------------------------
  # STEP 5. Convert  from saup spatial scale to OHI spatial scale  
  # -----------------------------------------------------------------------
  # In many cases the ohi reporting regions are comprised of multiple saup regions.
  # To correct for this, the proportion of each saup area of the total area of the 
  # OHI region was calculated. This was used to calculate Status from the Status_saup.
  # This type of adjustment is omitted if the data were collected at the same spatial 
  # scale as the collecting region.
  
  # Join region names/ids to Geom data
  fis_gapfill <- fis_gapfill_saup %>% 
   left_join(saup2rgn, by = 'saup_id')
 
  # weighted mean scores
  fis_gapfill <- fis_gapfill %>%
    group_by(rgn_id, year) %>%
    summarize(score = sum(score*prop_area)) %>%
    ungroup() %>%
    data.frame() %>%
    filter(!is.na(rgn_id))

## summarizing for status
  status_FIS <- fis_gapfill %>% 
    filter(year == 2011) %>%
    mutate(goal = "FIS") %>%
    mutate(dimension = "status") %>%
    select(goal, dimension, region_id=rgn_id, score)
    
## summarizing for trend
  trend_FIS <- fis_gapfill %>% 
    filter(year %in% (2011-4):2011) %>%
    group_by(rgn_id) %>%
    summarize(score = mean(score)) %>%
    mutate(goal = "FIS") %>%
    mutate(dimension = "trend") %>%
    ungroup() %>%
    select(goal, dimension, region_id=rgn_id, score) %>%
    data.frame()


### putting the data together
scores_FIS <- rbind(status_FIS, trend_FIS)
tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_FIS), 'scores.csv', row.names=FALSE, na="")

```

### Mariculture
Mariculture is basically calculated for each region and year, as: 

sum_species (sustainability * harvest_tonnes)

At the species level, the sustainability and harvest data will be score as a one or zero, depending (respectively) whether the value was gap-filled.  Then, for each species, the proportion of gap-filling will be calculated as:

Species_gf = (sustatinability_gf + harvest_tonnes_gf)/2

Then, for each region, the proportion of the species scores that were gap-filled will be calculated as:

region_gf = sum(species_gf)/total number of species

Types of gap-filling

data                | type of gap-filling
sustainability       | fairly extensive.  Trujillo data is provided for sustainability of species and regions.  If a region does not have sustatainability data for a species, it is gap-filled using the species, genera, or other taxonomic average.  These will be counted equally.
harvest_tonnes      | relatively little gap-filling. In a couple places, we assumed that NA values were 0.  This will count as gap-filling.


```{r mariculture, warning=FALSE, message=FALSE}

sustain <- read.csv('layers/mar_sustainability_score.csv') %>%
  select(region_id = id, species, species_code, year, gap_fill_sustain = gapfill) %>%
  mutate(gap_fill_sustain = ifelse(gap_fill_sustain == "actuals", 0, 1))


harvest <- read.csv('layers/mar_harvest_tonnes.csv') %>%
  select(region_id = id, species, species_code, year, gap_fill_harvest = gap_0_fill)%>%
  mutate(gap_fill_harvest = ifelse(gap_fill_harvest == "NA_to_zero", 1, 0)) 


gap_fill <- harvest %>%
  left_join(sustain, by=c("region_id", "year", "species", "species_code")) %>%
  mutate(gap_fill_species = (gap_fill_harvest + gap_fill_sustain)/2) %>%
  group_by(region_id, year) %>%
  summarize(score = sum(gap_fill_species)/length(gap_fill_species))


## summarizing for status
  status_MAR <- gap_fill %>% 
    filter(year == 2013) %>%
    mutate(goal = "MAR") %>%
    mutate(dimension = "status") %>%
    select(goal, dimension, region_id, score)
    
## summarizing for trend
  trend_MAR <- gap_fill %>% 
    filter(year %in% (2013-4):2013) %>%
    group_by(region_id) %>%
    summarize(score = mean(score)) %>%
    mutate(goal = "MAR") %>%
    mutate(dimension = "trend") %>%
    ungroup() %>%
    select(goal, dimension, region_id, score) %>%
    data.frame()


### putting the data together
scores_MAR <- rbind(status_MAR, trend_MAR)
tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_MAR), 'scores.csv', row.names=FALSE, na="")

```

### Natural Product
Natural product is calculated as (see issue 370 for more details):

Within each region, calculate the following for each of the 6 products (coral, sponges, ornamentals, fish oil, shells seaweeds):
sustainability = 1 - (exposure + risk)/2
product_status = sustainability * relative tonnes

Then for each region, take the average of the product_status scores for each product weighted by USD.   

There are 4 possible variables that could be gap-filled:

variable         | types of gap-filling
---------------- | -----------------------------------
tonnes           | zero-fill: Zero values are given when there are missing values for both USD and tonnes\
                 | r1_t/u_rgn: tonnes ~ usd within a region\
                 | r2_t/u_gr: tonnes ~ usd + year within a georegion\
                 | r2_t/u_gl: tonnes ~ usd + year global data
usd              | same as tonnes (but no gap-filling in more recent years used in analysis)                 
risk             | blast and cyanide: no gap-filling
exposure         | no gap-filling for rocky reef or coral habitat\
                 | gap-filling for FIS \
                 | gap-filled in some cases for overall exposure (done in functions.R)



```{r natural products, warning=FALSE, message=FALSE}

####################################################
## exposure: currently no gap-filling for coral or rocky reef
habitat <- read.csv('layers/hab_extent.csv') %>%
  filter(habitat %in% c('rocky_reef', 'coral'))

if(sum(!(is.na(habitat$gap_fill) | habitat$gap_fill ==0)) > 0){
  stop("coral or rocky reef habitat extents have gap-filling - will need to incorporate this into calculation")
}

# gapfilling for fish oil (use FIS data): use same data for all years
fis_exposure <- read.csv('scores.csv') %>%
  filter(goal == 'FIS' & dimension == "status") %>%
  filter(region_id != 0) %>%
  mutate(product = "fish_oil") %>%
  select(rgn_id = region_id, product, exposure=score) 

year_range <- 1976:2011
year <- rep(year_range, each=length(fis_exposure$rgn_id))
tmp <-   fis_exposure[rep(seq_len(nrow(fis_exposure)), length(year_range)), ]
fis_exposure <- cbind(tmp, year)
  

# function.R gap-filling for exposure when the product is a NP, but the corresponding habitat is not in the region
# in these cases we gapfilled with the mean exposure of the products in other regions
# this file is generated in functions.R NP function

exposure <- read.csv('../../eez2015/temp/NP_exposure_gapfill.csv') %>%
  mutate(exposure = ifelse(gap_fill==0, 0, 1)) %>%
  select(rgn_id, product, year, exposure) %>%
  bind_rows(fis_exposure)
  


########################################################
## risk gap-filling: none for blast/poison data
## not gap-filling at this point.  Will return a warning
## if subsequent datasets for these variable have gapfilling

blast <- read.csv('layers/np_blast.csv')
if(sum(blast$gap_fill) > 0){
  stop("risk: blast data has gap-filling - will need to incorporate this into calculation")
}

poison <- read.csv('layers/np_cyanide.csv')
if(sum(poison$gap_fill) > 0){
  stop("risk: blast data has gap-filling - will need to incorporate this into calculation")
}


#########################################################
## Harvest gap-filling
## 
weights <- read.csv('../../eez2015/layers/np_harvest_product_weight.csv')
## weights only include 2006:2011 data

gapData <- read.csv('layers/np_harvest_tonnes_relative.csv')
table(gapData$gapfill)
paperVals <- gapData %>%
  filter(year > 2001)
table(gapData$gapfill)
1243/(12983 + 1243 + 488 +15 + 13) # ~ 8% of data zero filled
(488 + 15 + 13)/(12983 + 488 +15 + 13)  # ~ 4% of remaining data filled with modeled data

# figure out what to do when _u_ is gap-filled (this indicates gapfilling for usd used to calculate the weights)
filter(gapData, gapfill == "r2_u_gr")  # all of these are from a long time ago - can ignore!  


# STEP 1: Figure out proportion of each region/year/product that was gap-filled (Each type of gap-filling counts as a 1, otherwise 0)
# STEP 2: Weight proportion of gap-filling by proportion of max USD for each product/region during past 6 years to get estimate of gap-filling across all products

productData <- gapData %>%
  filter(gapfill != "r2_u_gr") %>%  # filtered out because these are old
  group_by(rgn_id, product, year) %>%
  summarize(totalProducts=n(),
              totalGapfill=sum(!(gapfill %in% "none"))) %>%
  mutate(Proportion_gf_tonnes = totalGapfill / totalProducts) %>%
  left_join(weights, by=c("rgn_id", "product")) %>%
  filter(!is.na(weight)) %>%
  ungroup() %>%
  data.frame()

gap_fill <- productData %>%
  left_join(exposure, by=c('rgn_id', 'product', 'year')) %>%
  filter(!is.na(exposure)) %>%   # N=904 NA values, this is an error in gap-filling in functions.R...fix next time
  mutate(sustainability = exposure/2) %>%
  mutate(product_score_gf = (Proportion_gf_tonnes + sustainability)/2) %>%
  group_by(rgn_id, year) %>%
  summarize(score = weighted.mean(product_score_gf, weight))


## summarizing for status
  status_NP <- gap_fill %>% 
    filter(year == max(gap_fill$year)) %>%
    mutate(goal = "NP") %>%
    mutate(dimension = "status") %>%
    select(goal, dimension, region_id=rgn_id, score)
    
## summarizing for trend
  trend_NP <- gap_fill %>% 
    filter(year %in% (max(gap_fill$year)-4):max(gap_fill$year)) %>%
    group_by(rgn_id) %>%
    summarize(score = mean(score)) %>%
    mutate(goal = "NP") %>%
    mutate(dimension = "trend") %>%
    ungroup() %>%
    select(goal, dimension, region_id=rgn_id, score) %>%
    data.frame()


### putting the data together
scores_NP <- rbind(status_NP, trend_NP)
tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_NP), 'scores.csv', row.names=FALSE, na="")

```


### Tourism and Recreation
Tourism and Recreation is calculated as:

Ep = Proportion of employment in tourism and recreation (directly supplied by WTTC, but in the past calculated using additional World Bank Data for Unemployment, U, and Labor Force, L)

S = Sustainability score based on TTCI data

Xtr = Ep * S

Variables that could be gap-filled, are:

variable         | types of gap-filling
---------------- | -----------------------------------
Ep               | Ep values, UN r2 georegions
S                | gdp + georegion (mostly r2 designations, but some r1, and sometimes with gap-filled GDP)

Unemployment (U) and Labor Force are listed in data, but they are not used in practice because Ep is directly estimated (should probably simplify output in next iteration). 

GDP (used to estimate S) is also gap-filled in some cases. Estiamtes of S based on gap-filled GDP will have greater uncertainty, but for now, I will count all gap-filled S values the same. At some point, it would be good to incorporate estimates of error into the gapfill estimates (rather than binary: gapfilled/not gapfilled).  


```{r tourism and recreation, warning=FALSE, message=FALSE}

gf <- read.csv('layers/tr_sustainability.csv') 

gf <- separate(gf, gaps, c("Ep", "U", "S", "L", "G"), sep=c(1,2,3,4))

gf <- gf %>%  ## L and U don't actually matter
  mutate(Ep = ifelse(Ep == "E", NA, 
                      ifelse(Ep == "_", 0, 1))) %>%  ## E values are given an NA value
  mutate(S = ifelse(S == "S", NA,                   ## S values are given an NA value
                     ifelse(S == "_", 0, 1))) %>%
    mutate(G = ifelse(G %in% c("_", "*", "c"), 0,
                    ifelse(G == "G", NA, 1)))  %>%    ## G values are given an NA value, c is an alternative data source, * means it wasn't needed
  mutate(SG = paste0(S, G))  # Informational: for now, estimates of S are treated the same, regardless of whether the gdp is estimated                                                      
gap_fill <- gf %>%
  mutate(score = (Ep + S)/2)
  

## summarizing for status
  status_TR <- gap_fill %>% 
    filter(year == max(gap_fill$year)) %>%
    mutate(goal = "TR") %>%
    mutate(dimension = "status") %>%
    select(goal, dimension, region_id=rgn_id, score)
    
## summarizing for trend
  trend_TR <- gap_fill %>% 
    filter(year %in% (max(gap_fill$year)-4):max(gap_fill$year)) %>%
    group_by(rgn_id) %>%
    summarize(score = mean(score)) %>%
    mutate(goal = "TR") %>%
    mutate(dimension = "trend") %>%
    ungroup() %>%
    select(goal, dimension, region_id=rgn_id, score) %>%
    data.frame()


### putting the data together
scores_TR <- rbind(status_TR, trend_TR)
tmp <- read.csv('scores.csv')

write.csv(rbind(tmp, scores_TR), 'scores.csv', row.names=FALSE, na="")

```


### Checking data


```{r check, warning=FALSE, message=FALSE}

scores <- read.csv('scores.csv')

# should be 18 goals
if(length(table(scores$goal)) != 14){
  stop('There are not 14 goals/subgoals')
}

# every goal should have a status and trend
if(sum(is.na(table(scores$goal, scores$dimension))) > 0 ){
  stop('One or more goals is missing the status/trend dimension')
}

# Make sure the number of regions calculated is about right...this is a loose one
if(sum(table(scores$goal, scores$dimension) < 100 | table(scores$goal, scores$dimension) > 250) > 0) {
  stop('One or more of the goals appears to have too many or too few values')
}

## make sure scores are calculated on the same scale
if(min(scores$score, na.rm=TRUE) < 0 | max(scores$score, na.rm=TRUE) > 1) {
  stop('Scores are outside 0 to 1 range...check this')
}

```


