--- 
title: Layers descriptions 
output: 
  html_document: 
    toc: true 
    toc_depth: 1 
    number_sections: false 
    toc_float: yes 
---

```{r, message=FALSE, echo=FALSE, warning=FALSE, error=FALSE} 
 library(dplyr) 
 library(tidyr) 
 library(knitr) 
 layer_meta <- read.csv('../../eez_layers_meta_data/layers_eez_base.csv', stringsAsFactors = FALSE) 
 
```

 
#Adjusted workforce size 
####(le_workforcesize_adj) {-} 
```{r, child = '../../global_supplement/layers_info/le_workforcesize_adj.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of jobs

 
#Adjustment factor for jobs (current) 
####(le_jobs_cur_adj_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_cur_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for jobs (reference) 
####(le_jobs_ref_adj_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_ref_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for revenue (current) 
####(le_rev_cur_adj_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_cur_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for revenue (reference) 
####(le_rev_ref_adj_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_ref_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for wages (current) 
####(le_wage_cur_adj_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_cur_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Adjustment factor for wages (reference) 
####(le_wage_ref_adj_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_ref_adj_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Areas of blast fishing 
####(np_blast) {-} 
```{r, child = '../../global_supplement/layers_info/np_blast.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Areas of poison fishing 
####(np_cyanide) {-} 
```{r, child = '../../global_supplement/layers_info/np_cyanide.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Artisanal fisheries management effectiveness 
####(fp_mora_artisanal) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mora_artisanal.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Artisanal fisheries opportunity 
####(ao_access) {-} 
```{r, child = '../../global_supplement/layers_info/ao_access.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Average species condition 
####(spp_status) {-} 
```{r, child = '../../global_supplement/layers_info/spp_status.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 status score

 
#Average species condition trend 
####(spp_trend) {-} 
```{r, child = '../../global_supplement/layers_info/spp_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend score

 
#B/Bmsy estimates 
####(fis_b_bmsy) {-} 
```{r, child = '../../global_supplement/layers_info/fis_b_bmsy.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 B/Bmsy

 
#Carbon storage weights 
####(element_wts_cs_km2_x_storage) {-} 
```{r, child = '../../global_supplement/layers_info/element_wts_cs_km2_x_storage.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 extent*storage

 
#Chemical pollution 
####(po_chemicals) {-} 
```{r, child = '../../global_supplement/layers_info/po_chemicals.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Chemical pollution trend 
####(cw_chemical_trend) {-} 
```{r, child = '../../global_supplement/layers_info/cw_chemical_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#CITES signatories 
####(g_cites) {-} 
```{r, child = '../../global_supplement/layers_info/g_cites.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal chemical pollution 
####(po_chemicals_3nm) {-} 
```{r, child = '../../global_supplement/layers_info/po_chemicals_3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal nutrient pollution 
####(po_nutrients_3nm) {-} 
```{r, child = '../../global_supplement/layers_info/po_nutrients_3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal protected marine areas 
####(fp_mpa_coast) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mpa_coast.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal protected marine areas 
####(hd_mpa_coast) {-} 
```{r, child = '../../global_supplement/layers_info/hd_mpa_coast.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Coastal protection weights 
####(element_wts_cp_km2_x_protection) {-} 
```{r, child = '../../global_supplement/layers_info/element_wts_cp_km2_x_protection.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 extent*rank

 
#Commercial fishing management 
####(fp_mora) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mora.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Economic diversity 
####(li_sector_evenness) {-} 
```{r, child = '../../global_supplement/layers_info/li_sector_evenness.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled

 
#Economic need for artisanal fishing 
####(ao_need) {-} 
```{r, child = '../../global_supplement/layers_info/ao_need.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#EEZ protected marine areas 
####(fp_mpa_eez) {-} 
```{r, child = '../../global_supplement/layers_info/fp_mpa_eez.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#EEZ protected marine areas 
####(hd_mpa_eez) {-} 
```{r, child = '../../global_supplement/layers_info/hd_mpa_eez.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Fishery catch data 
####(fis_meancatch) {-} 
```{r, child = '../../global_supplement/layers_info/fis_meancatch.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 tonnes

 
#Food provision weights 
####(fp_wildcaught_weight) {-} 
```{r, child = '../../global_supplement/layers_info/fp_wildcaught_weight.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#GDP 
####(le_gdp) {-} 
```{r, child = '../../global_supplement/layers_info/le_gdp.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 2012 USD

 
#GDP per capita PPP 
####(le_gdp_pc_ppp) {-} 
```{r, child = '../../global_supplement/layers_info/le_gdp_pc_ppp.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 USD

 
#Genetic escapes 
####(sp_genetic) {-} 
```{r, child = '../../global_supplement/layers_info/sp_genetic.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Global Competitiveness Index (GCI) scores 
####(li_gci) {-} 
```{r, child = '../../global_supplement/layers_info/li_gci.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled

 
#Habitat condition 
####(hab_health) {-} 
```{r, child = '../../global_supplement/layers_info/hab_health.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Habitat condition trend 
####(hab_trend) {-} 
```{r, child = '../../global_supplement/layers_info/hab_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Habitat extent 
####(hab_extent) {-} 
```{r, child = '../../global_supplement/layers_info/hab_extent.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Habitat weights 
####(element_wts_hab_pres_abs) {-} 
```{r, child = '../../global_supplement/layers_info/element_wts_hab_pres_abs.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 boolean

 
#High bycatch due to artisanal fishing 
####(fp_art_hb) {-} 
```{r, child = '../../global_supplement/layers_info/fp_art_hb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#High bycatch due to commercial fishing 
####(fp_com_hb) {-} 
```{r, child = '../../global_supplement/layers_info/fp_com_hb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Inland area 
####(rgn_area_inland1km) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_area_inland1km.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Inland coastal population 
####(mar_coastalpopn_inland25mi) {-} 
```{r, child = '../../global_supplement/layers_info/mar_coastalpopn_inland25mi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of people

 
#Inland coastal protected areas 
####(lsp_prot_area_inland1km) {-} 
```{r, child = '../../global_supplement/layers_info/lsp_prot_area_inland1km.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Intertidal habitat destruction 
####(hd_intertidal) {-} 
```{r, child = '../../global_supplement/layers_info/hd_intertidal.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#ISO country codes 
####(cntry_rgn) {-} 
```{r, child = '../../global_supplement/layers_info/cntry_rgn.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 region id

 
#IUCN extinction risk 
####(ico_spp_iucn_status) {-} 
```{r, child = '../../global_supplement/layers_info/ico_spp_iucn_status.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 IUCN risk category

 
#Jobs for each sector and year 
####(le_jobs_sector_year) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_sector_year.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of jobs

 
#Jobs, most current value 
####(le_jobs_cur_base_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_cur_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Jobs, reference value 
####(le_jobs_ref_base_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_jobs_ref_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Low bycatch due to artisanal fishing 
####(fp_art_lb) {-} 
```{r, child = '../../global_supplement/layers_info/fp_art_lb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Low bycatch due to commercial fishing 
####(fp_com_lb) {-} 
```{r, child = '../../global_supplement/layers_info/fp_com_lb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of habitat to preserve biodiversity 
####(fp_habitat) {-} 
```{r, child = '../../global_supplement/layers_info/fp_habitat.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of habitat to preserve biodiversity 
####(hd_habitat) {-} 
```{r, child = '../../global_supplement/layers_info/hd_habitat.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of mariculture  to preserve biodiversity 
####(g_mariculture) {-} 
```{r, child = '../../global_supplement/layers_info/g_mariculture.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of nonindigenous species 
####(sp_alien_species) {-} 
```{r, child = '../../global_supplement/layers_info/sp_alien_species.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of tourism to preserve biodiversity 
####(g_tourism) {-} 
```{r, child = '../../global_supplement/layers_info/g_tourism.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Management of waters to preserve biodiversity 
####(po_water) {-} 
```{r, child = '../../global_supplement/layers_info/po_water.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Mariculture harvest 
####(mar_harvest_tonnes) {-} 
```{r, child = '../../global_supplement/layers_info/mar_harvest_tonnes.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 tonnes

 
#Mariculture Sustainability Index 
####(g_msi_gov) {-} 
```{r, child = '../../global_supplement/layers_info/g_msi_gov.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Mariculture sustainability score 
####(mar_sustainability_score) {-} 
```{r, child = '../../global_supplement/layers_info/mar_sustainability_score.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Marine plastics 
####(po_trash) {-} 
```{r, child = '../../global_supplement/layers_info/po_trash.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Measure of coastal ecological integrity 
####(species_diversity_3nm) {-} 
```{r, child = '../../global_supplement/layers_info/species_diversity_3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Measure of ecological integrity 
####(species_diversity_eez) {-} 
```{r, child = '../../global_supplement/layers_info/species_diversity_eez.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Natural product harvest 
####(np_harvest_tonnes) {-} 
```{r, child = '../../global_supplement/layers_info/np_harvest_tonnes.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 tonnes

 
#Nonindigenous species 
####(sp_alien) {-} 
```{r, child = '../../global_supplement/layers_info/sp_alien.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Nutrient pollution 
####(po_nutrients) {-} 
```{r, child = '../../global_supplement/layers_info/po_nutrients.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Nutrient pollution trend 
####(cw_nutrient_trend) {-} 
```{r, child = '../../global_supplement/layers_info/cw_nutrient_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Ocean acidification 
####(cc_acid) {-} 
```{r, child = '../../global_supplement/layers_info/cc_acid.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Offshore area 
####(rgn_area_offshore3nm) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_area_offshore3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Offshore coastal protected areas 
####(lsp_prot_area_offshore3nm) {-} 
```{r, child = '../../global_supplement/layers_info/lsp_prot_area_offshore3nm.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#OHI regions 
####(rgn_global) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_global.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 label

 
#Pathogen pollution 
####(po_pathogens) {-} 
```{r, child = '../../global_supplement/layers_info/po_pathogens.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Pathogen pollution trend 
####(cw_pathogen_trend) {-} 
```{r, child = '../../global_supplement/layers_info/cw_pathogen_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Percent direct employment in tourism 
####(tr_jobs_pct_tourism) {-} 
```{r, child = '../../global_supplement/layers_info/tr_jobs_pct_tourism.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Plastic trash trends 
####(cw_trash_trend) {-} 
```{r, child = '../../global_supplement/layers_info/cw_trash_trend.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 trend

 
#Region areas based on EEZ boundaries 
####(rgn_area) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_area.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 km2

 
#Regions 
####(rgn_labels) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_labels.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 label

 
#Relative harvest tonnes 
####(np_harvest_tonnes_relative) {-} 
```{r, child = '../../global_supplement/layers_info/np_harvest_tonnes_relative.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Relative harvest value 
####(np_harvest_product_weight) {-} 
```{r, child = '../../global_supplement/layers_info/np_harvest_product_weight.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#Revenue adjustment (GDP) 
####(le_revenue_adj) {-} 
```{r, child = '../../global_supplement/layers_info/le_revenue_adj.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 USD

 
#Revenue for each sector and year 
####(le_rev_sector_year) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_sector_year.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 2010 USD

 
#Revenue, most current value 
####(le_rev_cur_base_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_cur_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Revenue, reference value 
####(le_rev_ref_base_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_rev_ref_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Sea level rise 
####(cc_slr) {-} 
```{r, child = '../../global_supplement/layers_info/cc_slr.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Sea surface temperature 
####(cc_sst) {-} 
```{r, child = '../../global_supplement/layers_info/cc_sst.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Sectors in each region 
####(le_sector_weight) {-} 
```{r, child = '../../global_supplement/layers_info/le_sector_weight.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Social Progress Index 
####(res_spi) {-} 
```{r, child = '../../global_supplement/layers_info/res_spi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Strength of governance 
####(wgi_all) {-} 
```{r, child = '../../global_supplement/layers_info/wgi_all.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Subtidal hardbottom habitat destruction 
####(hd_subtidal_hb) {-} 
```{r, child = '../../global_supplement/layers_info/hd_subtidal_hb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Subtidal softbottom habitat destruction 
####(hd_subtidal_sb) {-} 
```{r, child = '../../global_supplement/layers_info/hd_subtidal_sb.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Targeted harvest of cetaceans and marine turtles 
####(fp_targetharvest) {-} 
```{r, child = '../../global_supplement/layers_info/fp_targetharvest.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Total human population 
####(le_popn) {-} 
```{r, child = '../../global_supplement/layers_info/le_popn.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 number of people

 
#Tourism sustainability index 
####(tr_sustainability) {-} 
```{r, child = '../../global_supplement/layers_info/tr_sustainability.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#Unemployment 
####(le_unemployment) {-} 
```{r, child = '../../global_supplement/layers_info/le_unemployment.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 proportion

 
#UN geopolitical region classifications 
####(rgn_georegions) {-} 
```{r, child = '../../global_supplement/layers_info/rgn_georegions.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 UN regions

 
#US State Department travel warnings 
####(tr_travelwarnings) {-} 
```{r, child = '../../global_supplement/layers_info/tr_travelwarnings.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 score

 
#UV radiation 
####(cc_uv) {-} 
```{r, child = '../../global_supplement/layers_info/cc_uv.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Wages, current value 
####(le_wage_cur_base_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_cur_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Wages for each sector and year 
####(le_wage_sector_year) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_sector_year.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 2010 USD

 
#Wages, reference value 
####(le_wage_ref_base_value) {-} 
```{r, child = '../../global_supplement/layers_info/le_wage_ref_base_value.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 value

 
#Weakness of governance 
####(ss_wgi) {-} 
```{r, child = '../../global_supplement/layers_info/ss_wgi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1

 
#Weakness of social progress 
####(ss_spi) {-} 
```{r, child = '../../global_supplement/layers_info/ss_spi.Rmd', echo=FALSE, results='asis'} 
 
``` 
 
####Units {-} 
 scaled 0-1
