## Artisanal opportunities

Artisanal fishing, often also called small-scale fishing, provides a critical source of food, nutrition, poverty alleviation and livelihood opportunities for many people around the world, in particular in developing nations [@allison_livelihoods_2001]. Artisanal fishing refers to fisheries involving households, cooperatives or small firms (as opposed to large, commercial companies) that use relatively small amounts of capital and energy and small fishing vessels (if any), make relatively short fishing trips, and use fish mainly for local consumption or trade. These traits differ from commercial scale fisheries that serve the global fish trade, and commercial and artisanal scale fisheries also differ in how they are valued by many communities around the world. 

Artisanal fisheries contribute over half of the world’s marine and inland fish catch, nearly all of which is used for direct human consumption [@united_nations_faostat_2010]. They employ over 90 percent of the world’s more than 35 million capture fishers and support another approximate 90 million people employed in jobs associated with fish processing, distribution and marketing [@united_nations_faostat_2010]. Artisanal fisheries also are distinguished by the role they play in shaping and sustaining human cultures around the world; this role contributes to their distinct value [@mcgoodwin_understanding_2001]. For this reason, we designate artisanal fishing opportunities as a distinct public goal. In some countries like the U.S.A., artisanal fishing may happen under a commercial license (e.g., a family run lobster boat or individual shellfish harvesting permit), or under a recreational fishing permit (e.g., families fishing with rods for fish to eat); the food provided by these activities should ideally be captured under the food provision goal, whereas the opportunity to pursue artisanal fishing is captured here. The goal is not about recreational fishing for sport, which is captured in food provision (if it provides food) and tourism and recreation.

The livelihood and household economy provided by fishing are considered part of the coastal livelihoods and economies goal, although similar to food provision from artisanal fishing it is currently impossible to measure on a global scale. Our focus is on the opportunity to conduct this kind of fishing. What is intended by the idea of ‘opportunity’ is the ability to conduct sustainable artisanal-scale fishing when the need is present, rather than the actual amount of catch or household revenue that is generated. Although this may seem nuanced on the value and intent of artisanal fishing, the opportunity to conduct this fishing is clearly of great importance to many people [@mcgoodwin_understanding_2001]. Status for this goal is a function of need for artisanal fishing opportunities and whether or not the opportunity is permitted and/or encouraged institutionally and done sustainability. This need could potentially be driven by any number of socio-economic factors, but perhaps the simplest and most directly tied to this need is the percent of the population that is below the poverty level. Data on how many people live below the poverty level are not available for many countries. Therefore, we used an analogous proxy that is more complete globally: per capita gross domestic product (pcGDP) adjusted by the purchasing power parity (PPP). This metric translates the average annual income (pcGDP) into its local value (PPP). These data correlate with UN data on the percent of a population living below the $2/day international poverty standard (linear: R^2^ = 0.61, p <0.001; logarithmic regression: R^2^ = 0.76, p < 0.001). Because the relationship is a better fit with the ln-linear regression, we ln-transform the PPPpcGDP scores.

#### Current status
Status for this goal ($x_{ao}$) is therefore measured by unmet demand ($D_u$), which includes measures of opportunity for artisanal fishing ($O_{ao}$, defined below) and the sustainability of the methods used ($S_{ao}$):

$$
x_{ao} = (1 – D_u) * S_{ao}, (Eq. 6.1)
$$

where $S_{ao}$ indicates whether artisanal fishing is done in a sustainable manner. This was approximated using Sea Around Us Project (SAUP) (2020) global marine fisheries catch data [@pauly2020] and B/Bmsy data [@ricard_examining_2012; @costello_status_2012; @martell_simple_2013; @thorson_new_2013; @rosenberg_developing_2014; @costello_global_2016; @ram_legacy_stock_assessment_database_ram_2021] calculated from our fisheries sub-goal (methods can be found in section 6.6.1), and subsetted for artisanal and subsistence stocks notated in the SAUP data. And, $D_u$ is calculated as:

$$
D_{u} = (1 – PPPpcGDP) * (1 – O_{ao}), (Eq. 6.2)
$$

where, $PPPpcGDP$ is the ln-transformed, rescaled purchasing power parity adjusted per capita GDP, and $O_{ao}$ is the access to artisanal-scale fishing determined by the United Nations Sustainable Development Goal (UN SDG) 14.b.1 [@food_and_agriculture_organization_of_the_united_nations_progress_2020]. 

We rescaled the ln-transformed $PPPpcGDP$ values from 0-1 by dividing by the value corresponding to the 99th quantile across all regions and years from 2005 to 2015 (values > 1 were capped at 1). Developed countries with lower demand for artisanal scale fishing (i.e., low poverty indicated by high PPPpcGDP) score high, regardless of the opportunity made available (since it would not matter to many), and developing countries with high demand and opportunity would also score high. 

To assess the opportunity or ability to meet this demand, $O_{ao}$, we used data from UN SDG 14.b.1 [@food_and_agriculture_organization_of_the_united_nations_progress_2020], which scores countries on the institutional measures that support or protect access to artisanal and small-scale fishing. The data come are FAO member country responses to the Code of Conduct for Responsible Fisheries (CCRF) (Table 6.1) survey questionnaire which is circulated by FAO every two years to members and IGOs and INGOs and are on a scale from 0 to 1. 

The sustainability of artisanal fishing practices was estimated by subsetting for artisanal and subsistence stock B/Bmsy values which were calculated in our fisheries sub-goal (section 6.6.1).

Several issues and datasets relevant to artisanal fishing opportunities were not included in our calculations for a number of reasons. High unemployment can lead to a greater demand for artisanal fishing opportunities [@cinner_socioeconomic_2009], but unemployment is not a good measure of potential 'demand' for most developing countries since many people not working do not get recorded in unemployment statistics, even though it may be relevant for developed countries. Regardless, it is very difficult to set an arbitrary cut-off for developing versus developed countries, and so there is no clear way to use unemployment data for this goal.


**Table 6.1. Artisanal access**. 
Questions from UN SDG 14.b.1 [@food_and_agriculture_organization_of_the_united_nations_progress_2020] that were used to evaluate access to artisanal scale fishing.

* Are there any laws, regulations, policies, plans or strategies that specifically target or address the
small-scale fisheries sector? 

|   |  Yes | No  |
|---|---|---|
| Law  |   |   |
| Regulation  |   |   |
| Policy  |   |   |
| Plan/strategy  |   |   |
| Other (please specify)  |   |   |
    
    
* The Voluntary Guidelines for Securing Sustainable Small-scale Fisheries in the Context of Food Security and Poverty Eradication (SSF Guidelines) were endorsed by [COFI in June 2014](www.fao.org/3/a-i4356e.pdf). Does your country have a specific initiative to implement the SSF Guidelines?     

#### Trend
Trend was calculated as described in section  5.3.1. 

#### Data
_Status and trend_

```{r AO data st, results="asis", echo=FALSE}
data_layers(goal="AO", dimension=c("status", "trend"))
```

_Pressure_

```{r AO data p, results="asis", echo=FALSE}
data_layers(goal="AO", dimension=c("pressure"))
```

_Resilience_

```{r AO r, results="asis", echo=FALSE}
data_layers(goal="AO", dimension=c("resilience"))

```

