### Habitat (subgoal of biodiversity)

The habitat subgoal measures the average condition of marine habitats present in each region that provide critical habitat for a broad range of species (mangroves, coral reefs, seagrass beds, kelp forests, salt marshes, sea ice edge, tidal flats, and subtidal soft bottom). This subgoal is considered a proxy for the condition of the broad suite of marine species.

Data availability remains a major challenge for species and habitat assessments. We compiled and analyzed the best available data in both cases, but key gaps remain. Although several efforts have been made in recent years to create or compile the data necessary to look at the status and trends of marine habitats, most efforts are still hampered by limited geographical and temporal sampling [@joppa2016filling], although sea ice [@digirolamo2022 data is an exception. In addition, most marine habitats have only been monitored since the late 1970s at the earliest, many sites were only sampled over a short period of time, and very few sites were monitored before the late 1990s so establishing reference points was difficult. Salt marshes, kelp forests, and seagrasses were the most data-limited of the habitats included in the analysis. 

#### Current status

The status of the habitat sub-goal, $x_{hab}$, was assessed as the average of the condition estimates, $C$, for each habitat, $k$, present in a region; measured as the loss of habitat and/or % degradation of remaining habitat, such that:

$$
x_{hab} = \frac { \displaystyle\sum _{ k=1 }^{ N }{ { C }_{ k } }  }{ N}, \quad \quad (Eq. 6.3)
$$

where, $C_{k} = C_{c}/C_{r}$ and $N$ is the number of habitats in a region. $C_{c}$ is the current condition and $C_{r}$ is the reference condition specific to each $k$ habitat present in the region (Table 6.2). This formulation ensures that each country is assessed only for those habitats that can exist (e.g., Canada is not assessed on the status of its nonexistent coral reefs). We generally considered the reference years to be between 1980-1995, although these varied by habitat due to data availability.

**Table 6.2. Habitat data**
Description of condition, extent, and trend calculations for habitat data (Note: extent is not used to calculate the habitat subgoal, but is used for the coastal protection and carbon storage goals). More information about the sources used to generate these values is located in Section 7 and Table 7.2. 

Habitat | Condition | Extent | Trend
-------- | --------------------- | ----------------- | ------------------
Seagrass | Increasing or stable trend assigned condition = 1.0; decreasing trend assigned condition = 0.71 based on global loss | Seagrass extent per oceanic region (vector based) | Calculated across data from 1990 - 2000
Kelp | Increasing or stable trend assigned condition = 1.0; decreasing trend assigned condition based on a 2% global yearly loss | Kelp extent per oceanic region (vector based) | Calculated across data from 1983 - 2012
Coral reefs | Current % cover divided by reference % cover | Coral reef extent per oceanic region (Vector based) | Calculated across data from 1975-2006
Mangroves | Current hectares divided by reference hectares, for coastal mangroves only | Mangrove extent per oceanic region (vector based) | Calculated using 5 most recent years of data
Salt marsh | All regions assigned condition = 0.75 based on conservative historical extent losses | Salt marsh extent per oceanic region | All regions assigned trend based on historical .28% global yearly loss 
Sea ice edge | Current (3-year rolling-average using the current year and previous 2 years) % cover of sea ice having 10-50% cover, divided by reference % cover average from 1979-2000 | Same as condition | Calculated from the fitted slope of %-deviation-from-reference per year, of the most recent 5 years of data (each year of data is based on 3-year average)
Soft bottom | Soft-bottom destructive fishing practices relative to area of soft-bottom habitat and rescaled to 0-1 based on relative global values | Halpern et al. [-@halpern2008global] | Calculated using 5 most recent years of condition data
Tidal flat | Average tidal flat extent of 2010 and 2013 relative to historic extent (average of 1989 and 1992) | Tidal flat extent per oceanic region (vector based) | Calculated across data from 2001-2013

A significant amount of pre-processing of the habitat data was needed to fill data gaps and resolve data quality issues (Section 7). Because consistent habitat monitoring data was unavailable for many countries, anomalous values can occur. This is particularly true for highly variable habitats like seagrasses or coral reefs which can have significant site-to-site and year-to-year differences in extent and condition [@bruno_regional_2016]. Biases may also have been introduced from spatial (e.g., protected or impacted sites) and temporal (e.g., directly after a disturbance event) selections in sampling. In regions where we had a limited number of surveys in a particular country, overall status can be under- or overestimated because of these fluctuations.

#### Trend

Trend in habitat data were calculated as the linear trend in extent or condition with slight variations depending on habitat type. Coral reef habitat trends were calculated on a per country basis, using all available data. For saltmarsh we apply a single global trend value to each region. For seagrasses and kelp we calculated trends on a per site basis. For mangroves we used the rate of change in areal extent over the most recent 5 years of available data. For sea ice we calculated the slope across the most recent 5 years of data, where each year of data is based on a 3-year moving averages to smooth out potential climate variation. For soft bottom habitat we simply calculated the slope of the recent change in condition over the past 5 years, i.e., the change in proportion of bottom trawl and dredge fishing per unit area of soft bottom habitat within a region.

#### Data

_Status and trend_

```{r HAB data st, results="asis", echo=FALSE}
data_layers(goal="HAB", dimension=c("status", "trend"))
```

_Pressure_

```{r HAB data p, results="asis", echo=FALSE}
data_layers(goal="HAB", dimension=c("pressure"))
```

_Resilience_

```{r HAB r, results="asis", echo=FALSE}
data_layers(goal="HAB", dimension=c("resilience"))

```