### Iconic species (subgoal of sense of place)

Iconic species are those that are relevant to local cultural identity through their relationship to one or more of the following: 1) traditional activities such as fishing, hunting or commerce; 2) local ethnic or religious practices; 3) existence value; and 4) locally-recognized aesthetic value (e.g., touristic attractions/common subjects for art such as whales).  Ultimately, almost any species can be iconic to someone, and so the intent with this goal was to focus on those species widely seen as iconic from a cultural or existence value (rather than a livelihoods or extractive reason). Habitat-forming species were not included, nor were species harvested solely for economic or utilitarian purposes (even though they may be iconic to a sector or individual). 

#### Current status
The status of this sub-goal, $x_{ico}$, is the average of status scores of the iconic species in each region based on their IUCN Red List threat categories [@iucn2020]:

$$
x_{ico} = \frac { \displaystyle\sum_{ i=EX }^{ LC }{ S_{i}\times w_{i} }  }{ \displaystyle\sum_{ i=EX }^{ LC }{ S_{i} }  }, (Eq. 6.17)
$$

where for each IUCN threat category $i$, $S_{i}$ is the number of assessed species and $w_{i}$ is the status (Table 6.3) following the methods described by Butchart et al. [-@butchart_improvements_2007]. This formulation gives partial credit to species that still exist but are in one of the other threat categories. The reference point is to have the risk status of all assessed species as Least Concern (i.e., a goal score = 1.0). Species that have not been assessed or labeled as data deficient are not included in the calculation.

The list of iconic species was drawn from several [data sources](http://ohi-science.org/ohi-global/layers#iucn_extinction_risk) (Table 6.3, IUCN extinction risk), but primarily from the World Wildlife Fund’s global and regional lists for Priority Species (especially important to people for their health, livelihoods, and/or culture) and Flagship Species (‘charismatic’ and/or well-known).  Many lists exist for globally important, threatened, endemic, etc. species, but in all cases it is not clear if or to what extent these species represent culturally iconic species. The World Wildlife Fund is the only data source that included cultural reasons for listing iconic species.  Although, iconic species vary largely among regions, we include little regional information in our list (i.e., the same list is applied to nearly all regions). Our ultimate goal is to develop a more region-specific iconic species list.  


#### Trend
We calculate trend using data the IUCN provides for current and past assessments of species, which we use to create a time series of average risk status for species within each region.  Because IUCN assessments are generally infrequent for any given species, we derive the trend as the annual change in risk status for each species across the previous twenty years, rather than a five-year window typical of other goals, and include only taxa with two or more IUCN assessments within the past 20 years.


#### Data
_Status and trend_

```{r ICO data st, results="asis", echo=FALSE}
data_layers(goal="ICO", dimension=c("status", "trend"))
```

_Pressure_

```{r ICO data p, results="asis", echo=FALSE}
data_layers(goal="ICO", dimension=c("pressure"))
```

_Resilience_

```{r ICO r, results="asis", echo=FALSE}
data_layers(goal="ICO", dimension=c("resilience"))

```


