### Livelihoods (subgoal of livelihoods and economies)

This subgoal measures the jobs produced from marine-related industries.  Livelihoods includes two equally important sub-components, the number of jobs, which is a proxy for livelihood quantity, and the per capita average annual wages, which is a proxy for job quality.

#### Current status
The status of the livelihoods sub-goal, $x_{liv}$, is calculated as:

$$
x_{liv} = \frac { \frac { \sum _{ 1 }^{ k }{ { j }_{ c,k } }  }{ \sum _{ 1 }^{ k }{ { j }_{ r,k } }  } \quad +\quad \frac { \sum _{ 1 }^{ k }{ { w }_{ m,k } }  }{ \sum _{ 1 }^{ k }{ { w }_{ r,k } }  }  }{ 2 }, (Eq. 6.13)
$$

where $j$ is the adjusted number of direct and indirect jobs within sector $k$ within a region and $w$ is the average PPP-adjusted wages per job within the sector. Jobs are summed across sectors and measured at current, $c$, and reference, $r$, time points. Adjusted wage data are averaged across sectors within each region, $m$, and the reference country, $r$, with the highest average wages across all sectors.

Because there is no absolute global reference point for jobs (i.e., a target number would be completely arbitrary), this component of the livelihoods subgoal uses a moving baseline as the reference point. Jobs, $j$, are calculated as a relative value: the value in the current year (or most recent year), $c$, relative to the value in a recent moving reference period, $r$, defined as 5 years prior to $c$. This reflects an implicit goal of maintaining coastal jobs on short time scales, allowing for decadal or generational shifts in what people want and expect. We allowed for a longer or shorter gap between the current and recent years if a 5 year span was not available from the data, but the gap could not be greater than 10 years. Our preferred gap between years was as follows (in order of preference): 5, 6, 4, 7, 3, 8, 2, 9, 1, and 10 years.  For wages, $w$, we assumed the reference value was the highest value observed across all regions. 


Absolute values for $j$ and $w$ in the current and reference period (jobs) or region (wages) were lumped across all sectors before calculating relative values (even though the current and reference years will not be exactly the same for all sectors), allowing a decrease in one sector to be balanced by an increase in another sector. As such, we do not track the status of individual sectors and instead always focus on the status of all sectors together. For wages, we use the most current data available for each country and each sector, but only use data from 1990 on, assuming that wages are relatively slow to change over time (apart from inflation adjustments, which we control for by using real dollars) and thus can be compared across sectors and countries without controlling for year.

Wages data were divided by the inflation conversion factor so that wage data across years would be comparable in 2010 US dollars (inflation conversion factors were downloaded from http://oregonstate.edu/cla/polisci/sahr/sahr). These data were also multiplied by the purchasing power parity-adjusted per capita GDP [https://data.worldbank.org/indicator/NY.GDP.PCAP.CD](https://data.worldbank.org/indicator/NY.GDP.PCAP.CD).  To account for broader economic forces that may affect jobs independent of changes in ocean health (e.g., a global recession), we  adjusted jobs data by dividing by percent employment for the corresponding year: (1 – percent unemployment) * total labor force [@world_bank_labor_2014; @world_bank_unemployment_2014]. For example, if unemployment increased from the reference to the current period, we would expect the number of marine-related jobs to decrease by a comparable proportion, without causing a lower score for the goal. Therefore, the objective of the goal is actually no loss of jobs and jobs must keep pace with growth in employment rates or sustain losses no greater than national increases in unemployment rates. The current and reference years used for unemployment data were based on the average current year and average reference year across the sector data sources used for number of jobs.

#### Trend
Trend was calculated as the slope in the individual sector values (not summed sectors) for jobs and wages over the most recent five years (as opposed to the status, which examines changes between two points in time, current versus five years prior to current), corrected by national trends in employment rates and average wages. We then calculated the average trend for jobs across all sectors, with the average weighted by the number of jobs in each sector. We calculated the average trend for wages across all sectors. We then averaged the wages and jobs average slopes to get the livelihoods trend.

#### Data
_Status and trend_

```{r LIV data st, results="asis", echo=FALSE}
data_layers(goal="LIV", dimension=c("status", "trend"))
```

_Pressure_

```{r LIV data p, results="asis", echo=FALSE}
data_layers(goal="LIV", dimension=c("pressure"))
```

_Resilience_

```{r LIV r, results="asis", echo=FALSE}
data_layers(goal="LIV", dimension=c("resilience"))

```
