### Lasting special places (subgoal of sense of place)

The lasting special places sub-goal focuses on geographic locations that hold particular value for aesthetic, spiritual, cultural, recreational or existence reasons [@trc_inventory_2004]. This sub-goal is particularly hard to quantify. Ideally one would survey every community around the world to determine the top list of special places, and then assess how those locations are faring relative to a desired state (e.g., protected or well managed). The reality is that such lists do not exist. Instead, we assume areas that are protected indicate special places (i.e., the effort to protect them suggests they are important places). Clearly this is an imperfect assumption but in many cases it will be true.

The identification of protected areas does not indicate the proportion of special places in a region that are protected.  To solve this problem we make two important assumptions. First, we assume that all countries have roughly the same percentage of their coastal waters and coastline that qualify as lasting special places. In other words, they all have the same reference target (as a percentage of the total area). Second, we assume that the target reference level is 30% of area protected [@hughes_climate_2003].

#### Current status
We calculate the status of this goal as:

$$
x_{lsp} = \frac { \left( \frac{\%_{CMPA}}{\%_{Ref_{CMPA}}} + \frac {\%_{CP}}{\%_{Ref_{CP}}} \right) }{ 2 }, (Eq. 6.19)
$$

where, $\%_{CMPA}$ is the proportion of coastal marine protected area, $\%_{CP}$ is the proportion of coastline protected, and $\%_{Ref} = 30%$ for both measures. 

We focus only on coastal waters (within 3 nautical miles of shore) for marine special places because we assume lasting special places are primarily in coastal areas. For coastlines, we focus only on the first 1-km-wide strip of land as a way to increase the likelihood that the area being protected by terrestrial parks is connected to the marine system in some way. 

We use the United Nation’s World Database on Protected Areas (WDPA) to identify protected areas [@unep-wcmcandiucn2021]. The WDPA aggregates several key databases: IUCN’s World Commission on Protected Areas, Global Marine Protected Areas, UNESCO World Heritage Marine sites, National Parks and Nature Reserves, and the United Nations List of Protected Places.  In most cases the year of designation is listed for each protected area. 

#### Trend
Trend was calculated as described in section  5.3.1.

#### Data
_Status and trend_

```{r LSP data st, results="asis", echo=FALSE}
data_layers(goal="LSP", dimension=c("status", "trend"))
```

_Pressure_

```{r LSP data p, results="asis", echo=FALSE}
data_layers(goal="LSP", dimension=c("pressure"))
```

_Resilience_

```{r LSP r, results="asis", echo=FALSE}
data_layers(goal="LSP", dimension=c("resilience"))

```
