### Mariculture (subgoal of food provision)

The mariculture subgoal attempts to measure each region's food production from mariculture relative to its capacity. Until the 2019 assessment, a basic problem facing assessments of mariculture was the lack of an ecologically- and socially-based reference point for the potential yield of every suitable mariculture species for every type of geographic habitat and location. Determining such reference points for every country at the global scale is a daunting challenge, not only because so much information was lacking, but also because species, genotypes and habitats are likely to change. However, recent research (Gentry et al. 2017) estimates the global potential for marine aquaculture at a high resolution spatial scale that we aggregrated for each country. Because the estimate provided by Gentry et al. 2017 is very opportunistic, 1% of this tonnage estimate is used for the reference point calculations. 


#### Current status
The status of the mariculture subgoal, $x_{mar}$, was defined as production of strictly marine taxa from both the marine and brackish water FAO categories, excluding species that were not used as a source of food for human consumption. Seaweeds are included, but the tonnes of harvest is multiplied by 0.2 to adjust for protein content relative to fish and shellfish mariculture.  The data reported by FAO does not always clearly describe whether harvest is derived through mariculture or from land-based facilities. Wherever possible, we excluded species that could not have been harvested from coastal waters, such as freshwater cyclids. Mariculture status was therefore assessed as the current sustainably-harvested yield, $Y_{c}$, within each country, such that:

$$
x_{mar}= \frac {Y_c}{Y_{c, ref}},   (Eq. 5.10)
$$
where, $Y_{c,ref}$ is the value that corresponds to 1% of the potential aquaculture harvest in each region, and $Y_c$ is: 

$$
Y_{c}  =  { \displaystyle\sum _{ k=1 }^{ N }{ { Y }_{ k }{ S }_{ k,r } }  } , (Eq. 5.11)
$$


where, $Y_{k}$ is the 4-year moving window average of tonnes of production [@united_nations_fao_2016] for each ${k}$ mariculture species that is currently or at one time cultured within a country, and $S_{k,r}$ is the sustainability score for each $k$ mariculture species and region.

All regions scoring above 1.0 are given a score of 1.0. However, when a region has a current sustainably-harvested yield, $Y_{c}$, that is less than 100 tonnes, and when 1% of potential aquaculture harvest is less and 100 tonnes, a score of NA is assigned. This assumption is made so that regions are not rewarded with a perfect score for having nearly no sustainabily-harvested yield, and potential aquaculture harvest. 

The sustainability score, $S_{k,r}$, for each species in each region is based on the Mariculture Sustainability Index (MSI, -@summerson_recruitment_1990). We used the three sub-indices that directly measured long-term renewability of a given mariculture practice: the wastewater treatment index, the origin of feed index (i.e., fishmeal or other) and the origin of seed (i.e., hatchery or wild caught). These scores are country and species-specific, and we require each species’ yield, $Y_{k}$, to have a corresponding sustainability score, $S_{k,r}$. However, if a country farms a species that was not assessed by the MSI for that country, but it was assessed in other countries, a global average score is used for that species and country. If a country farms a species that was not assessed at all by the MSI but a species within the same genus was assessed, a global average for the genus was used. Finally, if these scores were not available for the categories above, we used the global average for broad taxonomic grouping (e.g., crustaceans, algae, bivalves, etc.). We are aware that there is some bias associated with using scores derived as averages across countries because they were originally assigned to specific species-country pairs, nevertheless this is preferable to applying a sustainability score solely based on a subset of the species harvested.

#### Trend
Trend was calculated as described in section 4.3.1.

#### Data
_Status and trend_

```{r MAR data st, results="asis", echo=FALSE}
data_layers(goal="MAR", dimension=c("status", "trend"))
```

_Pressure_

```{r MAR data p, results="asis", echo=FALSE}
data_layers(goal="MAR", dimension=c("pressure"))
```

_Resilience_

```{r MAR r, results="asis", echo=FALSE}
data_layers(goal="MAR", dimension=c("resilience"))

```
