### Mariculture (subgoal of food provision)

The mariculture subgoal attempts to measure each region's food production from mariculture relative to its capacity [@unitednations2022a] and sustainability [@2022]. A basic problem facing previous assessments of mariculture was the lack of an ecologically- and socially-based reference point for the potential yield of every suitable mariculture species for every type of geographic habitat and location. Determining such reference points for every country at the global scale is difficult, not only because of key missing data and information, but also because species, genotypes and habitats suitable for production in any given location are likely to change from year to year. However, recent research [@gentry2019exploring] estimated the global biological potential for marine aquaculture at a high resolution spatial scale, addressing one of these key gaps: ecological reference points. To account for the social and economic realities and constraints to these ecological potentials, we constrained the per-country potential to 1% of this tonnage estimate and used these country values as reference points. Furthermore, the paper does not exclude high biodiversity or environmentally sensitive areas, meaning 100% of potential aquaculture tonnage estimate is a large overestimation of what is actually possible. Additionally, we include a sustainability score for each species in each region which is based on the [Monterey Bay Aquarium Seafood Watch aquaculture recommendations](https://www.seafoodwatch.org/seafood-recommendations/standards-revision) [@2022].


#### Current status
The status of the mariculture subgoal, $x_{mar}$, was defined as production of strictly marine taxa from FAO categories for both marine and brackish waters, excluding species that were not used as a source of food for human consumption. In particular this was only an issue for seaweeds, as many seaweed species are not used for human consumption (or only partially used for human consumption). Table 6.8 shows the proportions, with a justification column, explaining the proportions of each seaweed species used for human consumption.


**Table 6.8 Mariculture seaweed exclusion**. 
List of seaweed mariculture species, what proportion of their harvest is not used for human consumption, and a justification for the exclusion. 

```{r mar seaweeds, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
library(tidyverse)
library(knitr)
library(kableExtra)
data <- read.csv('https://raw.githubusercontent.com/OHI-Science/ohiprep_v2021/gh-pages/globalprep/mar/v2021/raw/species_list.csv') %>%
	dplyr::filter(Taxon_code == "AL") %>%
dplyr::select(`FAO species name` = FAO_name, `Proportion non food use` = exclude, `Justification` = notes_2)

kable(data) %>%
  kable_styling(full_width = F)
```



Harvest data reported by FAO does not always clearly describe whether it is derived from mariculture or from land-based facilities. Mariculture status, $x_{mar}$, was therefore assessed as the current re-scaled met potential of harvested yield, $Y_{c}$, within each country, multiplied by the production weighted average of sustainability of mariculture within each county, $S_{c}$, such that:

$$
x_{mar} = Y_{c} \ \times \ S_{c},  \   (Eq. 6.10)
$$

where, $Y_{c}$, is the current re-scaled met potential of harvested yield within each country, c, such that: 


$$
Y_{c}= \frac {\displaystyle\sum _{ k=1 }^{ N }{ { Y }_{ k } }}{Y_{r, ref}}, \  (Eq. 6.11)
$$



where, $Y_{r,ref}$ is the value that corresponds to 1% of the potential aquaculture harvest in each region, and $Y_{k}$ is the 4-year moving window average of tonnes of production [@unitednations2022a] for each ${k}$ mariculture species that is currently or at one time cultured within a country. $Y_{c}$ is then capped at 1, so that no country can receive a better-than-perfect score. $S_{c}$ is the production weighted average of sustainability of mariculture in each country, such that: 

$$
S_{c}  =  \frac { \displaystyle\sum _{ k=1 }^{ N }{ { Y }_{ k }{ S }_{ k,r } }  } {{\displaystyle\sum _{ k=1 }^{ N }{ { Y }_{ k } }}}, (Eq. 6.12)
$$


where, $Y_{k}$ is the 4-year moving window average of tonnes of production [@unitednations2022a] for each ${k}$ mariculture species that is currently or at one time cultured within a country, and $S_{k,r}$ is the sustainability score for each $k$ mariculture species and region.

All regions scoring above 1.0 are given a score of 1.0. A score of one could occur when the current aquaculture harvest is greater than 1% of the biological production potential (taken from [@gentry2019exploring]) and mariculture harvest is perfectly sustainable within a region. However, when a region has a current harvested yield that is less than 100 tonnes, and when 1% of potential mariculture harfvest is less than 100 tonnes, a score of NA is assigned. This assumption is made to avoid giving a perfect score to regions that have essentially zero harvested yield, and essentially zero biological production potential. 


The sustainability score, $S_{k,r}$, for each species in each region is based on the [Monterey Bay Aquarium Seafood Watch aquaculture recommendations](https://www.seafoodwatch.org/seafood-recommendations/standards-revision) [@2022]. Ten mariculture practice criteria from the Monterey Bay Aquarium Seafood Watch Aquaculture Recommendations contributed to the sustainability of mariculture (data quality, effluent, habitat risk, chemical use, feed, escapes, disease, source of stock, predator and wildlife mortalities, and escape of secondary species). These criteria represent the internal mariculture practices with the potential to affect the long term sustainability of the mariculture system. Scores for each assessment criterion were aggregated and averaged. All country average scores were then rescaled from 0 to 1 using the maximum possible raw SFW score of 10 and minimum of 1. These scores are country and species-specific, however, many country/species combinations are not assessed by Seafood Watch. Given that each mariculture record must have a corresponding sustainability score, we used a series of steps to estimate sustainability scores for every country and species. If a country/species match was available we used that, otherwise, we gapfilled using the following sequence:

1. Used the global species value provided by Seafood Watch. 
2. Within a country, used the average of species within the same family. 
3. Within a UN geo-political region, used the average of species within the same family. 
4. Global, used average of species within the same family. 
5. Global, used average of species within a broad taxonomic grouping (e.g., crustaceans, algae, bivalves, etc.). 
6. Finally, if these scores were not available for the categories above, we used the global average of all species.  

Seaweed or algae species were given the global seaweed sustainability score provided by the Seafood Watch recommendations. We are aware that there is some bias associated with using scores derived as averages across countries because they were originally assigned to specific species-country pairs, nevertheless this is preferable to applying a sustainability score solely based on a subset of the species harvested.



#### Trend
Trend was calculated as described in section 5.3.1.

#### Data
_Status and trend_

```{r MAR data st, results="asis", echo=FALSE, eval = FALSE}
data_layers(goal="MAR", dimension=c("status", "trend"))
```

_Pressure_

```{r MAR data p, results="asis", echo=FALSE, eval = FALSE}
data_layers(goal="MAR", dimension=c("pressure"))
```

_Resilience_

```{r MAR r, results="asis", echo=FALSE, eval = FALSE}
data_layers(goal="MAR", dimension=c("resilience"))

```
